### 2021-06-25 docs/IEEE/bare_jrnl.tex
Added IEEE LaTeX files to repo

%% bare_jrnl.tex
%% V1.4a
%% 2014/09/17
%% by Michael Shell
%% see http://www.michaelshell.org/
%% for current contact information.
%%
%% This is a skeleton file demonstrating the use of IEEEtran.cls
%% (requires IEEEtran.cls version 1.8a or later) with an IEEE
%% journal paper.
%%
%% Support sites:
%% http://www.michaelshell.org/tex/ieeetran/
%% http://www.ctan.org/tex-archive/macros/latex/contrib/IEEEtran/
%% and
%% http://www.ieee.org/

\documentclass[journal]{IEEEtran}

% Some very useful LaTeX packages include:
\usepackage{tcolorbox}
\usepackage{array}
\newcolumntype{N}{>{\centering\arraybackslash}m{.9cm}}
\newcolumntype{M}{>{\centering\arraybackslash}m{1.0cm}}
\newcolumntype{Z}{>{\centering\arraybackslash}m{1.6cm}}
\newcolumntype{L}{>{\centering\arraybackslash}m{2.3cm}}
\usepackage{multirow}
% (uncomment the ones you want to load)

% ORCID icon
\usepackage{tikz,xcolor}
\usepackage[hidelinks]{hyperref}
% Make Orcid icon
\newcommand{\orcidicon}{\raisebox{1mm}{\includegraphics[width=0.32cm]{figures/logo-orcid.eps}}}
% Define link and button for each author
\foreach \x in {A, ..., Z}{%
\expandafter\xdef\csname orcid\x\endcsname{\noexpand\href{https://orcid.org/\csname orcidauthor\x\endcsname}{\noexpand\orcidicon}}
}
% Define the ORCID iD command for each author separately.
\newcommand{\orcidauthorA}{0000-0002-4137-5605}

% *** MISC UTILITY PACKAGES ***
%
%\usepackage{ifpdf}
% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
% compilation based on whether the output is pdf or dvi.
% usage:
% \ifpdf
%   % pdf code
% \else
%   % dvi code
% \fi
% The latest version of ifpdf.sty can be obtained from:
% http://www.ctan.org/tex-archive/macros/latex/contrib/oberdiek/
% Also, note that IEEEtran.cls V1.7 and later provides a builtin
% \ifCLASSINFOpdf conditional that works the same way.
% When switching from latex to pdflatex and vice-versa, the compiler may
% have to be run twice to clear warning/error messages.

% *** CITATION PACKAGES ***
%
\usepackage{cite}
% cite.sty was written by Donald Arseneau
% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
% \cite{} output to follow that of IEEE. Loading the cite package will
% result in citation numbers being automatically sorted and properly
% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
% \cite will automatically add leading space, if needed. Use cite.sty's
% noadjust option (cite.sty V3.8 and later) if you want to turn this off
% such as if a citation ever needs to be enclosed in parenthesis.
% cite.sty is already installed on most LaTeX systems. Be sure and use
% version 5.0 (2009-03-20) and later if using hyperref.sty.
% The latest version can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/cite/
% The documentation is contained in the cite.sty file itself.

% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
%   \usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../pdf/}{../jpeg/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  % \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.eps}
\fi
% graphicx was written by David Carlisle and Sebastian Rahtz. It is
% required if you want graphics, photos, etc. graphicx.sty is already
% installed on most LaTeX systems. The latest version and documentation
% can be obtained at: 
% http://www.ctan.org/tex-archive/macros/latex/required/graphics/
% Another good source of documentation is "Using Imported Graphics in
% LaTeX2e" by Keith Reckdahl which can be found at:
% http://www.ctan.org/tex-archive/info/epslatex/
%
% latex, and pdflatex in dvi mode, support graphics in encapsulated
% postscript (.eps) format. pdflatex in pdf mode supports graphics
% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
% not a bitmapped formats (.jpeg, .png). IEEE frowns on bitmapped formats
% which can result in "jaggedy"/blurry rendering of lines and letters as
% well as large increases in file sizes.
%
% You can find documentation about the pdfTeX application at:
% http://www.tug.org/applications/pdftex

% *** MATH PACKAGES ***
%
\usepackage[cmex10]{amsmath}
% A popular package from the American Mathematical Society that provides
% many useful and powerful commands for dealing with mathematics. If using
% it, be sure to load this package with the cmex10 option to ensure that
% only type 1 fonts will utilized at all point sizes. Without this option,
% it is possible that some math symbols, particularly those within
% footnotes, will be rendered in bitmap form which will result in a
% document that can not be IEEE Xplore compliant!
%
% Also, note that the amsmath package sets \interdisplaylinepenalty to 10000
% thus preventing page breaks from occurring within multiline equations. Use:
%\interdisplaylinepenalty=2500
% after loading amsmath to restore such page breaks as IEEEtran.cls normally
% does. amsmath.sty is already installed on most LaTeX systems. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/required/amslatex/math/
\usepackage{amsfonts}
\usepackage{amsbsy}

% Used for KL-divergence
\usepackage{mathtools}

\DeclarePairedDelimiterX{\infdivx}[2]{(}{)}{%
  #1\;\delimsize\|\;#2%
}
\newcommand{\infdiv}{D\infdivx}
\DeclarePairedDelimiter{\norm}{\lVert}{\rVert}

% *** SPECIALIZED LIST PACKAGES ***
%
%\usepackage{algorithmic}
% algorithmic.sty was written by Peter Williams and Rogerio Brito.
% This package provides an algorithmic environment fo describing algorithms.
% You can use the algorithmic environment in-text or within a figure
% environment to provide for a floating algorithm. Do NOT use the algorithm
% floating environment provided by algorithm.sty (by the same authors) or
% algorithm2e.sty (by Christophe Fiorio) as IEEE does not use dedicated
% algorithm float types and packages that provide these will not provide
% correct IEEE style captions. The latest version and documentation of
% algorithmic.sty can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithms/
% There is also a support site at:
% http://algorithms.berlios.de/index.html
% Also of interest may be the (relatively newer and more customizable)
% algorithmicx.sty package by Szasz Janos:
% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithmicx/

% *** ALIGNMENT PACKAGES ***
%
%\usepackage{array}
% Frank Mittelbach's and David Carlisle's array.sty patches and improves
% the standard LaTeX2e array and tabular environments to provide better
% appearance and additional user controls. As the default LaTeX2e table
% generation code is lacking to the point of almost being broken with
% respect to the quality of the end results, all users are strongly
% advised to use an enhanced (at the very least that provided by array.sty)
% set of table tools. array.sty is already installed on most systems. The
% latest version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/required/tools/

% IEEEtran contains the IEEEeqnarray family of commands that can be used to
% generate multiline equations as well as matrices, tables, etc., of high
% quality.

% *** SUBFIGURE PACKAGES ***
%\ifCLASSOPTIONcompsoc
%  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
%\else
%  \usepackage[caption=false,font=footnotesize]{subfig}
%\fi
% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
% for subfigure.sty, the latter of which is no longer maintained and is
% incompatible with some LaTeX packages including fixltx2e. However,
% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
% which will override IEEEtran.cls' handling of captions and this will result
% in non-IEEE style figure/table captions. To prevent this problem, be sure
% and invoke subfig.sty's "caption=false" package option (available since
% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
% handling of captions.
% Note that the Computer Society format requires a larger sans serif font
% than the serif footnote size font used in traditional IEEE formatting
% and thus the need to invoke different subfig.sty package options depending
% on whether compsoc mode has been enabled.
%
% The latest version and documentation of subfig.sty can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/subfig/

% *** FLOAT PACKAGES ***
%
%\usepackage{fixltx2e}
% fixltx2e, the successor to the earlier fix2col.sty, was written by
% Frank Mittelbach and David Carlisle. This package corrects a few problems
% in the LaTeX2e kernel, the most notable of which is that in current
% LaTeX2e releases, the ordering of single and double column floats is not
% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
% single column figure to be placed prior to an earlier double column
% figure. The latest version and documentation can be found at:
% http://www.ctan.org/tex-archive/macros/latex/base/

%\usepackage{stfloats}
% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
% the ability to do double column floats at the bottom of the page as well
% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
% LaTeX2e). It also provides a command:
%\fnbelowfloat
% to enable the placement of footnotes below bottom floats (the standard
% LaTeX2e kernel puts them above bottom floats). This is an invasive package
% which rewrites many portions of the LaTeX2e float routines. It may not work
% with other packages that modify the LaTeX2e float routines. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/sttools/
% Do not use the stfloats baselinefloat ability as IEEE does not allow
% \baselineskip to stretch. Authors submitting work to the IEEE should note
% that IEEE rarely uses double column equations and that authors should try
% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
% packages (also by Sigitas Tolusis) as IEEE does not format its papers in
% such ways.
% Do not attempt to use stfloats with fixltx2e as they are incompatible.
% Instead, use Morten Hogholm'a dblfloatfix which combines the features
% of both fixltx2e and stfloats:
%
% \usepackage{dblfloatfix}
% The latest version can be found at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/dblfloatfix/

%\ifCLASSOPTIONcaptionsoff
%  \usepackage[nomarkers]{endfloat}
% \let\MYoriglatexcaption\caption
% \renewcommand{\caption}[2][\relax]{\MYoriglatexcaption[#2]{#2}}
%\fi
% endfloat.sty was written by James Darrell McCauley, Jeff Goldberg and 
% Axel Sommerfeldt. This package may be useful when used in conjunction with 
% IEEEtran.cls'  captionsoff option. Some IEEE journals/societies require that
% submissions have lists of figures/tables at the end of the paper and that
% figures/tables without any captions are placed on a page by themselves at
% the end of the document. If needed, the draftcls IEEEtran class option or
% \CLASSINPUTbaselinestretch interface can be used to increase the line
% spacing as well. Be sure and use the nomarkers option of endfloat to
% prevent endfloat from "marking" where the figures would have been placed
% in the text. The two hack lines of code above are a slight modification of
% that suggested by in the endfloat docs (section 8.4.1) to ensure that
% the full captions always appear in the list of figures/tables - even if
% the user used the short optional argument of \caption[]{}.
% IEEE papers do not typically make use of \caption[]'s optional argument,
% so this should not be an issue. A similar trick can be used to disable
% captions of packages such as subfig.sty that lack options to turn off
% the subcaptions:
% For subfig.sty:
% \let\MYorigsubfloat\subfloat
% \renewcommand{\subfloat}[2][\relax]{\MYorigsubfloat[]{#2}}
% However, the above trick will not work if both optional arguments of
% the \subfloat command are used. Furthermore, there needs to be a
% description of each subfigure *somewhere* and endfloat does not add
% subfigure captions to its list of figures. Thus, the best approach is to
% avoid the use of subfigure captions (many IEEE journals avoid them anyway)
% and instead reference/explain all the subfigures within the main caption.
% The latest version of endfloat.sty and its documentation can obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/endfloat/
%
% The IEEEtran \ifCLASSOPTIONcaptionsoff conditional can also be used
% later in the document, say, to conditionally put the References on a 
% page by themselves.

% *** PDF, URL AND HYPERLINK PACKAGES ***
%
%\usepackage{url}
% url.sty was written by Donald Arseneau. It provides better support for
% handling and breaking URLs. url.sty is already installed on most LaTeX
% systems. The latest version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/url/
% Basically, \url{my_url_here}.

% *** Do not adjust lengths that control margins, column widths, etc. ***
% *** Do not use packages that alter fonts (such as pslatex).         ***
% There should be no need to do such things with IEEEtran.cls V1.6 and later.
% (Unless specifically asked to do so by the journal or conference you plan
% to submit to, of course. )

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}
\bstctlcite{IEEEexample:BSTcontrol}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Uncertainty-aware graph-based multimodal remote sensing classification}
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%
\author{Iain~Rolland\orcidA{},~\IEEEmembership{Student~Member,~IEEE}%
\thanks{I. Rolland is with the Department
of Engineering, University of Cambridge, Cambridge, CB2 1PZ United Kingdom e-mail: imr27@cam.ac.uk.}% <-this % stops a space
\thanks{Manuscript received Month Date, Year; revised Month Date, Year.}}

% note the % following the last \IEEEmembership and also \thanks - 
% these prevent an unwanted space from occurring between the last author name
% and the end of the author line. i.e., if you had this:
% 
% \author{....lastname \thanks{...} \thanks{...} }
%                     ^------------^------------^----Do not want these spaces!
%
% a space would be appended to the last name and could cause every name on that
% line to be shifted left slightly. This is one of those "LaTeX things". For
% instance, "\textbf{A} \textbf{B}" will typeset as "A B" not "AB". To get
% "AB" then you have to do: "\textbf{A}\textbf{B}"
% \thanks is no different in this regard, so shield the last } of each \thanks
% that ends a line with a % and do not let a space in before the next \thanks.
% Spaces after \IEEEmembership other than the last one are OK (and needed) as
% you are supposed to have spaces between the names. For what it is worth,
% this is a minor point as most people would not even notice if the said evil
% space somehow managed to creep in.

% The paper headers
\markboth{Journal of X,~Vol.~Y, No.~Z, June~2021}%
{}
% The only time the second header will appear is for the odd numbered pages
% after the title page when using the twoside option.
% 
% *** Note that you probably will NOT want to include the author's ***
% *** name in the headers of peer review papers.                   ***
% You can use \ifCLASSOPTIONpeerreview for conditional compilation here if
% you desire.

% If you want to put a publisher's ID mark on the page you can do it like
% this:
%\IEEEpubid{0000--0000/00\$00.00~\copyright~2014 IEEE}
% Remember, if you use this you must call \IEEEpubidadjcol in the second
% column for its text to clear the IEEEpubid mark.

% use for special paper notices
%\IEEEspecialpapernotice{(Invited Paper)}

% make the title area
\maketitle

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
TBW.
\end{abstract}

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
TBW.
\end{IEEEkeywords}

% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle

\section{Introduction}
% The very first letter is a 2 line initial drop letter followed
% by the rest of the first word in caps.
% 
% form to use if the first word consists of a single letter:
% \IEEEPARstart{A}{demo} file is ....
% 
% form to use if you need the single drop letter followed by
% normal text (unknown if ever used by IEEE):
% \IEEEPARstart{A}{}demo file is ....
% 
% Some journals put the first two words in caps:
% \IEEEPARstart{T}{his demo} file is ....
% 
% Here we have the typical use of a "T" for an initial drop letter
% and "HIS" in caps to complete the first word.
\IEEEPARstart{T}{he} capability of algorithms to provide accurate measures of confidence and uncertainty is important if they are to be adopted in real-world scenarios where the stakes can be high \cite{Goodman_Flaxman_2017}. Although deep learning methods have provided new state of the art performance on many computer vision tasks \cite{lecun2015deeplearning}, and in many remote sensing tasks \cite{zhang2016deep}, they are often criticised for their lack of explainability \cite{pmlr_v70_guo17a} acting like a black box. Prediction transparency could be improved if models were able express when results can be given with confidence.

The remainder of this paper is organised as follows: Section \ref{sec::related_work} contains a summary of related research into uncertainty-aware remote sensing classification methods, Section \ref{sec::unc_framework} describes the uncertainty framework adopted in the methods presented, Section \ref{sec::networks} details the construction of the graph-based neural networks used, Section \ref{sec::results} presents an analysis of results and Section \ref{sec::conclusion} summarises and draws conclusions as well as suggests areas for future work.

% needed in second column of first page if using \IEEEpubid
%\IEEEpubidadjcol

% An example of a floating figure using the graphicx package.
% Note that \label must occur AFTER (or within) \caption.
% For figures, \caption should occur after the \includegraphics.
% Note that IEEEtran v1.7 and later has special internal code that
% is designed to preserve the operation of \label within \caption
% even when the captionsoff option is in effect. However, because
% of issues like this, it may be the safest practice to put all your
% \label just after \caption rather than within \caption{}.
%
% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
% option should be used if it is desired that the figures are to be
% displayed while in draft mode.
%
%\begin{figure}[!t]
%\centering
%\includegraphics[width=2.5in]{myfigure}
% where an .eps filename suffix will be assumed under latex, 
% and a .pdf suffix will be assumed for pdflatex; or what has been declared
% via \DeclareGraphicsExtensions.
%\caption{Simulation results for the network.}
%\label{fig_sim}
%\end{figure}

% Note that IEEE typically puts floats only at the top, even when this
% results in a large percentage of a column being occupied by floats.

% An example of a double column floating figure using two subfigures.
% (The subfig.sty package must be loaded for this to work.)
% The subfigure \label commands are set within each subfloat command,
% and the \label for the overall figure must come after \caption.
% \hfil is used as a separator to get equal spacing.
% Watch out that the combined width of all the subfigures on a 
% line do not exceed the text width or a line break will occur.
%
%\begin{figure*}[!t]
%\centering
%\subfloat[Case I]{\includegraphics[width=2.5in]{box}%
%\label{fig_first_case}}
%\hfil
%\subfloat[Case II]{\includegraphics[width=2.5in]{box}%
%\label{fig_second_case}}
%\caption{Simulation results for the network.}
%\label{fig_sim}
%\end{figure*}
%
% Note that often IEEE papers with subfigures do not employ subfigure
% captions (using the optional argument to \subfloat[]), but instead will
% reference/describe all of them (a), (b), etc., within the main caption.
% Be aware that for subfig.sty to generate the (a), (b), etc., subfigure
% labels, the optional argument to \subfloat must be present. If a
% subcaption is not desired, just leave its contents blank,
% e.g., \subfloat[].

% An example of a floating table. Note that, for IEEE style tables, the
% \caption command should come BEFORE the table and, given that table
% captions serve much like titles, are usually capitalized except for words
% such as a, an, and, as, at, but, by, for, in, nor, of, on, or, the, to
% and up, which are usually not capitalized unless they are the first or
% last word of the caption. Table text will default to \footnotesize as
% IEEE normally uses this smaller font for tables.
% The \label must come after \caption as always.
%
% \begin{table}[!t]
% % increase table row spacing, adjust to taste
% \renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
% \caption{An Example of a Table}
% \label{table_example}
% \centering
% % Some packages, such as MDW tools, offer better commands for making tables
% % than the plain LaTeX2e tabular which is used here.
% \begin{tabular}{|c||c|}
% \hline
% One & Two\\
% \hline
% Three & Four\\
% \hline
% \end{tabular}
% \end{table}

% Note that the IEEE does not put floats in the very first column
% - or typically anywhere on the first page for that matter. Also,
% in-text middle ("here") positioning is typically not used, but it
% is allowed and encouraged for Computer Society conferences (but
% not Computer Society journals). Most IEEE journals/conferences use
% top floats exclusively. 
% Note that, LaTeX2e, unlike IEEE journals/conferences, places
% footnotes above bottom floats. This can be corrected via the
% \fnbelowfloat command of the stfloats package.
\section{Related work}
\label{sec::related_work}
TBW.
\section{Uncertainty framework}
\label{sec::unc_framework}

\subsection{Subjective Logic}
In order to understand the mapping between Dirichlet distributions and uncertainty estimates, it is first necessary to describe the Subjective Logic (SL) framework. The uncertainty reasoning described by SL takes an evidence-based approach to decision making \cite{DBLP:books/sp/Josang16}. Expressing an opinion using measured quantities of belief allows the distinction to be made between uncertainty due to a lack of evidence (vacuity) or uncertainty due to the presence of conflicting evidence (dissonance). A multinomial opinion, $\omega$, can be expressed as $\omega=\left(\mathbf{b}, u, \mathbf{a}\right)$, where $\mathbf{b}$ is a belief mass vector, the scalar $u$ is the uncertainty mass and $\mathbf{a}$ is the base rate vector. For an output, $\mathbf{y}$, of dimension K
\begin{equation}
    \mathbf{b}\in\mathbb{R}^K,\quad\mathbf{a}\in\mathbb{R}^K,\quad\mathbf{y}\in\mathbb{R}^K.
\end{equation}
A projection of $\omega$ onto a probability distribution can be made according to
\begin{equation}
    P(y=k) = b_k + a_ku.
\label{eq:prob_projection}
\end{equation}
Given that for the base rate vector $\sum_{k=1}^Ka_k=1$, an additivity requirement is described by
\begin{equation}
    u+\sum_{k=1}^K b_k=1.
\end{equation}

\subsection{Dirichlet mapping}
If $\mathbf{p}$ is a K-dimensional random vector containing the probability of belonging to each output class, and $\boldsymbol{\alpha}$ is the strength vector which parameterizes the Dirichlet distribution, the probability density function of the Dirichlet is given by
\begin{equation}
    \textrm{Dir}(\mathbf{p}|\boldsymbol{\alpha})= \frac{\Gamma(\sum_{k=1}^K\alpha_k)}{\prod_{k=1}\alpha_k}\prod_{k=1}^Kp_k^{\alpha_k-1},
\end{equation}
where $\Gamma()$ is the gamma function. The distribution's expected value is given by
\begin{equation}
    \mathbb{E}\left[\textrm{Dir}(p_k\vert\boldsymbol{\alpha})\right]=\frac{\alpha_k}{\sum_{k=1}^K\alpha_k}.
\label{eq:expected_dir}
\end{equation}
If we allow the uncertainty mass and base rates to be given by
\begin{equation}
    u=\frac{K}{\sum_{k=1}^K\alpha_k}=\frac{K}{S}
\end{equation}
and
\begin{equation}
    a_k=1/K, \forall k
\end{equation}
respectively, where $S$ refers to the Dirichlet strength, then by equating the probability projection of (\ref{eq:prob_projection}) with the expected value of the Dirichlet distribution given by (\ref{eq:expected_dir}), the expression for the belief mass can be obtained as
\begin{equation}
    b_k = \frac{\alpha_k-1}{S},
\end{equation}
which completes the mapping from Dirichlet distribution to SL opinion.
\subsection{Uncertainty measures}
From the definitions of the evidential uncertainties presented in \cite{8455454}, the measures of vacuity and dissonance have been adopted. The measure of vacuity uncertainty is simply given by the uncertainty mass, i.e.
\begin{equation}
    vac(\omega)\equiv u = \frac{K}{S},
\label{eq::vacuity}
\end{equation}
and the measure of dissonance uncertainty is given by
\begin{equation}
    diss(\omega)=\sum_{i=1}^K\left(\frac{b_i\sum_{j\neq i}b_j\textrm{Bal}(b_j,b_i)}{\sum_{j\neq i}b_j}\right),
\end{equation}
where $\textrm{Bal}()$ is a function which gives the relative balance between two belief masses, defined by
\begin{equation}
    \textrm{Bal}(b_j,b_i)=\begin{cases}1-\frac{\vert b_i-b_j\vert}{b_i+b_j},&\text{if } b_i+b_j\neq0,\\
    0,&\text{otherwise.}\end{cases}
\end{equation}

In order assess the relative ability of evidential uncertainties to express different types of doubt, three commonly used probabilistic measures of uncertainty (aleatoric, epistemic and entropy) are computed to provide comparisons. For a Bayesian model with inputs, outputs and parameters denoted $x$, $y$ and $\boldsymbol{\theta}$ respectively, the posterior which will be approximated is $p(\boldsymbol{\theta}\vert\mathcal{D})$, where $\mathcal{D}$ is the observed dataset. The total entropy, made up of both aleatoric and epistemic uncertainty \cite{pmlr_v80_depeweg18a} is given by
\begin{equation}
    \mathcal{H}\left(\mathbb{E}_{p(\boldsymbol{\theta}\vert \mathcal{D})}\left[p(y\vert x;\boldsymbol{\theta}\right]\right),
\end{equation}
where $\mathcal{H}()$ computes the differential entropy of a distribution. Aleatoric uncertainty, which accounts for noise inherent to the data observations and cannot be reduced with extra samples \cite{NIPS2017_2650d608}, is given by
\begin{equation}
        \mathbb{E}_{p\left(\boldsymbol{\theta}\vert \mathcal{D}\right)}\left[\mathcal{H}(p(y\vert x; \boldsymbol{\theta}))\right].
\end{equation}
The epistemic uncertainty, therefore, is given by the difference between these two quantities
\begin{equation}
        \mathcal{H}\left(\mathbb{E}_{p(\boldsymbol{\theta}\vert \mathcal{D})}\left[p(y\vert x;\boldsymbol{\theta}\right]\right)-\mathbb{E}_{p\left(\boldsymbol{\theta}\vert \mathcal{D}\right)}\left[\mathcal{H}(p(y\vert x; \boldsymbol{\theta}))\right].
\label{eq::epistemic}
\end{equation}
In order to compute the above expressions for aleatoric and epistemic uncertainty, the posterior distribution over models is approximated by samples obtained using dropout inference \cite{pmlr_v48_gal16} as is described in Section \ref{sec::dropout_bayesian}.

\section{Networks}
\label{sec::networks}
\subsection{Graph convolutional networks}
The problem involves a graph with $N$ nodes described by an adjacency matrix $\mathbf{A}\in\mathbb{R}^{N\times N}$ and node features $\mathbf{X}\in\mathbb{R}^{N\times C}$, where $C$ denotes the number of channels in the input which describes each node. The graph's degree matrix, $\mathbf{D}\in\mathbb{R}^{N\times N}$, is a diagonal matrix with elements given by $\mathbf{D}_{ii}=\sum_j\mathbf{A}_{ij} $. For brevity, the tilde operator is used to represent the inclusion of self-connection edges in the graph, i.e. $\tilde{\mathbf{A}}=\mathbf{A}+\mathbf{I}$ and $\tilde{\mathbf{D}}=\mathbf{D}+\mathbf{I}$.
Using the first-order approximation to spectral graph convolution derived by \cite{KipfW17}, the graph convolutional layer is given by
\begin{equation}
    \mathbf{Z}^{(l+1)}=\sigma\left(\tilde{\mathbf{D}}^{-\frac{1}{2}}\tilde{\mathbf{A}}\tilde{\mathbf{D}}^{-\frac{1}{2}}\mathbf{Z}^{(l)}\boldsymbol{W}^{(l)}\right),
\label{eq::gcn_layer}
\end{equation}
where $\mathbf{Z}^{(l)}$, $\mathbf{Z}^{(l+1)}$ and $\boldsymbol{W}^{(l)}$ are the inputs, outputs and weights of the $\textrm{l}^\textrm{th}$ layer respectively, and $\sigma()$ is a non-linear activation function. For the first layer, the weights are $\boldsymbol{W}^{(0)}\in\mathbb{R}^{C\times F}$ and $\mathbf{Z}^{(0)} = \mathbf{X}\in\mathbb{R}^{N\times C}$ where $F$ is the number of features in the layer's output (a hyperparameter of the layer).
Models referred to as graph convolutional networks (GCNs) from henceforth will refer to a model which consists of two of these layers used in sequence, the first using the rectified linear unit (ReLU) activation function, the second using a softmax activation.
\subsection{Subjective models}
In order to obtain models which will give node-level Dirichlet distribution parameters, the softmax output activation function used in a GCN is substituted for a ReLU function. In this way, the model is trained to output non-negative evidence contributions, $\mathbf{E}\in\mathbb{R}^{N\times K}$, where $\mathbf{E}_{i} = \boldsymbol{\alpha}_{i}-\mathbf{1}$ and $\boldsymbol{\alpha}_{i}$ refers to the K-dimensional concentration parameters of the $\text{i}^\text{th}$ node. In order to train an evidential model, the loss function is made up of two components; a squared error term which is minimised in order to classify a greater proportion of the nodes correctly and a variance term which is minimized to incentivize the model to provide confident predictions where possible. This loss, $\mathcal{L}(\boldsymbol{\theta})$, is given by
\begin{equation}
\begin{split}
    \mathcal{L}(\boldsymbol{\theta})&=\sum_{i\in\mathbb{L}}\sum_k \left[(p_{ik}-y_{ik})^2+\text{Var}(p_{ik})\right],\\
    &=\sum_{i\in\mathbb{L}}\sum_k \left[(p_{ik}-y_{ik})^2+\frac{\left(\frac{\alpha_{ik}}{S_i}\right)\left(1-\frac{\alpha_{ik}}{S_i}\right)}{S_i-K}\right],
\end{split}
\label{eq:core_loss}
\end{equation}
where $i\in\mathbb{L}$ refers to the fact that the loss is computed using a sum only over nodes in the training set, $\mathbb{L}$. Models trained with such an output activation and loss function will be denoted using the `S-' prefix in order to indicate they provide subjective predictions, e.g. S-GCN.
\subsection{Dropout inference as a Bayesian approximation}
\label{sec::dropout_bayesian}
It has been shown that a model with dropout can be considered to represent the posterior distribution over models \cite{pmlr_v48_gal16}. The dropouts are used to represent stochasticity in the model parameters \cite{C9SC01992H}. A given combination of dropouts can be considered to represent a model sampled from the approximate posterior, $q(\boldsymbol{\theta})$, with the actual posterior distribution of models being $p(\boldsymbol{\theta}|\mathcal{D})$. Monte Carlo sampling can be used to approximately compute quantities such as the term $\mathbb{E}_{p\left(\boldsymbol{\theta}\vert \mathcal{D}\right)}\left[\mathcal{H}(p(y\vert x; \boldsymbol{\theta}))\right]$ in (\ref{eq::epistemic}) allowing the aleatoric and epistemic uncertainty to be calculated. This can be done using the approximation 
\begin{equation}
    \mathbb{E}_{p\left(\boldsymbol{\theta}\vert \mathcal{D}\right)}\left[\mathcal{H}(p(y\vert x; \boldsymbol{\theta}))\right]\approx\frac{1}{M}\sum_{m=1}^M \mathcal{H}\left(p(y\vert x; \boldsymbol{\theta}^m)\right),
\end{equation}
where $\boldsymbol{\theta}^m\sim q(\boldsymbol{\theta})$ is a model sampled by performing dropout inference. When this technique has been used, the model name represents this using a `B' in its name, e.g. S-BGCN, showing that this Bayesian approximation has been used. The Drop-GCN model, which is used for benchmarking the subjective methods, refers to the same technique when applied to a `vanilla' GCN.

\subsection{Convergence assistance techniques}
In order to assist the convergence of subjective models, two additional assistance techniques have been used: teacher knowledge distillation and the use of a Dirichlet prior. These methods have been shown to allow subjective models to provide better uncertainty estimates \cite{Zhao2020}.
\subsubsection{Teacher knowledge distillation}
By training a non-subjective model in advance, its outputs, $\hat{p}_{ik}$, can be used in order to encourage the subjective model to converge to node Dirichlet distributions with $\mathbb{E}[p_{ik}]$ which are close to the teacher's deterministic estimates. This is achieved using an additional term in the loss function,
\begin{equation}
    \mathcal{L}_{\text{``-T''}}(\boldsymbol{\theta})=\sum_i\sum_k\left(\hat{p}_{ik}\log\frac{\hat{p}_{ik}}{\mathbb{E}[p_{ik}]}\right),
\end{equation}
which corresponds to the summation of KL-divergence terms between the teacher output probability and the expected value of the subjective model's Dirichlet distribution for each node, $\sum_i\infdiv{\hat{p}_{ik}}{\mathbb{E}[p_{ik}]}$. Notice that this sum is computed over all nodes as opposed to just the nodes in $\mathbb{L}$. Models trained using a teacher are denoted using the ``-T'' suffix e.g. a S-BGCN-T model would indicate that a pre-trained GCN was used as a teacher in order to assist the training convergence of a subjective graph convolutional model.
\subsubsection{Dirichlet prior}
A second convergence assistance technique which can be used involves the use of a Dirichlet prior, $\hat{\boldsymbol{\alpha}}$. The exact method chosen to provide $\hat{\boldsymbol{\alpha}}$ will depend on the nature of the problem but we will assume nodes which are nearby in the graph are more likely to belong to the same output class than nodes which are far apart, a property known as homophily \cite{huang2021combining}. Using this assumption, we can use the computed distances on the graph in order to assign contributions of evidence from observed node labels to the other nodes in the graph using a function of our choosing. If $d_{ij}$ denotes the shortest path distance between a given node, indexed by $i$ and an observed node, indexed by $j$, then the amount of evidence contributed to suggest that the $\text{i}^\text{th}$ node belongs to the $\text{k}^\text{th}$ class is given by
\begin{equation}
    h_{ik}(y_j,d_{ij})=
    \begin{cases}
    \frac{1}{\sqrt{2\pi\sigma^2}}\exp{\left(\frac{-d_{ij}^2}{2\sigma^2}\right)}, & \text{if } y_{jk}=1,\\
    0, & \text{otherwise},
    \end{cases}
\end{equation}
where $\sigma$ is a scale parameter which controls the order of distance magnitude over which evidence will propagate in the prior. The total evidence to suggest the $\text{i}^\text{th}$ node belongs to the $\text{k}^\text{th}$ class, $e_{ik}$ can be found by summing these contributions over the nodes in the training set such that the element in the prior is given by 
\begin{equation}
    \hat{\boldsymbol{\alpha}}_{ik}=1+e_{ik}=1+\sum_{j\in\mathbb{L}}h_{ik}(y_j, d_{ij}).
\end{equation}
A node which is far from all observed nodes, i.e. $h_{ik}(y_j,d_{ij})\approx0, \forall j\in\mathbb{L}$, will mean that $\hat{\boldsymbol{\alpha}}_{i}\approx\mathbf{1}$. The prior's Dirichlet strength for the $\text{i}^\text{th}$ node, $\hat{S}_i$, will therefore be approximately $K$ and the node's vacuity, as given by (\ref{eq::vacuity}), will be approximately 1. On the other hand, a node which is near to many observed nodes will have large $\hat{S}_i$ and node vacuity will be small. The KL-divergence between the Dirichlet distribution of the prior and the model output can be incorporated into the loss function using the term
\begin{equation}
    \mathcal{L}_{\text{``-K''}}(\boldsymbol{\theta})=\sum_i\infdiv{\text{Dir}(\mathbf{p}_i\vert\boldsymbol{\alpha}_i)}{\text{Dir}(\hat{\mathbf{p}}_i\vert\hat{\boldsymbol{\alpha}}_i)},
\label{eq::teacher_loss}
\end{equation}
which can be incorporated into the total loss. Models trained using a prior are denoted using the ``-K'' suffix e.g. a S-BGCN-K model would indicate that the graph convolutional network was trained with a loss function using a weighted combination of the loss in (\ref{eq:core_loss}) and the term described in (\ref{eq::teacher_loss}).

Table \ref{loss_table} shows how these convergence assistance techniques can be weighted and combined in various permutations to provide a total loss function, $\mathcal{L}_\text{total}(\boldsymbol{\theta})$, as well as the model name abbreviations used to denote which combination has been used. The coefficients $\lambda_{\text{``-T''}}$ and $\lambda_{\text{``-K''}}$ are used to control the relative importance of the teacher network and the Dirichlet prior respectively against the importance of the subjective loss function given in (\ref{eq:core_loss}). These are considered hyperparameters of the model which are to be tuned during training.

\begin{table}
\renewcommand{\arraystretch}{1.5}
\caption{Loss function components and their weighting coefficients for different model types}
\label{loss_table}
\centering
\begin{tabular}{cc}
\hline
\bfseries Model name & \bfseries $\mathcal{L}_{\text{total}}(\boldsymbol{\theta})$\\
\hline
S-BGCN & $\mathcal{L}(\boldsymbol{\theta})$ \\
S-BGCN-T & $\mathcal{L}(\boldsymbol{\theta})+\lambda_{\text{``-T''}}\mathcal{L}_{\text{``-T''}}(\boldsymbol{\theta})$ \\
S-BGCN-K & $\mathcal{L}(\boldsymbol{\theta})+\lambda_{\text{``-K''}}\mathcal{L}_{\text{``-K''}}(\boldsymbol{\theta})$ \\
S-BGCN-T-K & $\mathcal{L}(\boldsymbol{\theta})+\lambda_{\text{``-T''}}\mathcal{L}_{\text{``-T''}}(\boldsymbol{\theta})+\lambda_{\text{``-K''}}\mathcal{L}_{\text{``-K''}}(\boldsymbol{\theta})$ \\
\hline
\end{tabular}
\end{table}

\section{Results and Analysis}
\label{sec::results}
\subsection{Data}
A subsection of the 2018 IEEE GRSS Data Fusion Challenge dataset was selected for the purposes of validating the described methods as a means for obtaining uncertainty aware classifications. The modes of data collected come from three sensor types: LiDAR, optical and hyperspectral (HS). The LiDAR data was provided at $0.5$ m resolution, the same resolution as the ground truth labels (GT). In order to simplify analysis, the optical data (which was provided at $0.05$ m resolution) and the HS data (which was provided at $1.0$ m resolution) were bilinearly resampled to obtain $0.5$ m resolution across inputs and outputs.

The graph was constructed with each $0.5$ m $\times$ $0.5$ m pixel representing a node in the graph. Each node has a 52-dimensional feature vector (produced by stacking 3 optical channels, 48 HS channels and 1 LiDAR channel) describing it. The graph edges are computed using a $k$-nearest neighbors algorithm with two nodes receiving an edge connecting them if either node was one of the $k$ nodes which were nearest the other. This produces a graph which is both undirected and unweighted. The graph, which contains approximately 2.16 million nodes, was computed with $k=15$.

The ground truth labels describe 20 different urban land cover/land use classes as well as an unlabelled state, described as Unclassified. The exact types and abundances of these classes can be found in Table \ref{tab::classes}. The classes which do not appear in the subsection of the dataset but exist within the wider GT are included for completeness.

\begin{table}
% \renewcommand{\arraystretch}{1.5}
\caption{Land cover/Land use classes in selected subsection of Houston dataset ground truth}
\label{tab::classes}
\centering
\begin{tabular}{NNcZ}
\hline
\bfseries Class Value & \bfseries Legend Color & \bfseries Class Name & \bfseries Number of Nodes (total)\\
\hline
$0$ & \colorbox[rgb]{0.0,0.0,0.0}{\textcolor{white}{\phantom{A}}} & Unclassified & $1302595$\\
$1$ & \colorbox[rgb]{0.0,1.0,0.03}{\textcolor{white}{\phantom{A}}} & Healthy grass & $10120$ \\
$2$ & \colorbox[rgb]{0.21, 0.69, 0.15}{\textcolor{white}{\phantom{A}}} & Stressed grass & $16332$ \\
$3$ & \colorbox[rgb]{0.53, 0.73, 0.57}{\textcolor{white}{\phantom{A}}} & Artificial turf & $0$ \\
$4$ & \colorbox[rgb]{0.  , 0.47, 0.08}{\textcolor{white}{\phantom{A}}} & Evergreen trees & $38288$ \\
$5$ & \colorbox[rgb]{0.  , 0.3 , 0.}{\textcolor{white}{\phantom{A}}} & Deciduous trees & $3082$ \\
$6$ & \colorbox[rgb]{0.75, 0.48, 0.08}{\textcolor{white}{\phantom{A}}} & Bare earth & $0$ \\
$7$ & \colorbox[rgb]{0.  , 0.89, 0.89}{\textcolor{white}{\phantom{A}}} & Water & $332$ \\
$8$ & \colorbox[rgb]{0.98, 0.98, 0.98}{\textcolor{white}{\phantom{A}}} & Residential buildings & $12417$ \\
$9$ & \colorbox[rgb]{0.94, 0.76, 0.92}{\textcolor{white}{\phantom{A}}} & Non-residential buildings & $587141$ \\
$10$ & \colorbox[rgb]{1.  , 0.35, 0.36}{\textcolor{white}{\phantom{A}}} & Roads & $68831$ \\
$11$ & \colorbox[rgb]{0.64, 0.64, 0.64}{\textcolor{white}{\phantom{A}}} & Sidewalks & $96020$ \\
$12$ & \colorbox[rgb]{0.36, 0.36, 0.36}{\textcolor{white}{\phantom{A}}} & Crosswalks & $3584$ \\
$13$ & \colorbox[rgb]{0.79, 0.  , 0.01}{\textcolor{white}{\phantom{A}}} & Major thoroughfares & $17181$ \\
$14$ & \colorbox[rgb]{0.54, 0.  , 0.04}{\textcolor{white}{\phantom{A}}} & Highways & $0$ \\
$15$ & \colorbox[rgb]{1.  , 0.65, 0.07}{\textcolor{white}{\phantom{A}}} & Railways & $0$ \\
$16$ & \colorbox[rgb]{1.,1.,0.}{\textcolor{white}{\phantom{A}}} & Paved parking lots & $7677$ \\
$17$ & \colorbox[rgb]{0.92, 0.44, 0.}{\textcolor{white}{\phantom{A}}} & Unpaved parking lots & $0$ \\
$18$ & \colorbox[rgb]{0.98, 0.  , 1.}{\textcolor{white}{\phantom{A}}} & Cars & $0$ \\
$19$ & \colorbox[rgb]{0.  , 0.  , 1.}{\textcolor{white}{\phantom{A}}} & Trains & $0$ \\
$20$ & \colorbox[rgb]{0.49, 0.76, 0.8}{\textcolor{white}{\phantom{A}}} & Stadium seats & $0$ \\
\hline
\end{tabular}
\end{table}

\begin{figure}[!t]
\centering
\includegraphics[width=\columnwidth]{figures/gt.jpg}
\caption{Ground truth data with colors depicting classes as defined in Table \ref{tab::classes}. The subset area of the 2018 IEEE GRSS Data Fusion Challenge dataset covers the region with lower-left coordinate 272956, 3289689 and upper-right coordinate 273856, 3290290 (coordinates given in the NAD83 / UTM zone 15N Coordinate Reference System).}
\label{fig::gt}
\end{figure}

In order to divide the annotations into a training, a validation and a test set, any adjacent pixels with the same label were considered part of one contiguous label block. Before randomly allocating these contiguous label blocks into the different sets, the blocks were separated along grid lines in order to prevent any particularly large contiguous blocks from skewing its set into having an over-representation of that class (see Figure \ref{fig::dataset_split} for a visual depiction of a random split). The set of contiguous blocks obtained after splitting along these arbitrary grid lines were then randomly allocated into training, validation and test sets with proportions of 40\%, 30\% and 30\% respectively. This method of assigning contiguous blocks into a split together as opposed to randomly splitting pixels was done so as to reduce the number of strongly correlated samples (due to local spatial correlations in the input vectors) across the test/validation/test sets which would come with having pixels of immediate proximity split into different sets.

\begin{figure}[!t]
\centering
\includegraphics[width=\columnwidth]{figures/dataset_split.jpg}
\caption{RGB data channels with overlaying colors used to depict a random dataset split with the red, green and blue overlay colors representing training, validation and test set pixels respectively.}
\label{fig::dataset_split}
\end{figure}

\subsection{Network training and hyperparameters}
Models were implemented and trained using the TensorFlow library \cite{tensorflow2015_whitepaper}. In order to handle the imbalance of classes in the dataset, sample weighting was used. Samples were given weights which were inversely proportional to the number of total samples of each class in the training set. These weights were used when computing the loss during training such that the loss related to nodes belonging to under-represented classes were given an increased influence over parameter updates and vice versa.

All GCN-based models were constructed using a dropout layer (dropout probability $0.5$), a graph convolutional layer, as described in (\ref{eq::gcn_layer}), a second dropout layer (dropout probability $0.5$) and a second graph convolutional layer with the relevant output activation function. The kernel weights of the first graph convolutional layer were regularized using an $L_2$ penalization. Where dropout inference has been used, the number of samples taken, $M$, was 100.

Hyperparameters including the learning rate, the $L_2$ regularization coefficient and the number of GCN layer output features, $F$, were selected via a grid-search method. Where used, $\lambda_{\text{``-T''}}$ and $\lambda_{\text{``-K''}}$ were also found using a grid-search.

Learning was performed for a maximum of 400 epochs, but was stopped early if the validation loss failed to decrease further for 60 consecutive epochs. If stopped early, model weights were returned to the settings which provided the lowest validation set loss upon the termination of training.

Each test was performed for different random dataset splits and model weight initializations in order to obtain mean and standard deviation measures of performance.

Benchmark models presented include the `vanilla' GCN (which can provide uncertainty via entropy) and the Drop-GCN which is a GCN where dropout inference has been applied in order to produce estimates of aleatoric and epistemic uncertainty in addition to entropy.

\subsection{Misclassification detection}

Given that model uncertainties should provide a measure of the confidence which can be had about a model's predictions, a worthwhile estimate of uncertainty should be able to distinguish model misclassifications from accurate classifications. In order to measure a uncertainty output's ability to separate misclassifications, an experiment which produces a receiver operating characteristic (ROC) curve can be performed. By plotting the true positive rate (the proportion of misclassified nodes correctly flagged as misclassifications) against the false positive rate (the proportion of correctly classified nodes which were incorrectly flagged as misclassified) for various threshold values of the uncertainty metric, the ROC curve can be used to illustrate how well the uncertainty metric can separate the model's misclassifications. The area under the ROC curve (AUROC) can be used as a single numerical representation of the ROC figure, where a perfect discriminator would have an AUROC of $1.0$. An alternative measure of how well the uncertainty metric separates misclassified nodes is provided by considering the precision-recall (PR) curve, which plots the proportion of nodes which were detected as misclassifications which were actually misclassified nodes (precision) against the proportion of actually misclassified nodes which were detected as misclassifications (recall). Again, the area under the PR curve (AUPR) can be used as a single numerical summary of this relationship, and a perfect discriminator would have an AUPR of $1.0$.

Models of each type described (as well as benchmark models) were trained and their outputs analysed in order to assess which model types as well as which of their uncertainty measures were best able to distinguish misclassified nodes. This was done by comparing the output labels for the test nodes to the respective test nodes' GT labels in order to separate correctly and incorrectly classified nodes. Each uncertainty metric in turn was then used to measure ROC and PR curve values for various threshold uncertainty metric values and the area under these curves subsequently calculated.

The AUROC and AUPR values measured for the task of misclassification detection can be seen in Table \ref{tab::misc_auroc} and Table \ref{tab::misc_aupr} respectively.

\begin{table}[!t]
\renewcommand{\arraystretch}{1.3}
\caption{Misclassification detection: Ability of each uncertainty type to detect misclassifications (measured by the AUROC metric).}
\label{tab::misc_auroc}
\small
\begin{center}
\begin{tabular}{Lccccc}
\hline
\multirow{2}{*}{Model}  & \multicolumn{5}{c}{AUROC}             \\
      & Vac. & Dis. & Ale. & Epi. & Ent. \\ \hline 
S-BGCN-T-K (superpixel prior) & $0.676$ & $0.801$ &$0.792$&$0.509$&$0.798$    \\
S-BGCN-T-K (pixel prior) & $0.908$ & $0.840$ &$0.905$&$0.451$&$\mathbf{0.912}$ \\
S-BGCN-T & $0.729$ & $0.834$ &$0.869$&$0.618$&$0.861$ \\ 
S-BGCN & $0.760$ & $0.877$ &$0.894$&$0.623$&$0.886$ \\ 
S-GCN & $0.729$ & $0.842$ &-&-&$0.859$ \\ 
S-MLP &$0.845$&$0.904$&-&-&$0.909$ \\
GCN & - & - &-&-&$0.887$ \\ 
Drop-GCN & - & - &$0.897$&$0.552$&$0.887$ \\ \hline
\end{tabular}
\end{center}
\end{table}

\begin{table}[!t]
\renewcommand{\arraystretch}{1.3}
\caption{Misclassification detection: Ability of each uncertainty type to detect misclassifications (measured by the AUPR metric).}
\label{tab::misc_aupr}
\small
\begin{center}
\begin{tabular}{Lccccc}
\hline
\multirow{2}{*}{Model}  & \multicolumn{5}{c}{AUPR}             \\
      & Vac. & Dis. & Ale. & Epi. & Ent. \\ \hline 
S-BGCN-T-K (superpixel prior) & $0.352$&$0.398$&$0.467$&$0.237$&$0.474$ \\
S-BGCN-T-K (pixel prior) & $0.659$&$0.545$&$0.649$&$0.206$&$\mathbf{0.672}$ \\
S-BGCN-T & $0.451$&$0.484$&$0.591$&$0.278$&$0.579$ \\ 
S-BGCN & $0.489$ & $0.558$  &$0.633$&$0.268$&$0.616$ \\ 
S-GCN & $0.472$ & $0.538$  &-&-&$0.595$ \\ 
S-MLP & $0.417$&$0.566$&-&-&$0.616$ \\
GCN & - & -  &-&-&$0.606$ \\ 
Drop-GCN & - & -  & $0.619$&$0.243$&$0.600$ \\ \hline
\end{tabular}
\end{center}
\end{table}

The S-BGCN-T-K model trained using the pixel prior achieves the highest ranked misclassification detection performance, with the uncertainty measured by entropy providing the best distinguishing metric, with AUROC and AUPR of $0.912$ and $0.672$ respectively, closely followed by the performance achieved by the measures of vacuity (AUROC and AUPR of $0.908$ and $0.659$ respectively) and aleatoric uncertainty (AUROC and AUPR of $0.905$ and $0.649$ respectively). The performance seen for the S-BGCN-T-K model trained using the superpixel prior is markedly lower, with its best-detecting uncertainty metrics (dissonance and aleatoric uncertainty) not exceeding AUROC and AUPR of $0.801$ and $0.467$ respectively.

\subsection{Out of distribution detection}

A lack of confidence held about the model's prediction might also arise if it receives an input which belongs to a distribution other than the distributions seen during training. The relative inability of neural networks' to successfully extrapolate beyond the support of the training data is a well-known weakness of these methods \cite{NIPS2017_9ef2ed4b}. By training models using only a subset of the classes provided by the GT, with the other classes acting as out of distribution (OOD) samples, an analysis of whether the uncertainty metrics are capable of distinguishing OOD nodes can be performed. Using the same approach as described for misclassification detection, the AUROC and AUPR can be calculated for each uncertainty output provided by each model type, in order to determine the relative performance of the respective metrics for this task.

In the results presented, two classes were randomly selected to act as OOD. This was repeated 10 times, with two new randomly sampled classes selected for each training and evaluation loop in order that the variation in OOD detection performance due to the nature of the classes selected as OOD could be averaged out and the mean and standard deviation of performance presented. Each model type was assessed over the same 10 sampled OOD class pairs for fairness. The AUROC and AUPR values measured can be found in Table \ref{tab::ood_auroc} and Table \ref{tab::ood_aupr} respectively.

\begin{table*}[!t]
\renewcommand{\arraystretch}{1.3}
\caption{OOD detection: Ability of each uncertainty type to detect OOD nodes (measured by the AUROC metric). Values shown represent the mean $\pm$ standard deviation.}
\label{tab::ood_auroc}
\small
\begin{center}
\begin{tabular}{Lccccc}
\hline
\multirow{2}{*}{Model}  & \multicolumn{5}{c}{AUROC}             \\
      & Vac. & Dis. & Ale. & Epi. & Ent. \\ \hline 
S-BGCN-T-K (superpixel prior) & $0.839\pm0.092$ & $0.691\pm0.173$ &$0.831\pm0.079$&$0.268\pm0.180$&$0.833\pm0.076$    \\           
S-BGCN-T-K (pixel prior) & $\mathbf{0.882\pm0.085}$ & $0.605\pm0.197$ &$0.877\pm0.089$&$0.193\pm0.107$&$0.878\pm0.089$    \\        
S-BGCN-T & $0.588\pm0.147$ & $0.664\pm0.133$ &$0.593\pm0.188$&$0.396\pm0.096$&$0.578\pm0.186$    \\ 
S-BGCN & $0.586\pm0.147$ & $0.666\pm0.132$ &$0.596\pm0.193$&$0.401\pm0.092$&$0.580\pm0.191$    \\ 
S-GCN & $0.580\pm0.145$ & $0.650\pm0.120$ &-&-&$0.586\pm0.181$    \\ 
S-MLP & $0.767\pm0.152$ & $0.805\pm0.114$ &-&-&$0.787\pm0.125$    \\   
GCN & - & - &-&-&$0.538\pm0.188$    \\ 
Drop-GCN & - & - &$0.541\pm0.185$&$0.420\pm0.161$&$0.538\pm0.187$    \\ \hline
\end{tabular}
\end{center}
\end{table*}

\begin{table*}[!t]
\renewcommand{\arraystretch}{1.3}
\caption{OOD detection: Ability of each uncertainty type to detect OOD nodes (measured by the AUPR metric). Values shown represent the mean $\pm$ standard deviation.}
\label{tab::ood_aupr}
\small
\begin{center}
\begin{tabular}{Lccccc}
\hline
\multirow{2}{*}{Model}  & \multicolumn{5}{c}{AUPR}             \\
      & Vac. & Dis. & Ale. & Epi. & Ent. \\ \hline 
S-BGCN-T-K (superpixel prior) &$0.234\pm0.252$&$0.142\pm0.185$&$0.214\pm0.249$&$0.099\pm0.227$&$0.212\pm0.251$    \\   
S-BGCN-T-K (pixel prior) &$\mathbf{0.318\pm0.289}$&$0.132\pm0.184$&$0.316\pm0.306$&$0.082\pm0.178$&$0.316\pm0.306$    \\        
S-BGCN-T &$0.128\pm0.187$&$0.137\pm0.192$&$0.148\pm0.211$&$0.095\pm0.193$&$0.143\pm0.208$    \\ 
S-BGCN & $0.127\pm0.186$ & $0.139\pm0.190$  &$0.150\pm0.213$&$0.095\pm0.195$&$0.145\pm0.209$    \\ 
S-GCN & $0.125\pm0.185$ & $0.130\pm0.191$  &-&-&$0.143\pm0.207$    \\ 
S-MLP & $0.245\pm0.214$ & $0.233\pm0.170$ &-&-&$0.219\pm0.201$    \\   
GCN & - & -  &-&-&$0.116\pm0.179$    \\ 
Drop-GCN & - & -  & $0.116\pm0.179$&$0.115\pm0.257$&$0.116\pm0.179$    \\ \hline
\end{tabular}
\end{center}
\end{table*}

As for the task of misclassification detection, the S-BGCN-T-K model trained using the pixel prior is also the highest ranked model for the task of OOD detection. Its measure of vacuity uncertainty provided the best distinguishing metric, with mean AUROC and AUPR of $0.882$ and $0.318$ respectively, closely followed by performance from the measures of entropy (AUROC and AUPR of $0.878$ and $0.316$ respectively) and aleatoric uncertainty (AUROC and AUPR of $0.877$ and $0.316$ respectively). While competitive performance was observed across a number of the model types trained for the task of misclassification detection, in the task of OOD detection the performance of the S-BGCN-T-K model trained using the pixel prior stands out above others. This highlights the importance of describing a meaningful prior in advance for the purposes of achieving improved uncertainty estimates. While the S-BGCN-T-K model trained using the superpixel prior does not detect OOD nodes quite so successfully, it still seems to benefit from the use of the prior as it achieves next-best performance (with its measure of vacuity giving a mean AUROC and AUPR of $0.839$ and $0.234$ respectively), perhaps also alongside the S-MLP (with its measure of dissonance giving a mean AUROC and AUPR of $0.805$ and $0.233$ respectively).

The fact that vacuity is the uncertainty measure which best distinguishes OOD nodes for either form of S-BGCN-T-K model reflects intuition. Since vacuity measures the absence of evidence for a prediction, it is natural to expect that it would better distinguish OOD nodes for which vacuity is likely higher.

\section{Conclusion}
\label{sec::conclusion}

The misclassification and OOD detection performance of the S-BGCN-T-K presented represents a promising avenue for uncertainty-aware learning. The uncertainties which are produced by this model can be used to better distinguish misclassified nodes and OOD nodes than any of the other methods which are presented. Models which are capable of better quantifying confidence in this way are important for real-world applications where the consequences of misplaced model certainty can be high-stake.

The improved estimate of uncertainty obtained through the use of a prior is shown in the S-BGCN-T-K results, with equivalent models which do not use a prior, e.g. S-BGCN-T, producing uncertainty measures which cannot identify misclassified or OOD nodes as successfully. In order to distinguish misclassifications, the S-BGCN-T-K model measures of vacuity, aleatoric uncertainty or entropy all provide near-best performance. For the task of identifying nodes which come from a distribution other than the distributions on which the model was trained, the measure of vacuity stands out as the uncertainty metric which does this most successfully.

% if have a single appendix:
%\appendix[Proof of the Zonklar Equations]
% or
%\appendix  % for no appendix heading
% do not use \section anymore after \appendix, only \section*
% is possibly needed

% use appendices with more than one appendix
% then use \section to start each appendix
% you must declare a \section before using any
% \subsection or using \label (\appendices by itself
% starts a section numbered zero.)
%

% use section* for acknowledgment
\section*{Acknowledgment}

The authors would like to thank...

% Can use something like this to put references on a page
% by themselves when using endfloat and the captionsoff option.
\ifCLASSOPTIONcaptionsoff
  \newpage
\fi

% trigger a \newpage just before the given reference
% number - used to balance the columns on the last page
% adjust value as needed - may need to be readjusted if
% the document is modified later
%\IEEEtriggeratref{8}
% The "triggered" command can be changed if desired:
%\IEEEtriggercmd{\enlargethispage{-5in}}

% references section

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
\bibliography{bibtex/bib/IEEEabrv, bibtex/bib/imrolland}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
% \begin{thebibliography}{1}

% \bibitem{IEEEhowto:kopka}
% H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
%   0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.

% \end{thebibliography}

% biography section
% 
% If you have an EPS/PDF photo (graphicx package needed) extra braces are
% needed around the contents of the optional argument to biography to prevent
% the LaTeX parser from getting confused when it sees the complicated
% \includegraphics command within an optional argument. (You could create
% your own custom macro containing the \includegraphics command to make things
% simpler here.)
%\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{mshell}}]{Michael Shell}
% or if you just want to reserve a space for a photo:

% \begin{IEEEbiography}{Michael Shell}
% Biography text here.
% \end{IEEEbiography}

% % if you will not have a photo at all:
% \begin{IEEEbiographynophoto}{John Doe}
% Biography text here.
% \end{IEEEbiographynophoto}

% % insert where needed to balance the two columns on the last page with
% % biographies
% %\newpage

% \begin{IEEEbiographynophoto}{Jane Doe}
% Biography text here.
% \end{IEEEbiographynophoto}

% You can push biographies down or up by placing
% a \vfill before or after them. The appropriate
% use of \vfill depends on what kind of text is
% on the last page and whether or not the columns
% are being equalized.

%\vfill

% Can be used to pull up biographies so that the bottom of the last one
% is flush with the other column.
%\enlargethispage{-5in}

% that's all folks
\end{document}

### 2021-06-25 latex/CEUR/paper.tex
Moved latex into designated dir

%% The first command in your LaTeX source must be the \documentclass command.
%%
%% Options:
%% twocolumn : Two column layout.
%% hf: enable header and footer.
\documentclass[
twocolumn,
% hf,
]{ceurart}

%%
%% One can fix some overfulls
\sloppy

%%
%% Minted listings support 
%% Need pygment <http://pygments.org/> <http://pypi.python.org/pypi/Pygments>
%% \usepackage{minted}
\graphicspath{ {./figures/} }
%% auto break lines
%% \setminted{breaklines=true}

%%
%% end of the preamble, start of the body of the document source.
\begin{document}

%%
%% Rights management information.
%% CC-BY is default license.
\copyrightyear{2021}
\copyrightclause{Copyright for this paper by its authors.
  Use permitted under Creative Commons License Attribution 4.0
  International (CC BY 4.0).}

%%
%% This command is for the conference information
\conference{CIKM'21: Complex Data Challenges for Earth Observation,
  November 01--05, 2021, Online}

%%
%% The "title" command
\title{Uncertainty-aware graph-based multimodal remote sensing classification}
%

%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
\author[1]{Iain~Rolland}[orcid=0000-0002-4137-5605, email=imr27@cam.ac.uk,]

\address[1]{Department of Engineering, University of Cambridge, Cambridge, CB2 1PZ United Kingdom}
\address[2]{Joint Institute for Nuclear Research, 6 Joliot-Curie, Dubna, Moscow region, 141980, Russian Federation}

\author[2]{A Nother}[%
orcid=0000-0001-7116-9338,
email=another@vu.nl,
]
\address[3]{Vrije Universiteit Amsterdam, De Boelelaan 1105, 1081 HV Amsterdam, The Netherlands}

\author[3]{A Nother}[%
orcid=0000-0002-9421-8566,
email=another@acm.org,
]

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  A clear and well-documented document is presented as an
  article formatted for publication by CEUR-WS in a conference
  proceedings. Based on the ``ceurart'' document class, this article
  presents and explains many of the common variations, as well as many
  of the formatting elements an author may use in the preparation of
  the documentation of their work.
\end{abstract}

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\begin{keywords}
  paper template \sep
  paper formatting \sep
  CEUR-WS
\end{keywords}

%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.
\maketitle

\section{Introduction}

\section{Modifications}

\section{Template parameters}

\section{Front matter}

\subsection{Title Information}

\subsection{Title variants}

\subsection{Authors and Affiliations}

\subsection{Abstract and Keywords}

Abstract here.

\section{Sectioning Commands}

\section{Math Equations}

\subsection{Inline (In-text) Equations}

\subsection{Display Equations}

\section{Citations and Bibliographies}

\subsection{Some examples}

\section{Acknowledgments}

%% The acknowledgments section is defined using the "acknowledgments" environment
%% (and NOT an unnumbered section). This ensures the proper
%% identification of the section in the article metadata, and the
%% consistent spelling of the heading.
\begin{acknowledgments}
  Thanks to the developers of ACM consolidated LaTeX styles
\end{acknowledgments}

%%
%% Define the bibliography file to be used
\bibliography{sample-ceur}

\end{document}

%%
%% End of file

### 2021-06-25 latex/IEEE/bare_jrnl.tex
Moved latex into designated dir

--- 2021-06-25 docs/IEEE/bare_jrnl.tex
@@
 \subsection{Subjective Logic}
+
 In order to understand the mapping between Dirichlet distributions and uncertainty estimates, it is first necessary to describe the Subjective Logic (SL) framework.

### 2021-06-28 latex/CEUR/paper.tex
Reformatting LaTeX for git i.e. new sentence on each line

@@
 
-\author[2]{A Nother}[%
-orcid=0000-0001-7116-9338,
-email=another@vu.nl,
-]
+\author[2]{A Nother}[orcid=0000-0001-7116-9338, email=another@vu.nl,]
 \address[3]{Vrije Universiteit Amsterdam, De Boelelaan 1105, 1081 HV Amsterdam, The Netherlands}
 
-\author[3]{A Nother}[%
-orcid=0000-0002-9421-8566,
-email=another@acm.org,
-]
+\author[3]{A Nother}[orcid=0000-0002-9421-8566,email=another@acm.org,]
 
@@
 \begin{abstract}
-  A clear and well-documented document is presented as an
-  article formatted for publication by CEUR-WS in a conference
-  proceedings. Based on the ``ceurart'' document class, this article
-  presents and explains many of the common variations, as well as many
-  of the formatting elements an author may use in the preparation of
-  the documentation of their work.
+  A clear and well-documented document is presented as an article formatted for publication by CEUR-WS in a conference proceedings.
+  Based on the ``ceurart'' document class, this article presents and explains many of the common variations, as well as many of the formatting elements an author may use in the preparation of the documentation of their work.
 \end{abstract}
@@
 
-%%
 %% This command processes the author and affiliation and title
@@
 \section{Introduction}
+The capability of algorithms to provide accurate measures of confidence and uncertainty is important if they are to be adopted in real-world scenarios where the stakes can be high \cite{Goodman_Flaxman_2017}.
+Although deep learning methods have provided new state of the art performance on many computer vision tasks \cite{lecun2015deeplearning}, and in many remote sensing tasks \cite{zhang2016deep}, they are often criticised for their lack of explainability \cite{pmlr_v70_guo17a} acting like a black box.
+Prediction transparency could be improved if models were able express when results can be given with confidence.
 
-\section{Modifications}
+The remainder of this paper is organised as follows: Section \ref{sec::related_work} contains a summary of related research into uncertainty-aware remote sensing classification methods, Section \ref{sec::unc_framework} describes the uncertainty framework adopted in the methods presented, Section \ref{sec::networks} details the construction of the graph-based neural networks used, Section \ref{sec::results} presents an analysis of results and Section \ref{sec::conclusion} summarises and draws conclusions as well as suggests areas for future work.
 
-\section{Template parameters}
+\section{Related Work}
+\label{sec::related_work}
+TBW.
 
-\section{Front matter}
+\section{Uncertainty framework}
+\label{sec::unc_framework}
+
+\subsection{Subjective Logic}
+In order to understand the mapping between Dirichlet distributions and uncertainty estimates, it is first necessary to describe the Subjective Logic (SL) framework.
+The uncertainty reasoning described by SL takes an evidence-based approach to decision making \cite{DBLP:books/sp/Josang16}.
+Expressing an opinion using measured quantities of belief allows the distinction to be made between uncertainty due to a lack of evidence (vacuity) or uncertainty due to the presence of conflicting evidence (dissonance).
+A multinomial opinion, $\omega$, can be expressed as $\omega=\left(\mathbf{b}, u, \mathbf{a}\right)$, where $\mathbf{b}$ is a belief mass vector, the scalar $u$ is the uncertainty mass and $\mathbf{a}$ is the base rate vector.
+For an output, $\mathbf{y}$, of dimension K
+\begin{equation}
+    \mathbf{b}\in\mathbb{R}^K,\quad\mathbf{a}\in\mathbb{R}^K,\quad\mathbf{y}\in\mathbb{R}^K.
+\end{equation}
+A projection of $\omega$ onto a probability distribution can be made according to
+\begin{equation}
+    P(y=k) = b_k + a_ku.
+\label{eq:prob_projection}
+\end{equation}
+Given that for the base rate vector $\sum_{k=1}^Ka_k=1$, an additivity requirement is described by
+\begin{equation}
+    u+\sum_{k=1}^K b_k=1.
+\end{equation}
+
+\subsection{Dirichlet mapping}
+If $\mathbf{p}$ is a K-dimensional random vector containing the probability of belonging to each output class, and $\boldsymbol{\alpha}$ is the strength vector which parameterizes the Dirichlet distribution, the probability density function of the Dirichlet is given by
+\begin{equation}
+    \textrm{Dir}(\mathbf{p}|\boldsymbol{\alpha})= \frac{\Gamma(\sum_{k=1}^K\alpha_k)}{\prod_{k=1}\alpha_k}\prod_{k=1}^Kp_k^{\alpha_k-1},
+\end{equation}
+where $\Gamma()$ is the gamma function.
+The distribution's expected value is given by
+\begin{equation}
+\mathbb{E}\left[\textrm{Dir}(p_k\vert\boldsymbol{\alpha})\right]=\frac{\alpha_k}{\sum_{k=1}^K\alpha_k}.
+\label{eq:expected_dir}
+\end{equation}
+If we allow the uncertainty mass and base rates to be given by
+\begin{equation}
+    u=\frac{K}{\sum_{k=1}^K\alpha_k}=\frac{K}{S}
+\end{equation}
+and
+\begin{equation}
+    a_k=1/K, \forall k
+\end{equation}
+respectively, where $S$ refers to the Dirichlet strength, then by equating the probability projection of (\ref{eq:prob_projection}) with the expected value of the Dirichlet distribution given by (\ref{eq:expected_dir}), the expression for the belief mass can be obtained as
+\begin{equation}
+    b_k = \frac{\alpha_k-1}{S},
+\end{equation}
+which completes the mapping from Dirichlet distribution to SL opinion.
+\subsection{Uncertainty measures}
+From the definitions of the evidential uncertainties presented in \cite{8455454}, the measures of vacuity and dissonance have been adopted.
+The measure of vacuity uncertainty is simply given by the uncertainty mass, i.e.
+\begin{equation}
+    vac(\omega)\equiv u = \frac{K}{S},
+\label{eq::vacuity}
+\end{equation}
+and the measure of dissonance uncertainty is given by
+\begin{equation}
+    diss(\omega)=\sum_{i=1}^K\left(\frac{b_i\sum_{j\neq i}b_j\textrm{Bal}(b_j,b_i)}{\sum_{j\neq i}b_j}\right),
+\end{equation}
+where $\textrm{Bal}()$ is a function which gives the relative balance between two belief masses, defined by
+\begin{equation}
+    \textrm{Bal}(b_j,b_i)=\begin{cases}1-\frac{\vert b_i-b_j\vert}{b_i+b_j},&\text{if } b_i+b_j\neq0,\\
+    0,&\text{otherwise.}\end{cases}
+\end{equation}
+
+In order assess the relative ability of evidential uncertainties to express different types of doubt, three commonly used probabilistic measures of uncertainty (aleatoric, epistemic and entropy) are computed to provide comparisons.
+For a Bayesian model with inputs, outputs and parameters denoted $x$, $y$ and $\boldsymbol{\theta}$ respectively, the posterior which will be approximated is $p(\boldsymbol{\theta}\vert\mathcal{D})$, where $\mathcal{D}$ is the observed dataset.
+The total entropy, made up of both aleatoric and epistemic uncertainty \cite{pmlr_v80_depeweg18a} is given by
+\begin{equation}
+    \mathcal{H}\left(\mathbb{E}_{p(\boldsymbol{\theta}\vert \mathcal{D})}\left[p(y\vert x;\boldsymbol{\theta}\right]\right),
+\end{equation}
+where $\mathcal{H}()$ computes the differential entropy of a distribution.
+Aleatoric uncertainty, which accounts for noise inherent to the data observations and cannot be reduced with extra samples \cite{NIPS2017_2650d608}, is given by
+\begin{equation}
+    \mathbb{E}_{p\left(\boldsymbol{\theta}\vert \mathcal{D}\right)}\left[\mathcal{H}(p(y\vert x; \boldsymbol{\theta}))\right].
+\end{equation}
+The epistemic uncertainty, therefore, is given by the difference between these two quantities
+\begin{equation}
+    \mathcal{H}\left(\mathbb{E}_{p(\boldsymbol{\theta}\vert \mathcal{D})}\left[p(y\vert x;\boldsymbol{\theta}\right]\right)-\mathbb{E}_{p\left(\boldsymbol{\theta}\vert \mathcal{D}\right)}\left[\mathcal{H}(p(y\vert x; \boldsymbol{\theta}))\right].
+\label{eq::epistemic}
+\end{equation}
+In order to compute the above expressions for aleatoric and epistemic uncertainty, the posterior distribution over models is approximated by samples obtained using dropout inference \cite{pmlr_v48_gal16} as is described in Section \ref{sec::dropout_bayesian}.
+
+\section{Networks}
+\label{sec::networks}
+\subsection{Graph convolutional networks}
+The problem involves a graph with $N$ nodes described by an adjacency matrix $\mathbf{A}\in\mathbb{R}^{N\times N}$ and node features $\mathbf{X}\in\mathbb{R}^{N\times C}$, where $C$ denotes the number of channels in the input which describes each node.
+The graph's degree matrix, $\mathbf{D}\in\mathbb{R}^{N\times N}$, is a diagonal matrix with elements given by $\mathbf{D}_{ii}=\sum_j\mathbf{A}_{ij} $.
+For brevity, the tilde operator is used to represent the inclusion of self-connection edges in the graph, i.e.
+$\tilde{\mathbf{A}}=\mathbf{A}+\mathbf{I}$ and $\tilde{\mathbf{D}}=\mathbf{D}+\mathbf{I}$.
+Using the first-order approximation to spectral graph convolution derived by \cite{KipfW17}, the graph convolutional layer is given by
+\begin{equation}
+    \mathbf{Z}^{(l+1)}=\sigma\left(\tilde{\mathbf{D}}^{-\frac{1}{2}}\tilde{\mathbf{A}}\tilde{\mathbf{D}}^{-\frac{1}{2}}\mathbf{Z}^{(l)}\boldsymbol{W}^{(l)}\right),
+\label{eq::gcn_layer}
+\end{equation}
+where $\mathbf{Z}^{(l)}$, $\mathbf{Z}^{(l+1)}$ and $\boldsymbol{W}^{(l)}$ are the inputs, outputs and weights of the $\textrm{l}^\textrm{th}$ layer respectively, and $\sigma()$ is a non-linear activation function.
+For the first layer, the weights are $\boldsymbol{W}^{(0)}\in\mathbb{R}^{C\times F}$ and $\mathbf{Z}^{(0)} = \mathbf{X}\in\mathbb{R}^{N\times C}$ where $F$ is the number of features in the layer's output (a hyperparameter of the layer).
+Models referred to as graph convolutional networks (GCNs) from henceforth will refer to a model which consists of two of these layers used in sequence, the first using the rectified linear unit (ReLU) activation function, the second using a softmax activation.
+\subsection{Subjective models}
+In order to obtain models which will give node-level Dirichlet distribution parameters, the softmax output activation function used in a GCN is substituted for a ReLU function.
+In this way, the model is trained to output non-negative evidence contributions, $\mathbf{E}\in\mathbb{R}^{N\times K}$, where $\mathbf{E}_{i} = \boldsymbol{\alpha}_{i}-\mathbf{1}$ and $\boldsymbol{\alpha}_{i}$ refers to the K-dimensional concentration parameters of the $\text{i}^\text{th}$ node.
+In order to train an evidential model, the loss function is made up of two components; a squared error term which is minimised in order to classify a greater proportion of the nodes correctly and a variance term which is minimized to incentivize the model to provide confident predictions where possible.
+This loss, $\mathcal{L}(\boldsymbol{\theta})$, is given by
+\begin{equation}
+\begin{split}
+    \mathcal{L}(\boldsymbol{\theta})&=\sum_{i\in\mathbb{L}}\sum_k \left[(p_{ik}-y_{ik})^2+\text{Var}(p_{ik})\right],\\
+    &=\sum_{i\in\mathbb{L}}\sum_k \left[(p_{ik}-y_{ik})^2+\frac{\left(\frac{\alpha_{ik}}{S_i}\right)\left(1-\frac{\alpha_{ik}}{S_i}\right)}{S_i-K}\right],
+\end{split}
+\label{eq:core_loss}
+\end{equation}
+where $i\in\mathbb{L}$ refers to the fact that the loss is computed using a sum only over nodes in the training set, $\mathbb{L}$.
+Models trained with such an output activation and loss function will be denoted using the `S-' prefix in order to indicate they provide subjective predictions, e.g.
+S-GCN.
+\subsection{Dropout inference as a Bayesian approximation}
+\label{sec::dropout_bayesian}
+It has been shown that a model with dropout can be considered to represent the posterior distribution over models \cite{pmlr_v48_gal16}.
+The dropouts are used to represent stochasticity in the model parameters \cite{C9SC01992H}.
+A given combination of dropouts can be considered to represent a model sampled from the approximate posterior, $q(\boldsymbol{\theta})$, with the actual posterior distribution of models being $p(\boldsymbol{\theta}|\mathcal{D})$.
+Monte Carlo sampling can be used to approximately compute quantities such as the term $\mathbb{E}_{p\left(\boldsymbol{\theta}\vert \mathcal{D}\right)}\left[\mathcal{H}(p(y\vert x; \boldsymbol{\theta}))\right]$ in (\ref{eq::epistemic}) allowing the aleatoric and epistemic uncertainty to be calculated.
+This can be done using the approximation
+\begin{equation}
+    \mathbb{E}_{p\left(\boldsymbol{\theta}\vert \mathcal{D}\right)}\left[\mathcal{H}(p(y\vert x; \boldsymbol{\theta}))\right]\approx\frac{1}{M}\sum_{m=1}^M \mathcal{H}\left(p(y\vert x; \boldsymbol{\theta}^m)\right),
+\end{equation}
+where $\boldsymbol{\theta}^m\sim q(\boldsymbol{\theta})$ is a model sampled by performing dropout inference.
+When this technique has been used, the model name represents this using a `B' in its name, e.g.
+S-BGCN, showing that this Bayesian approximation has been used.
+The Drop-GCN model, which is used for benchmarking the subjective methods, refers to the same technique when applied to a `vanilla' GCN.
+
+\subsection{Convergence assistance techniques}
+In order to assist the convergence of subjective models, two additional assistance techniques have been used: teacher knowledge distillation and the use of a Dirichlet prior.
+These methods have been shown to allow subjective models to provide better uncertainty estimates \cite{Zhao2020}.
+\subsubsection{Teacher knowledge distillation}
+By training a non-subjective model in advance, its outputs, $\hat{p}_{ik}$, can be used in order to encourage the subjective model to converge to node Dirichlet distributions with $\mathbb{E}[p_{ik}]$ which are close to the teacher's deterministic estimates.
+This is achieved using an additional term in the loss function,
+\begin{equation}
+    \mathcal{L}_{\text{``-T''}}(\boldsymbol{\theta})=\sum_i\sum_k\left(\hat{p}_{ik}\log\frac{\hat{p}_{ik}}{\mathbb{E}[p_{ik}]}\right),
+\end{equation}
+which corresponds to the summation of KL-divergence terms between the teacher output probability and the expected value of the subjective model's Dirichlet distribution for each node, $\sum_i\infdiv{\hat{p}_{ik}}{\mathbb{E}[p_{ik}]}$.
+Notice that this sum is computed over all nodes as opposed to just the nodes in $\mathbb{L}$.
+Models trained using a teacher are denoted using the ``-T'' suffix e.g.
+a S-BGCN-T model would indicate that a pre-trained GCN was used as a teacher in order to assist the training convergence of a subjective graph convolutional model.
+\subsubsection{Dirichlet prior}
+A second convergence assistance technique which can be used involves the use of a Dirichlet prior, $\hat{\boldsymbol{\alpha}}$.
+The exact method chosen to provide $\hat{\boldsymbol{\alpha}}$ will depend on the nature of the problem but we will assume nodes which are nearby in the graph are more likely to belong to the same output class than nodes which are far apart, a property known as homophily \cite{huang2021combining}.
+Using this assumption, we can use the computed distances on the graph in order to assign contributions of evidence from observed node labels to the other nodes in the graph using a function of our choosing.
+If $d_{ij}$ denotes the shortest path distance between a given node, indexed by $i$ and an observed node, indexed by $j$, then the amount of evidence contributed to suggest that the $\text{i}^\text{th}$ node belongs to the $\text{k}^\text{th}$ class is given by
+\begin{equation}
+    h_{ik}(y_j,d_{ij})=
+    \begin{cases}
+    \frac{1}{\sqrt{2\pi\sigma^2}}\exp{\left(\frac{-d_{ij}^2}{2\sigma^2}\right)}, & \text{if } y_{jk}=1,\\
+    0, & \text{otherwise},
+    \end{cases}
+\end{equation}
+where $\sigma$ is a scale parameter which controls the order of distance magnitude over which evidence will propagate in the prior.
+The total evidence to suggest the $\text{i}^\text{th}$ node belongs to the $\text{k}^\text{th}$ class, $e_{ik}$ can be found by summing these contributions over the nodes in the training set such that the element in the prior is given by
+\begin{equation}
+    \hat{\boldsymbol{\alpha}}_{ik}=1+e_{ik}=1+\sum_{j\in\mathbb{L}}h_{ik}(y_j, d_{ij}).
+\end{equation}
+A node which is far from all observed nodes, i.e.
+$h_{ik}(y_j,d_{ij})\approx0, \forall j\in\mathbb{L}$, will mean that $\hat{\boldsymbol{\alpha}}_{i}\approx\mathbf{1}$.
+The prior's Dirichlet strength for the $\text{i}^\text{th}$ node, $\hat{S}_i$, will therefore be approximately $K$ and the node's vacuity, as given by (\ref{eq::vacuity}), will be approximately 1.
+On the other hand, a node which is near to many observed nodes will have large $\hat{S}_i$ and node vacuity will be small.
+The KL-divergence between the Dirichlet distribution of the prior and the model output can be incorporated into the loss function using the term
+\begin{equation}
+    \mathcal{L}_{\text{``-K''}}(\boldsymbol{\theta})=\sum_i\infdiv{\text{Dir}(\mathbf{p}_i\vert\boldsymbol{\alpha}_i)}{\text{Dir}(\hat{\mathbf{p}}_i\vert\hat{\boldsymbol{\alpha}}_i)},
+\label{eq::teacher_loss}
+\end{equation}
+which can be incorporated into the total loss.
+Models trained using a prior are denoted using the ``-K'' suffix e.g.
+a S-BGCN-K model would indicate that the graph convolutional network was trained with a loss function using a weighted combination of the loss in (\ref{eq:core_loss}) and the term described in (\ref{eq::teacher_loss}).
+
+Table \ref{loss_table} shows how these convergence assistance techniques can be weighted and combined in various permutations to provide a total loss function, $\mathcal{L}_\text{total}(\boldsymbol{\theta})$, as well as the model name abbreviations used to denote which combination has been used.
+The coefficients $\lambda_{\text{``-T''}}$ and $\lambda_{\text{``-K''}}$ are used to control the relative importance of the teacher network and the Dirichlet prior respectively against the importance of the subjective loss function given in (\ref{eq:core_loss}).
+These are considered hyperparameters of the model which are to be tuned during training.
+
+\begin{table}
+\renewcommand{\arraystretch}{1.5}
+\caption{Loss function components and their weighting coefficients for different model types}
+\label{loss_table}
+\centering
+\begin{tabular}{cc}
+\hline
+\bfseries Model name & \bfseries $\mathcal{L}_{\text{total}}(\boldsymbol{\theta})$\\
+\hline
+S-BGCN & $\mathcal{L}(\boldsymbol{\theta})$ \\
+S-BGCN-T & $\mathcal{L}(\boldsymbol{\theta})+\lambda_{\text{``-T''}}\mathcal{L}_{\text{``-T''}}(\boldsymbol{\theta})$ \\
+S-BGCN-K & $\mathcal{L}(\boldsymbol{\theta})+\lambda_{\text{``-K''}}\mathcal{L}_{\text{``-K''}}(\boldsymbol{\theta})$ \\
+S-BGCN-T-K & $\mathcal{L}(\boldsymbol{\theta})+\lambda_{\text{``-T''}}\mathcal{L}_{\text{``-T''}}(\boldsymbol{\theta})+\lambda_{\text{``-K''}}\mathcal{L}_{\text{``-K''}}(\boldsymbol{\theta})$ \\
+\hline
+\end{tabular}
+\end{table}
 

### 2021-06-28 latex/CEUR/paper.tex
Added 'Results and analysis' section from other document

@@
 \graphicspath{ {./figures/} }
+\usepackage{tcolorbox}
+\usepackage{array}
+\newcolumntype{N}{>{\centering\arraybackslash}m{.9cm}}
+\newcolumntype{M}{>{\centering\arraybackslash}m{1.0cm}}
+\newcolumntype{Z}{>{\centering\arraybackslash}m{1.6cm}}
+\newcolumntype{L}{>{\centering\arraybackslash}m{2.3cm}}
+\usepackage{multirow}
+%
 %% auto break lines
@@
 
-\subsection{Title Information}
+\subsection{Results and analysis}
+\label{sec::results}
+\subsection{Data}
+A subsection of the 2018 IEEE GRSS Data Fusion Challenge dataset was selected for the purposes of validating the described methods as a means for obtaining uncertainty aware classifications.
+The modes of data collected come from three sensor types: LiDAR, optical and hyperspectral (HS).
+The LiDAR data was provided at $0.5$ m resolution, the same resolution as the ground truth labels (GT).
+In order to simplify analysis, the optical data (which was provided at $0.05$ m resolution) and the HS data (which was provided at $1.0$ m resolution) were bilinearly resampled to obtain $0.5$ m resolution across inputs and outputs.
+
+The graph was constructed with each $0.5$ m $\times$ $0.5$ m pixel representing a node in the graph.
+Each node has a 52-dimensional feature vector (produced by stacking 3 optical channels, 48 HS channels and 1 LiDAR channel) describing it.
+The graph edges are computed using a $k$-nearest neighbors algorithm with two nodes receiving an edge connecting them if either node was one of the $k$ nodes which were nearest the other.
+This produces a graph which is both undirected and unweighted.
+The graph, which contains approximately 2.16 million nodes, was computed with $k=15$.
+
+The ground truth labels describe 20 different urban land cover/land use classes as well as an unlabelled state, described as Unclassified.
+The exact types and abundances of these classes can be found in Table \ref{tab::classes}.
+The classes which do not appear in the subsection of the dataset but exist within the wider GT are included for completeness.
+
+\begin{table}
+% \renewcommand{\arraystretch}{1.5}
+\caption{Land cover/Land use classes in selected subsection of Houston dataset ground truth}
+\label{tab::classes}
+\centering
+\begin{tabular}{NNcZ}
+\hline
+\bfseries Class Value & \bfseries Legend Color & \bfseries Class Name & \bfseries Number of Nodes (total)\\
+\hline
+$0$ & \colorbox[rgb]{0.0,0.0,0.0}{\textcolor{white}{\phantom{A}}} & Unclassified & $1302595$\\
+$1$ & \colorbox[rgb]{0.0,1.0,0.03}{\textcolor{white}{\phantom{A}}} & Healthy grass & $10120$ \\
+$2$ & \colorbox[rgb]{0.21, 0.69, 0.15}{\textcolor{white}{\phantom{A}}} & Stressed grass & $16332$ \\
+$3$ & \colorbox[rgb]{0.53, 0.73, 0.57}{\textcolor{white}{\phantom{A}}} & Artificial turf & $0$ \\
+$4$ & \colorbox[rgb]{0.  , 0.47, 0.08}{\textcolor{white}{\phantom{A}}} & Evergreen trees & $38288$ \\
+$5$ & \colorbox[rgb]{0.  , 0.3 , 0.}{\textcolor{white}{\phantom{A}}} & Deciduous trees & $3082$ \\
+$6$ & \colorbox[rgb]{0.75, 0.48, 0.08}{\textcolor{white}{\phantom{A}}} & Bare earth & $0$ \\
+$7$ & \colorbox[rgb]{0.  , 0.89, 0.89}{\textcolor{white}{\phantom{A}}} & Water & $332$ \\
+$8$ & \colorbox[rgb]{0.98, 0.98, 0.98}{\textcolor{white}{\phantom{A}}} & Residential buildings & $12417$ \\
+$9$ & \colorbox[rgb]{0.94, 0.76, 0.92}{\textcolor{white}{\phantom{A}}} & Non-residential buildings & $587141$ \\
+$10$ & \colorbox[rgb]{1.  , 0.35, 0.36}{\textcolor{white}{\phantom{A}}} & Roads & $68831$ \\
+$11$ & \colorbox[rgb]{0.64, 0.64, 0.64}{\textcolor{white}{\phantom{A}}} & Sidewalks & $96020$ \\
+$12$ & \colorbox[rgb]{0.36, 0.36, 0.36}{\textcolor{white}{\phantom{A}}} & Crosswalks & $3584$ \\
+$13$ & \colorbox[rgb]{0.79, 0.  , 0.01}{\textcolor{white}{\phantom{A}}} & Major thoroughfares & $17181$ \\
+$14$ & \colorbox[rgb]{0.54, 0.  , 0.04}{\textcolor{white}{\phantom{A}}} & Highways & $0$ \\
+$15$ & \colorbox[rgb]{1.  , 0.65, 0.07}{\textcolor{white}{\phantom{A}}} & Railways & $0$ \\
+$16$ & \colorbox[rgb]{1.,1.,0.}{\textcolor{white}{\phantom{A}}} & Paved parking lots & $7677$ \\
+$17$ & \colorbox[rgb]{0.92, 0.44, 0.}{\textcolor{white}{\phantom{A}}} & Unpaved parking lots & $0$ \\
+$18$ & \colorbox[rgb]{0.98, 0.  , 1.}{\textcolor{white}{\phantom{A}}} & Cars & $0$ \\
+$19$ & \colorbox[rgb]{0.  , 0.  , 1.}{\textcolor{white}{\phantom{A}}} & Trains & $0$ \\
+$20$ & \colorbox[rgb]{0.49, 0.76, 0.8}{\textcolor{white}{\phantom{A}}} & Stadium seats & $0$ \\
+\hline
+\end{tabular}
+\end{table}
+
+\begin{figure}[!t]
+\centering
+\includegraphics[width=\columnwidth]{figures/gt.jpg}
+\caption{Ground truth data with colors depicting classes as defined in Table \ref{tab::classes}.
+The subset area of the 2018 IEEE GRSS Data Fusion Challenge dataset covers the region with lower-left coordinate 272956, 3289689 and upper-right coordinate 273856, 3290290 (coordinates given in the NAD83 / UTM zone 15N Coordinate Reference System).}
+\label{fig::gt}
+\end{figure}
+
+In order to divide the annotations into a training, a validation and a test set, any adjacent pixels with the same label were considered part of one contiguous label block.
+Before randomly allocating these contiguous label blocks into the different sets, the blocks were separated along grid lines in order to prevent any particularly large contiguous blocks from skewing its set into having an over-representation of that class (see Figure \ref{fig::dataset_split} for a visual depiction of a random split).
+The set of contiguous blocks obtained after splitting along these arbitrary grid lines were then randomly allocated into training, validation and test sets with proportions of 40\%, 30\% and 30\% respectively.
+This method of assigning contiguous blocks into a split together as opposed to randomly splitting pixels was done so as to reduce the number of strongly correlated samples (due to local spatial correlations in the input vectors) across the test/validation/test sets which would come with having pixels of immediate proximity split into different sets.
+
+\begin{figure}[!t]
+\centering
+\includegraphics[width=\columnwidth]{figures/dataset_split.jpg}
+\caption{RGB data channels with overlaying colors used to depict a random dataset split with the red, green and blue overlay colors representing training, validation and test set pixels respectively.}
+\label{fig::dataset_split}
+\end{figure}
+
+\subsection{Network training and hyperparameters}
+Models were implemented and trained using the TensorFlow library \cite{tensorflow2015_whitepaper}.
+In order to handle the imbalance of classes in the dataset, sample weighting was used.
+Samples were given weights which were inversely proportional to the number of total samples of each class in the training set.
+These weights were used when computing the loss during training such that the loss related to nodes belonging to under-represented classes were given an increased influence over parameter updates and vice versa.
+
+All GCN-based models were constructed using a dropout layer (dropout probability $0.5$), a graph convolutional layer, as described in (\ref{eq::gcn_layer}), a second dropout layer (dropout probability $0.5$) and a second graph convolutional layer with the relevant output activation function.
+The kernel weights of the first graph convolutional layer were regularized using an $L_2$ penalization.
+Where dropout inference has been used, the number of samples taken, $M$, was 100.
+
+Hyperparameters including the learning rate, the $L_2$ regularization coefficient and the number of GCN layer output features, $F$, were selected via a grid-search method.
+Where used, $\lambda_{\text{``-T''}}$ and $\lambda_{\text{``-K''}}$ were also found using a grid-search.
+
+Learning was performed for a maximum of 400 epochs, but was stopped early if the validation loss failed to decrease further for 60 consecutive epochs.
+If stopped early, model weights were returned to the settings which provided the lowest validation set loss upon the termination of training.
+
+Each test was performed for different random dataset splits and model weight initializations in order to obtain mean and standard deviation measures of performance.
+
+Benchmark models presented include the `vanilla' GCN (which can provide uncertainty via entropy) and the Drop-GCN which is a GCN where dropout inference has been applied in order to produce estimates of aleatoric and epistemic uncertainty in addition to entropy.
+
+\subsection{Misclassification detection}
+
+Given that model uncertainties should provide a measure of the confidence which can be had about a model's predictions, a worthwhile estimate of uncertainty should be able to distinguish model misclassifications from accurate classifications.
+In order to measure a uncertainty output's ability to separate misclassifications, an experiment which produces a receiver operating characteristic (ROC) curve can be performed.
+By plotting the true positive rate (the proportion of misclassified nodes correctly flagged as misclassifications) against the false positive rate (the proportion of correctly classified nodes which were incorrectly flagged as misclassified) for various threshold values of the uncertainty metric, the ROC curve can be used to illustrate how well the uncertainty metric can separate the model's misclassifications.
+The area under the ROC curve (AUROC) can be used as a single numerical representation of the ROC figure, where a perfect discriminator would have an AUROC of $1.0$.
+An alternative measure of how well the uncertainty metric separates misclassified nodes is provided by considering the precision-recall (PR) curve, which plots the proportion of nodes which were detected as misclassifications which were actually misclassified nodes (precision) against the proportion of actually misclassified nodes which were detected as misclassifications (recall).
+Again, the area under the PR curve (AUPR) can be used as a single numerical summary of this relationship, and a perfect discriminator would have an AUPR of $1.0$.
+
+Models of each type described (as well as benchmark models) were trained and their outputs analysed in order to assess which model types as well as which of their uncertainty measures were best able to distinguish misclassified nodes.
+This was done by comparing the output labels for the test nodes to the respective test nodes' GT labels in order to separate correctly and incorrectly classified nodes.
+Each uncertainty metric in turn was then used to measure ROC and PR curve values for various threshold uncertainty metric values and the area under these curves subsequently calculated.
+
+The AUROC and AUPR values measured for the task of misclassification detection can be seen in Table \ref{tab::misc_auroc} and Table \ref{tab::misc_aupr} respectively.
+
+\begin{table}[!t]
+\renewcommand{\arraystretch}{1.3}
+\caption{Misclassification detection: Ability of each uncertainty type to detect misclassifications (measured by the AUROC metric).}
+\label{tab::misc_auroc}
+\small
+\begin{center}
+\begin{tabular}{Lccccc}
+\hline
+\multirow{2}{*}{Model}  & \multicolumn{5}{c}{AUROC}             \\
+      & Vac. & Dis. & Ale. & Epi. & Ent. \\ \hline 
+S-BGCN-T-K (superpixel prior) & $0.676$ & $0.801$ &$0.792$&$0.509$&$0.798$    \\
+S-BGCN-T-K (pixel prior) & $0.908$ & $0.840$ &$0.905$&$0.451$&$\mathbf{0.912}$ \\
+S-BGCN-T & $0.729$ & $0.834$ &$0.869$&$0.618$&$0.861$ \\ 
+S-BGCN & $0.760$ & $0.877$ &$0.894$&$0.623$&$0.886$ \\ 
+S-GCN & $0.729$ & $0.842$ &-&-&$0.859$ \\ 
+S-MLP &$0.845$&$0.904$&-&-&$0.909$ \\
+GCN & - & - &-&-&$0.887$ \\ 
+Drop-GCN & - & - &$0.897$&$0.552$&$0.887$ \\ \hline
+\end{tabular}
+\end{center}
+\end{table}
+
+\begin{table}[!t]
+\renewcommand{\arraystretch}{1.3}
+\caption{Misclassification detection: Ability of each uncertainty type to detect misclassifications (measured by the AUPR metric).}
+\label{tab::misc_aupr}
+\small
+\begin{center}
+\begin{tabular}{Lccccc}
+\hline
+\multirow{2}{*}{Model}  & \multicolumn{5}{c}{AUPR}             \\
+      & Vac. & Dis. & Ale. & Epi. & Ent. \\ \hline 
+S-BGCN-T-K (superpixel prior) & $0.352$&$0.398$&$0.467$&$0.237$&$0.474$ \\
+S-BGCN-T-K (pixel prior) & $0.659$&$0.545$&$0.649$&$0.206$&$\mathbf{0.672}$ \\
+S-BGCN-T & $0.451$&$0.484$&$0.591$&$0.278$&$0.579$ \\ 
+S-BGCN & $0.489$ & $0.558$  &$0.633$&$0.268$&$0.616$ \\ 
+S-GCN & $0.472$ & $0.538$  &-&-&$0.595$ \\ 
+S-MLP & $0.417$&$0.566$&-&-&$0.616$ \\
+GCN & - & -  &-&-&$0.606$ \\ 
+Drop-GCN & - & -  & $0.619$&$0.243$&$0.600$ \\ \hline
+\end{tabular}
+\end{center}
+\end{table}
+
+The S-BGCN-T-K model trained using the pixel prior achieves the highest ranked misclassification detection performance, with the uncertainty measured by entropy providing the best distinguishing metric, with AUROC and AUPR of $0.912$ and $0.672$ respectively, closely followed by the performance achieved by the measures of vacuity (AUROC and AUPR of $0.908$ and $0.659$ respectively) and aleatoric uncertainty (AUROC and AUPR of $0.905$ and $0.649$ respectively).
+The performance seen for the S-BGCN-T-K model trained using the superpixel prior is markedly lower, with its best-detecting uncertainty metrics (dissonance and aleatoric uncertainty) not exceeding AUROC and AUPR of $0.801$ and $0.467$ respectively.
+
+\subsection{Out of distribution detection}
+
+A lack of confidence held about the model's prediction might also arise if it receives an input which belongs to a distribution other than the distributions seen during training.
+The relative inability of neural networks' to successfully extrapolate beyond the support of the training data is a well-known weakness of these methods \cite{NIPS2017_9ef2ed4b}.
+By training models using only a subset of the classes provided by the GT, with the other classes acting as out of distribution (OOD) samples, an analysis of whether the uncertainty metrics are capable of distinguishing OOD nodes can be performed.
+Using the same approach as described for misclassification detection, the AUROC and AUPR can be calculated for each uncertainty output provided by each model type, in order to determine the relative performance of the respective metrics for this task.
+
+In the results presented, two classes were randomly selected to act as OOD.
+This was repeated 10 times, with two new randomly sampled classes selected for each training and evaluation loop in order that the variation in OOD detection performance due to the nature of the classes selected as OOD could be averaged out and the mean and standard deviation of performance presented.
+Each model type was assessed over the same 10 sampled OOD class pairs for fairness.
+The AUROC and AUPR values measured can be found in Table \ref{tab::ood_auroc} and Table \ref{tab::ood_aupr} respectively.
+
+\begin{table*}[!t]
+\renewcommand{\arraystretch}{1.3}
+\caption{OOD detection: Ability of each uncertainty type to detect OOD nodes (measured by the AUROC metric). Values shown represent the mean $\pm$ standard deviation.}
+\label{tab::ood_auroc}
+\small
+\begin{center}
+\begin{tabular}{Lccccc}
+\hline
+\multirow{2}{*}{Model}  & \multicolumn{5}{c}{AUROC}             \\
+      & Vac. & Dis. & Ale. & Epi. & Ent. \\ \hline 
+S-BGCN-T-K (superpixel prior) & $0.839\pm0.092$ & $0.691\pm0.173$ &$0.831\pm0.079$&$0.268\pm0.180$&$0.833\pm0.076$    \\           
+S-BGCN-T-K (pixel prior) & $\mathbf{0.882\pm0.085}$ & $0.605\pm0.197$ &$0.877\pm0.089$&$0.193\pm0.107$&$0.878\pm0.089$    \\        
+S-BGCN-T & $0.588\pm0.147$ & $0.664\pm0.133$ &$0.593\pm0.188$&$0.396\pm0.096$&$0.578\pm0.186$    \\ 
+S-BGCN & $0.586\pm0.147$ & $0.666\pm0.132$ &$0.596\pm0.193$&$0.401\pm0.092$&$0.580\pm0.191$    \\ 
+S-GCN & $0.580\pm0.145$ & $0.650\pm0.120$ &-&-&$0.586\pm0.181$    \\ 
+S-MLP & $0.767\pm0.152$ & $0.805\pm0.114$ &-&-&$0.787\pm0.125$    \\   
+GCN & - & - &-&-&$0.538\pm0.188$    \\ 
+Drop-GCN & - & - &$0.541\pm0.185$&$0.420\pm0.161$&$0.538\pm0.187$    \\ \hline
+\end{tabular}
+\end{center}
+\end{table*}
+
+\begin{table*}[!t]
+\renewcommand{\arraystretch}{1.3}
+\caption{OOD detection: Ability of each uncertainty type to detect OOD nodes (measured by the AUPR metric). Values shown represent the mean $\pm$ standard deviation.}
+\label{tab::ood_aupr}
+\small
+\begin{center}
+\begin{tabular}{Lccccc}
+\hline
+\multirow{2}{*}{Model}  & \multicolumn{5}{c}{AUPR}             \\
+      & Vac. & Dis. & Ale. & Epi. & Ent. \\ \hline 
+S-BGCN-T-K (superpixel prior) &$0.234\pm0.252$&$0.142\pm0.185$&$0.214\pm0.249$&$0.099\pm0.227$&$0.212\pm0.251$    \\   
+S-BGCN-T-K (pixel prior) &$\mathbf{0.318\pm0.289}$&$0.132\pm0.184$&$0.316\pm0.306$&$0.082\pm0.178$&$0.316\pm0.306$    \\        
+S-BGCN-T &$0.128\pm0.187$&$0.137\pm0.192$&$0.148\pm0.211$&$0.095\pm0.193$&$0.143\pm0.208$    \\ 
+S-BGCN & $0.127\pm0.186$ & $0.139\pm0.190$  &$0.150\pm0.213$&$0.095\pm0.195$&$0.145\pm0.209$    \\ 
+S-GCN & $0.125\pm0.185$ & $0.130\pm0.191$  &-&-&$0.143\pm0.207$    \\ 
+S-MLP & $0.245\pm0.214$ & $0.233\pm0.170$ &-&-&$0.219\pm0.201$    \\   
+GCN & - & -  &-&-&$0.116\pm0.179$    \\ 
+Drop-GCN & - & -  & $0.116\pm0.179$&$0.115\pm0.257$&$0.116\pm0.179$    \\ \hline
+\end{tabular}
+\end{center}
+\end{table*}
+
+As for the task of misclassification detection, the S-BGCN-T-K model trained using the pixel prior is also the highest ranked model for the task of OOD detection.
+Its measure of vacuity uncertainty provided the best distinguishing metric, with mean AUROC and AUPR of $0.882$ and $0.318$ respectively, closely followed by performance from the measures of entropy (AUROC and AUPR of $0.878$ and $0.316$ respectively) and aleatoric uncertainty (AUROC and AUPR of $0.877$ and $0.316$ respectively).
+While competitive performance was observed across a number of the model types trained for the task of misclassification detection, in the task of OOD detection the performance of the S-BGCN-T-K model trained using the pixel prior stands out above others.
+This highlights the importance of describing a meaningful prior in advance for the purposes of achieving improved uncertainty estimates.
+While the S-BGCN-T-K model trained using the superpixel prior does not detect OOD nodes quite so successfully, it still seems to benefit from the use of the prior as it achieves next-best performance (with its measure of vacuity giving a mean AUROC and AUPR of $0.839$ and $0.234$ respectively), perhaps also alongside the S-MLP (with its measure of dissonance giving a mean AUROC and AUPR of $0.805$ and $0.233$ respectively).
+
+The fact that vacuity is the uncertainty measure which best distinguishes OOD nodes for either form of S-BGCN-T-K model reflects intuition.
+Since vacuity measures the absence of evidence for a prediction, it is natural to expect that it would better distinguish OOD nodes for which vacuity is likely higher.
 
@@
 %% Define the bibliography file to be used
-\bibliography{sample-ceur}
+\bibliography{bibtex/bib/IEEEabrv, bibtex/bib/imrolland}
 

### 2021-06-28 latex/CEUR/paper.tex
Reformatting LaTeX for git i.e. new sentence on each line
Added conclusion

@@
-%% The first command in your LaTeX source must be the \documentclass command.
-%%
-%% Options:
-%% twocolumn : Two column layout.
-%% hf: enable header and footer.
 \documentclass[
@@
 
-%%
-%% One can fix some overfulls
+% One can fix some overfulls
 \sloppy
 
-%%
-%% Minted listings support 
-%% Need pygment <http://pygments.org/> <http://pypi.python.org/pypi/Pygments>
-%% \usepackage{minted}
+% Minted listings support 
+% Need pygment <http://pygments.org/> <http://pypi.python.org/pypi/Pygments>
+% \usepackage{minted}
+
+% Add figures directory as graphics path
 \graphicspath{ {./figures/} }
+
+% Used for KL-divergence
+\usepackage{mathtools}
+\DeclarePairedDelimiterX{\infdivx}[2]{(}{)}{%
+  #1\;\delimsize\|\;#2%
+}
+\newcommand{\infdiv}{D\infdivx}
+\DeclarePairedDelimiter{\norm}{\lVert}{\rVert}
+
+% Used for colored boxes in class legend table
 \usepackage{tcolorbox}
+% Custom column widths`
 \usepackage{array}
@@
 \newcolumntype{Z}{>{\centering\arraybackslash}m{1.6cm}}
-\newcolumntype{L}{>{\centering\arraybackslash}m{2.3cm}}
+\newcolumntype{Y}{>{\centering\arraybackslash}m{2.3cm}}
 \usepackage{multirow}
-%
-%% auto break lines
-%% \setminted{breaklines=true}
 
-%%
-%% end of the preamble, start of the body of the document source.
+% auto break lines
+% \setminted{breaklines=true}
+
+% end of the preamble, start of the body of the document source.
 \begin{document}
 
-%%
-%% Rights management information.
-%% CC-BY is default license.
+% Rights management information.
+% CC-BY is default license.
 \copyrightyear{2021}
@@
 
-%%
-%% This command is for the conference information
+% This command is for the conference information
 \conference{CIKM'21: Complex Data Challenges for Earth Observation,
@@
 
-%%
-%% The "title" command
+% The "title" command
 \title{Uncertainty-aware graph-based multimodal remote sensing classification}
-%
 
-%% The "author" command and its associated commands are used to define
-%% the authors and their affiliations.
+% The "author" command and its associated commands are used to define
+% the authors and their affiliations.
 \author[1]{Iain~Rolland}[orcid=0000-0002-4137-5605, email=imr27@cam.ac.uk,]
@@
 
-%%
-%% The abstract is a short summary of the work to be presented in the
-%% article.
+% The abstract is a short summary of the work to be presented in the article.
 \begin{abstract}
@@
 
-%%
-%% Keywords. The author(s) should pick words that accurately describe
-%% the work being presented. Separate the keywords with commas.
+% Keywords. The author(s) should pick words that accurately describe the work being presented. Separate the keywords with commas.
 \begin{keywords}
@@
 
-%% This command processes the author and affiliation and title
-%% information and builds the first part of the formatted document.
+% This command processes the author and affiliation and title information and builds the first part of the formatted document.
 \maketitle
@@
 where $i\in\mathbb{L}$ refers to the fact that the loss is computed using a sum only over nodes in the training set, $\mathbb{L}$.
-Models trained with such an output activation and loss function will be denoted using the `S-' prefix in order to indicate they provide subjective predictions, e.g.
-S-GCN.
+Models trained with such an output activation and loss function will be denoted using the `S-' prefix in order to indicate they provide subjective predictions, e.g. S-GCN.
 \subsection{Dropout inference as a Bayesian approximation}
@@
 where $\boldsymbol{\theta}^m\sim q(\boldsymbol{\theta})$ is a model sampled by performing dropout inference.
-When this technique has been used, the model name represents this using a `B' in its name, e.g.
-S-BGCN, showing that this Bayesian approximation has been used.
+When this technique has been used, the model name represents this using a `B' in its name, e.g. S-BGCN, showing that this Bayesian approximation has been used.
 The Drop-GCN model, which is used for benchmarking the subjective methods, refers to the same technique when applied to a `vanilla' GCN.
@@
 \end{equation}
-A node which is far from all observed nodes, i.e.
-$h_{ik}(y_j,d_{ij})\approx0, \forall j\in\mathbb{L}$, will mean that $\hat{\boldsymbol{\alpha}}_{i}\approx\mathbf{1}$.
+A node which is far from all observed nodes, i.e. $h_{ik}(y_j,d_{ij})\approx0, \forall j\in\mathbb{L}$, will mean that $\hat{\boldsymbol{\alpha}}_{i}\approx\mathbf{1}$.
 The prior's Dirichlet strength for the $\text{i}^\text{th}$ node, $\hat{S}_i$, will therefore be approximately $K$ and the node's vacuity, as given by (\ref{eq::vacuity}), will be approximately 1.
@@
 
-\subsection{Results and analysis}
+\section{Results and analysis}
 \label{sec::results}
@@
 \begin{center}
-\begin{tabular}{Lccccc}
+\begin{tabular}{Yccccc}
 \hline
@@
 
-\subsection{Title variants}
+\section{Conclusion}
+\label{sec::conclusion}
 
-\subsection{Authors and Affiliations}
+The misclassification and OOD detection performance of the S-BGCN-T-K presented represents a promising avenue for uncertainty-aware learning.
+The uncertainties which are produced by this model can be used to better distinguish misclassified nodes and OOD nodes than any of the other methods which are presented.
+Models which are capable of better quantifying confidence in this way are important for real-world applications where the consequences of misplaced model certainty can be high-stake.
 
-\subsection{Abstract and Keywords}
-
-Abstract here.
-
-\section{Sectioning Commands}
-
-\section{Math Equations}
-
-\subsection{Inline (In-text) Equations}
-
-\subsection{Display Equations}
-
-\section{Citations and Bibliographies}
-
-\subsection{Some examples}
-
-\section{Acknowledgments}
+The improved estimate of uncertainty obtained through the use of a prior is shown in the S-BGCN-T-K results, with equivalent models which do not use a prior, e.g.
+S-BGCN-T, producing uncertainty measures which cannot identify misclassified or OOD nodes as successfully.
+In order to distinguish misclassifications, the S-BGCN-T-K model measures of vacuity, aleatoric uncertainty or entropy all provide near-best performance.
+For the task of identifying nodes which come from a distribution other than the distributions on which the model was trained, the measure of vacuity stands out as the uncertainty metric which does this most successfully.
 
@@
 \begin{acknowledgments}
-  Thanks to the developers of ACM consolidated LaTeX styles
+  Thanks to ...
 \end{acknowledgments}
 
-%%
-%% Define the bibliography file to be used
+% Define the bibliography file to be used
 \bibliography{bibtex/bib/IEEEabrv, bibtex/bib/imrolland}
@@
 \end{document}
-
-%%
-%% End of file

### 2021-06-28 latex/CEUR/paper.tex
Rewrote bib names using 'NameYear' format.

@@
 \section{Introduction}
-The capability of algorithms to provide accurate measures of confidence and uncertainty is important if they are to be adopted in real-world scenarios where the stakes can be high \cite{Goodman_Flaxman_2017}.
-Although deep learning methods have provided new state of the art performance on many computer vision tasks \cite{lecun2015deeplearning}, and in many remote sensing tasks \cite{zhang2016deep}, they are often criticised for their lack of explainability \cite{pmlr_v70_guo17a} acting like a black box.
+The capability of algorithms to provide accurate measures of confidence and uncertainty is important if they are to be adopted in real-world scenarios where the stakes can be high \cite{Goodman2017}.
+Although deep learning methods have provided new state of the art performance on many computer vision tasks \cite{LeCun2015}, and in many remote sensing tasks \cite{LiangpeiZhang2016}, they are often criticised for their lack of explainability \cite{ChuanGuo2017} acting like a black box.
 Prediction transparency could be improved if models were able express when results can be given with confidence.
@@
 In order to understand the mapping between Dirichlet distributions and uncertainty estimates, it is first necessary to describe the Subjective Logic (SL) framework.
-The uncertainty reasoning described by SL takes an evidence-based approach to decision making \cite{DBLP:books/sp/Josang16}.
+The uncertainty reasoning described by SL takes an evidence-based approach to decision making \cite{Josang2016}.
 Expressing an opinion using measured quantities of belief allows the distinction to be made between uncertainty due to a lack of evidence (vacuity) or uncertainty due to the presence of conflicting evidence (dissonance).
@@
 \subsection{Uncertainty measures}
-From the definitions of the evidential uncertainties presented in \cite{8455454}, the measures of vacuity and dissonance have been adopted.
+From the definitions of the evidential uncertainties presented in \cite{Josang2018}, the measures of vacuity and dissonance have been adopted.
 The measure of vacuity uncertainty is simply given by the uncertainty mass, i.e.
@@
 For a Bayesian model with inputs, outputs and parameters denoted $x$, $y$ and $\boldsymbol{\theta}$ respectively, the posterior which will be approximated is $p(\boldsymbol{\theta}\vert\mathcal{D})$, where $\mathcal{D}$ is the observed dataset.
-The total entropy, made up of both aleatoric and epistemic uncertainty \cite{pmlr_v80_depeweg18a} is given by
+The total entropy, made up of both aleatoric and epistemic uncertainty \cite{Depeweg2018} is given by
 \begin{equation}
@@
 where $\mathcal{H}()$ computes the differential entropy of a distribution.
-Aleatoric uncertainty, which accounts for noise inherent to the data observations and cannot be reduced with extra samples \cite{NIPS2017_2650d608}, is given by
+Aleatoric uncertainty, which accounts for noise inherent to the data observations and cannot be reduced with extra samples \cite{Kendall2017}, is given by
 \begin{equation}
@@
 \end{equation}
-In order to compute the above expressions for aleatoric and epistemic uncertainty, the posterior distribution over models is approximated by samples obtained using dropout inference \cite{pmlr_v48_gal16} as is described in Section \ref{sec::dropout_bayesian}.
+In order to compute the above expressions for aleatoric and epistemic uncertainty, the posterior distribution over models is approximated by samples obtained using dropout inference \cite{Gal2016} as is described in Section \ref{sec::dropout_bayesian}.
 
@@
 $\tilde{\mathbf{A}}=\mathbf{A}+\mathbf{I}$ and $\tilde{\mathbf{D}}=\mathbf{D}+\mathbf{I}$.
-Using the first-order approximation to spectral graph convolution derived by \cite{KipfW17}, the graph convolutional layer is given by
+Using the first-order approximation to spectral graph convolution derived by \cite{Kipf2017}, the graph convolutional layer is given by
 \begin{equation}
@@
 \label{sec::dropout_bayesian}
-It has been shown that a model with dropout can be considered to represent the posterior distribution over models \cite{pmlr_v48_gal16}.
-The dropouts are used to represent stochasticity in the model parameters \cite{C9SC01992H}.
+It has been shown that a model with dropout can be considered to represent the posterior distribution over models \cite{Gal2016}.
+The dropouts are used to represent stochasticity in the model parameters \cite{Ryu2019}.
 A given combination of dropouts can be considered to represent a model sampled from the approximate posterior, $q(\boldsymbol{\theta})$, with the actual posterior distribution of models being $p(\boldsymbol{\theta}|\mathcal{D})$.
@@
 In order to assist the convergence of subjective models, two additional assistance techniques have been used: teacher knowledge distillation and the use of a Dirichlet prior.
-These methods have been shown to allow subjective models to provide better uncertainty estimates \cite{Zhao2020}.
+These methods have been shown to allow subjective models to provide better uncertainty estimates \cite{ZhaoXujiang2020}.
 \subsubsection{Teacher knowledge distillation}
@@
 A second convergence assistance technique which can be used involves the use of a Dirichlet prior, $\hat{\boldsymbol{\alpha}}$.
-The exact method chosen to provide $\hat{\boldsymbol{\alpha}}$ will depend on the nature of the problem but we will assume nodes which are nearby in the graph are more likely to belong to the same output class than nodes which are far apart, a property known as homophily \cite{huang2021combining}.
+The exact method chosen to provide $\hat{\boldsymbol{\alpha}}$ will depend on the nature of the problem but we will assume nodes which are nearby in the graph are more likely to belong to the same output class than nodes which are far apart, a property known as homophily \cite{HuangQian2019}.
 Using this assumption, we can use the computed distances on the graph in order to assign contributions of evidence from observed node labels to the other nodes in the graph using a function of our choosing.
@@
 \subsection{Network training and hyperparameters}
-Models were implemented and trained using the TensorFlow library \cite{tensorflow2015_whitepaper}.
+Models were implemented and trained using the TensorFlow library \cite{Abadi2015}.
 In order to handle the imbalance of classes in the dataset, sample weighting was used.
@@
 A lack of confidence held about the model's prediction might also arise if it receives an input which belongs to a distribution other than the distributions seen during training.
-The relative inability of neural networks' to successfully extrapolate beyond the support of the training data is a well-known weakness of these methods \cite{NIPS2017_9ef2ed4b}.
+The relative inability of neural networks' to successfully extrapolate beyond the support of the training data is a well-known weakness of these methods \cite{Lakshminarayanan2017}.
 By training models using only a subset of the classes provided by the GT, with the other classes acting as out of distribution (OOD) samples, an analysis of whether the uncertainty metrics are capable of distinguishing OOD nodes can be performed.

### 2021-07-01 latex/CEUR/paper.tex
Added to conclusion. Brainstormed abstract. Added some keywords

@@
 % This command is for the conference information
-\conference{CIKM'21: Complex Data Challenges for Earth Observation,
-  November 01--05, 2021, Online}
+\conference{Proceedings of the CIKM 2021 Workshops, November 01--05, 2021, Online}
 
@@
 \begin{abstract}
-  A clear and well-documented document is presented as an article formatted for publication by CEUR-WS in a conference proceedings.
-  Based on the ``ceurart'' document class, this article presents and explains many of the common variations, as well as many of the formatting elements an author may use in the preparation of the documentation of their work.
+Satellite data is abundant.
+Satellite processing methods are important.
+Many satellite processing tasks involve classification.
+Many of the most successful processing methods are deterministic.
+Decision-making in high-stakes environments should be made with knowledge about the uncertainties of belief.
+Graph-based evidential classification has the potential to provide measures of uncertainty to better assist decision-making.
+Using Subjective Logic framework, this method is capable of distinguishing uncertainty due to the lack of previously observed training samples (vacuity) from the uncertainty due to having observed training samples with conflicting classifications (dissonance).
+Using provided measures of vacuity and dissonance, the networks are better able to identify misclassified nodes as assessed.
+The method is also better able to identify out of distribution samples.
 \end{abstract}
@@
 \begin{keywords}
-  paper template \sep
-  paper formatting \sep
-  CEUR-WS
+  Multimodal remote sensing \sep
+  Uncertainty-aware \sep
+  Graph convolutional networks \sep
+  Subjective logic \sep
+  Land cover classification
 \end{keywords}
@@
 
-The misclassification and OOD detection performance of the S-BGCN-T-K presented represents a promising avenue for uncertainty-aware learning.
-The uncertainties which are produced by this model can be used to better distinguish misclassified nodes and OOD nodes than any of the other methods which are presented.
-Models which are capable of better quantifying confidence in this way are important for real-world applications where the consequences of misplaced model certainty can be high-stake.
+In this paper we have presented a novel method for providing uncertainties while perfoming multi-class classification of multimodal remote sensing data.
+The adopted framework, based upon the theory of Subjective Logic, provides measures of vacuity and dissonance which are better capable of identifying misclassifications and out of distribution samples than the alternative probabilistic measures of uncertainty assessed.
+Experimental results have shown the performance of the S-BGCN-T-K model in the tasks of misclassification and OOD detection to be improved against baseline methods.
+This represents a promising avenue for uncertainty-aware learning in the task of multimodal remote sensing classification.
+The development of algorithms which can be used to better distinguish misclassified nodes and OOD nodes and thus can better quantify confidence, is important for real-world applications where the consequences of misplaced model certainty can be high-stake.
 
-The improved estimate of uncertainty obtained through the use of a prior is shown in the S-BGCN-T-K results, with equivalent models which do not use a prior, e.g.
-S-BGCN-T, producing uncertainty measures which cannot identify misclassified or OOD nodes as successfully.
-In order to distinguish misclassifications, the S-BGCN-T-K model measures of vacuity, aleatoric uncertainty or entropy all provide near-best performance.
-For the task of identifying nodes which come from a distribution other than the distributions on which the model was trained, the measure of vacuity stands out as the uncertainty metric which does this most successfully.
+The presented results have illustrated an improvement in the quality of uncertainty estimates obtained through the use of a prior.
+This can be seen by comparing the S-BGCN-T-K misclassification detection and OOD detection performance with equivalent models which do not use a prior, e.g. S-BGCN-T.
+Of the uncertainty measures produced by the presented S-BGCN-T-K model, the measures of vacuity, aleatoric uncertainty or entropy all provide near-best performance for the task of identifying misclassifications.
+In order to identify OOD nodes, the measure of vacuity stands out as the best-performing   uncertainty metric.
 
+Future work should consider the generalisation potential of this method by considering its performance on other challenging remote sensing classification datasets.
+There is also scope for research into how the choice of method for computing the $\hat{\boldsymbol{\alpha}}$ prior affects the quality of uncertainty estimates, either by varying the scale parameter $\sigma$ or by assessing a variety of entirely different functions.
 %% The acknowledgments section is defined using the "acknowledgments" environment

### 2021-07-01 latex/CEUR/paper.tex
Wrote abstract

@@
 \address[1]{Department of Engineering, University of Cambridge, Cambridge, CB2 1PZ United Kingdom}
-\address[2]{Joint Institute for Nuclear Research, 6 Joliot-Curie, Dubna, Moscow region, 141980, Russian Federation}
+\address[2]{Department of Physics and Technology, UiT the Arctic University of Norway, P.O. box 6050 Langnes, NO-9037, Tromsø, Norway}
 
-\author[2]{A Nother}[orcid=0000-0001-7116-9338, email=another@vu.nl,]
-\address[3]{Vrije Universiteit Amsterdam, De Boelelaan 1105, 1081 HV Amsterdam, The Netherlands}
+\author[1]{A Nother}[orcid=0000-0001-7116-9338, email=another@vu.nl,]
 
-\author[3]{A Nother}[orcid=0000-0002-9421-8566,email=another@acm.org,]
+\author[1]{A Nother}[orcid=0000-0002-9421-8566,email=another@acm.org,]
 
@@
 \begin{abstract}
-Satellite data is abundant.
-Satellite processing methods are important.
-Many satellite processing tasks involve classification.
-Many of the most successful processing methods are deterministic.
-Decision-making in high-stakes environments should be made with knowledge about the uncertainties of belief.
-Graph-based evidential classification has the potential to provide measures of uncertainty to better assist decision-making.
-Using Subjective Logic framework, this method is capable of distinguishing uncertainty due to the lack of previously observed training samples (vacuity) from the uncertainty due to having observed training samples with conflicting classifications (dissonance).
-Using provided measures of vacuity and dissonance, the networks are better able to identify misclassified nodes as assessed.
-The method is also better able to identify out of distribution samples.
+In order to adopt deep learning methods in environments where the decisions being made are high-stakes, it is important to have methods which are capable of producing a quantification of the prediction confidence or uncertainty.
+Graph-based convolutional neural networks which are trained to perform classification of multimodal remote sensing data such that the model output represents a Dirichlet distribution parameterization can also be used to obtain measures of prediction uncertainty.
+By making a correspondence between a multinomial opinion, as described by subjective logic, and a Dirichlet distribution parameterization, a direct mapping between the two can be performed.
+A multinomial opinion of this kind can produce quantified measures of uncertainty and distinguishes uncertainty due to a lack of evidence (vacuity) and uncertainty due to conflicting evidence (dissonance).
+With an appropriately chosen loss function, the graph-based classifier will converge to provide accurate estimates of uncertainty.
+The results presented in this paper show that the measures of uncertainty provided by such models are capable of better distinguishing model misclassifications as well as out-of-distribution data samples than probabilistic measures of uncertainty produced by deterministic neural networks.
 \end{abstract}
@@
   Multimodal remote sensing \sep
-  Uncertainty-aware \sep
-  Graph convolutional networks \sep
-  Subjective logic \sep
-  Land cover classification
+  uncertainty estimates \sep
+  graph convolutional networks \sep
+  subjective logic \sep
+  land cover classification
 \end{keywords}
@@
 The capability of algorithms to provide accurate measures of confidence and uncertainty is important if they are to be adopted in real-world scenarios where the stakes can be high \cite{Goodman2017}.
-Although deep learning methods have provided new state of the art performance on many computer vision tasks \cite{LeCun2015}, and in many remote sensing tasks \cite{LiangpeiZhang2016}, they are often criticised for their lack of explainability \cite{ChuanGuo2017} acting like a black box.
-Prediction transparency could be improved if models were able express when results can be given with confidence.
+Although deep learning methods are often capable of producing high-accuracy predictions \cite{LeCun2015, LiangpeiZhang2016}, they are generally criticised for being unable to express when to have confidence in the prediction and when the prediction should be presented as uncertain.
+If deep learning models are to be integrated reliably into real-world decision making processes, it is of vital importance that the methods being used are capable of accurately expressing uncertainty.
+
+ANOTHER PARAGRAPH OR TWO HERE!
 
@@
 Future work should consider the generalisation potential of this method by considering its performance on other challenging remote sensing classification datasets.
-There is also scope for research into how the choice of method for computing the $\hat{\boldsymbol{\alpha}}$ prior affects the quality of uncertainty estimates, either by varying the scale parameter $\sigma$ or by assessing a variety of entirely different functions.
+There is also scope for research into how the choice of method for computing the $\hat{\boldsymbol{\alpha}}$ prior affects the quality of uncertainty estimates, either by varying the scale parameter $\sigma$ or by assessing a variety of entirely different function.
 %% The acknowledgments section is defined using the "acknowledgments" environment

### 2021-07-02 latex/CEUR/paper.tex
Combined Misclassification AUROC and AUPR tables into one to save space. Removed table of classes to save space.

@@
 
-\begin{table}
-% \renewcommand{\arraystretch}{1.5}
-\caption{Land cover/Land use classes in selected subsection of Houston dataset ground truth}
-\label{tab::classes}
-\centering
-\begin{tabular}{NNcZ}
-\hline
-\bfseries Class Value & \bfseries Legend Color & \bfseries Class Name & \bfseries Number of Nodes (total)\\
-\hline
-$0$ & \colorbox[rgb]{0.0,0.0,0.0}{\textcolor{white}{\phantom{A}}} & Unclassified & $1302595$\\
-$1$ & \colorbox[rgb]{0.0,1.0,0.03}{\textcolor{white}{\phantom{A}}} & Healthy grass & $10120$ \\
-$2$ & \colorbox[rgb]{0.21, 0.69, 0.15}{\textcolor{white}{\phantom{A}}} & Stressed grass & $16332$ \\
-$3$ & \colorbox[rgb]{0.53, 0.73, 0.57}{\textcolor{white}{\phantom{A}}} & Artificial turf & $0$ \\
-$4$ & \colorbox[rgb]{0.  , 0.47, 0.08}{\textcolor{white}{\phantom{A}}} & Evergreen trees & $38288$ \\
-$5$ & \colorbox[rgb]{0.  , 0.3 , 0.}{\textcolor{white}{\phantom{A}}} & Deciduous trees & $3082$ \\
-$6$ & \colorbox[rgb]{0.75, 0.48, 0.08}{\textcolor{white}{\phantom{A}}} & Bare earth & $0$ \\
-$7$ & \colorbox[rgb]{0.  , 0.89, 0.89}{\textcolor{white}{\phantom{A}}} & Water & $332$ \\
-$8$ & \colorbox[rgb]{0.98, 0.98, 0.98}{\textcolor{white}{\phantom{A}}} & Residential buildings & $12417$ \\
-$9$ & \colorbox[rgb]{0.94, 0.76, 0.92}{\textcolor{white}{\phantom{A}}} & Non-residential buildings & $587141$ \\
-$10$ & \colorbox[rgb]{1.  , 0.35, 0.36}{\textcolor{white}{\phantom{A}}} & Roads & $68831$ \\
-$11$ & \colorbox[rgb]{0.64, 0.64, 0.64}{\textcolor{white}{\phantom{A}}} & Sidewalks & $96020$ \\
-$12$ & \colorbox[rgb]{0.36, 0.36, 0.36}{\textcolor{white}{\phantom{A}}} & Crosswalks & $3584$ \\
-$13$ & \colorbox[rgb]{0.79, 0.  , 0.01}{\textcolor{white}{\phantom{A}}} & Major thoroughfares & $17181$ \\
-$14$ & \colorbox[rgb]{0.54, 0.  , 0.04}{\textcolor{white}{\phantom{A}}} & Highways & $0$ \\
-$15$ & \colorbox[rgb]{1.  , 0.65, 0.07}{\textcolor{white}{\phantom{A}}} & Railways & $0$ \\
-$16$ & \colorbox[rgb]{1.,1.,0.}{\textcolor{white}{\phantom{A}}} & Paved parking lots & $7677$ \\
-$17$ & \colorbox[rgb]{0.92, 0.44, 0.}{\textcolor{white}{\phantom{A}}} & Unpaved parking lots & $0$ \\
-$18$ & \colorbox[rgb]{0.98, 0.  , 1.}{\textcolor{white}{\phantom{A}}} & Cars & $0$ \\
-$19$ & \colorbox[rgb]{0.  , 0.  , 1.}{\textcolor{white}{\phantom{A}}} & Trains & $0$ \\
-$20$ & \colorbox[rgb]{0.49, 0.76, 0.8}{\textcolor{white}{\phantom{A}}} & Stadium seats & $0$ \\
-\hline
-\end{tabular}
-\end{table}
+% \begin{table}
+% % \renewcommand{\arraystretch}{1.5}
+% \caption{Land cover/Land use classes in selected subsection of Houston dataset ground truth}
+% \label{tab::classes}
+% \centering
+% \begin{tabular}{NNcZ}
+% \hline
+% \bfseries Class Value & \bfseries Legend Color & \bfseries Class Name & \bfseries Number of Nodes (total)\\
+% \hline
+% $0$ & \colorbox[rgb]{0.0,0.0,0.0}{\textcolor{white}{\phantom{A}}} & Unclassified & $1302595$\\
+% $1$ & \colorbox[rgb]{0.0,1.0,0.03}{\textcolor{white}{\phantom{A}}} & Healthy grass & $10120$ \\
+% $2$ & \colorbox[rgb]{0.21, 0.69, 0.15}{\textcolor{white}{\phantom{A}}} & Stressed grass & $16332$ \\
+% $3$ & \colorbox[rgb]{0.53, 0.73, 0.57}{\textcolor{white}{\phantom{A}}} & Artificial turf & $0$ \\
+% $4$ & \colorbox[rgb]{0.  , 0.47, 0.08}{\textcolor{white}{\phantom{A}}} & Evergreen trees & $38288$ \\
+% $5$ & \colorbox[rgb]{0.  , 0.3 , 0.}{\textcolor{white}{\phantom{A}}} & Deciduous trees & $3082$ \\
+% $6$ & \colorbox[rgb]{0.75, 0.48, 0.08}{\textcolor{white}{\phantom{A}}} & Bare earth & $0$ \\
+% $7$ & \colorbox[rgb]{0.  , 0.89, 0.89}{\textcolor{white}{\phantom{A}}} & Water & $332$ \\
+% $8$ & \colorbox[rgb]{0.98, 0.98, 0.98}{\textcolor{white}{\phantom{A}}} & Residential buildings & $12417$ \\
+% $9$ & \colorbox[rgb]{0.94, 0.76, 0.92}{\textcolor{white}{\phantom{A}}} & Non-residential buildings & $587141$ \\
+% $10$ & \colorbox[rgb]{1.  , 0.35, 0.36}{\textcolor{white}{\phantom{A}}} & Roads & $68831$ \\
+% $11$ & \colorbox[rgb]{0.64, 0.64, 0.64}{\textcolor{white}{\phantom{A}}} & Sidewalks & $96020$ \\
+% $12$ & \colorbox[rgb]{0.36, 0.36, 0.36}{\textcolor{white}{\phantom{A}}} & Crosswalks & $3584$ \\
+% $13$ & \colorbox[rgb]{0.79, 0.  , 0.01}{\textcolor{white}{\phantom{A}}} & Major thoroughfares & $17181$ \\
+% $14$ & \colorbox[rgb]{0.54, 0.  , 0.04}{\textcolor{white}{\phantom{A}}} & Highways & $0$ \\
+% $15$ & \colorbox[rgb]{1.  , 0.65, 0.07}{\textcolor{white}{\phantom{A}}} & Railways & $0$ \\
+% $16$ & \colorbox[rgb]{1.,1.,0.}{\textcolor{white}{\phantom{A}}} & Paved parking lots & $7677$ \\
+% $17$ & \colorbox[rgb]{0.92, 0.44, 0.}{\textcolor{white}{\phantom{A}}} & Unpaved parking lots & $0$ \\
+% $18$ & \colorbox[rgb]{0.98, 0.  , 1.}{\textcolor{white}{\phantom{A}}} & Cars & $0$ \\
+% $19$ & \colorbox[rgb]{0.  , 0.  , 1.}{\textcolor{white}{\phantom{A}}} & Trains & $0$ \\
+% $20$ & \colorbox[rgb]{0.49, 0.76, 0.8}{\textcolor{white}{\phantom{A}}} & Stadium seats & $0$ \\
+% \hline
+% \end{tabular}
+% \end{table}
 
@@
 
-The AUROC and AUPR values measured for the task of misclassification detection can be seen in Table \ref{tab::misc_auroc} and Table \ref{tab::misc_aupr} respectively.
+The AUROC and AUPR values measured for the task of misclassification detection can be seen in Table \ref{tab::misc_auroc}.
 
-\begin{table}[!t]
+\begin{table*}[!t]
 \renewcommand{\arraystretch}{1.3}
-\caption{Misclassification detection: Ability of each uncertainty type to detect misclassifications (measured by the AUROC metric).}
+\caption{Misclassification detection: Ability of each uncertainty type to detect misclassifications (measured by AUROC and AUPR).}
 \label{tab::misc_auroc}
@@
 \begin{center}
-\begin{tabular}{Yccccc}
+\begin{tabular}{Y|ccccc|ccccc}
 \hline
-\multirow{2}{*}{Model}  & \multicolumn{5}{c}{AUROC}             \\
-      & Vac. & Dis. & Ale. & Epi. & Ent. \\ \hline 
-S-BGCN-T-K (superpixel prior) & $0.676$ & $0.801$ &$0.792$&$0.509$&$0.798$    \\
-S-BGCN-T-K (pixel prior) & $0.908$ & $0.840$ &$0.905$&$0.451$&$\mathbf{0.912}$ \\
-S-BGCN-T & $0.729$ & $0.834$ &$0.869$&$0.618$&$0.861$ \\ 
-S-BGCN & $0.760$ & $0.877$ &$0.894$&$0.623$&$0.886$ \\ 
-S-GCN & $0.729$ & $0.842$ &-&-&$0.859$ \\ 
-S-MLP &$0.845$&$0.904$&-&-&$0.909$ \\
-GCN & - & - &-&-&$0.887$ \\ 
-Drop-GCN & - & - &$0.897$&$0.552$&$0.887$ \\ \hline
+\multirow{2}{*}{Model}  & \multicolumn{5}{c}{AUROC}\vline&\multicolumn{5}{c}{AUPR}        \\
+                        & Vac. & Dis. & Ale. & Epi. & Ent. & Vac. & Dis. & Ale. & Epi. & Ent. \\ \hline 
+S-BGCN-T-K (superpixel prior) & $0.676$ & $0.801$ &$0.792$&$0.509$&$0.798$&0.352&0.398&0.467&0.237&0.474    \\
+S-BGCN-T-K (pixel prior) & $0.908$ & $0.840$ &$0.905$&$0.451$&$\mathbf{0.912}$&0.659&0.545&0.649&0.206&0.672  \\
+S-BGCN-T & $0.729$ & $0.834$ &$0.869$&$0.618$&$0.861$&0.451&0.484&0.591&0.278&0.579  \\ 
+S-BGCN & $0.760$ & $0.877$ &$0.894$&$0.623$&$0.886$&0.489&0.558&0.633&0.268&0.616  \\ 
+S-GCN & $0.729$ & $0.842$ &-&-&$0.859$&0.472&0.538&-&-&0.595  \\ 
+S-MLP &$0.845$&$0.904$&-&-&$0.909$&0.417&0.566&-&-&0.606  \\
+GCN & - & - &-&-&$0.887$&-&-&-&-&0.606  \\ 
+Drop-GCN & - & - &$0.897$&$0.552$&$0.887$&-&-&0.619&0.243&0.600  \\ \hline
 \end{tabular}
 \end{center}
-\end{table}
+\end{table*}
 
-\begin{table}[!t]
-\renewcommand{\arraystretch}{1.3}
-\caption{Misclassification detection: Ability of each uncertainty type to detect misclassifications (measured by the AUPR metric).}
-\label{tab::misc_aupr}
-\small
-\begin{center}
-\begin{tabular}{Yccccc}
-\hline
-\multirow{2}{*}{Model}  & \multicolumn{5}{c}{AUPR}             \\
-      & Vac. & Dis. & Ale. & Epi. & Ent. \\ \hline 
-S-BGCN-T-K (superpixel prior) & $0.352$&$0.398$&$0.467$&$0.237$&$0.474$ \\
-S-BGCN-T-K (pixel prior) & $0.659$&$0.545$&$0.649$&$0.206$&$\mathbf{0.672}$ \\
-S-BGCN-T & $0.451$&$0.484$&$0.591$&$0.278$&$0.579$ \\ 
-S-BGCN & $0.489$ & $0.558$  &$0.633$&$0.268$&$0.616$ \\ 
-S-GCN & $0.472$ & $0.538$  &-&-&$0.595$ \\ 
-S-MLP & $0.417$&$0.566$&-&-&$0.616$ \\
-GCN & - & -  &-&-&$0.606$ \\ 
-Drop-GCN & - & -  & $0.619$&$0.243$&$0.600$ \\ \hline
-\end{tabular}
-\end{center}
-\end{table}
+% \begin{table*}[!t]
+% \renewcommand{\arraystretch}{1.3}
+% \caption{Misclassification detection: Ability of each uncertainty type to detect misclassifications (measured by the AUPR metric).}
+% \label{tab::misc_aupr}
+% \small
+% \begin{center}
+% \begin{tabular}{cccccc}
+% \hline
+% \multirow{2}{*}{Model}  & \multicolumn{5}{c}{AUPR}             \\
+%       & Vac. & Dis. & Ale. & Epi. & Ent. \\ \hline 
+% S-BGCN-T-K (superpixel prior) & $0.352$&$0.398$&$0.467$&$0.237$&$0.474$ \\
+% S-BGCN-T-K (pixel prior) & $0.659$&$0.545$&$0.649$&$0.206$&$\mathbf{0.672}$ \\
+% S-BGCN-T & $0.451$&$0.484$&$0.591$&$0.278$&$0.579$ \\ 
+% S-BGCN & $0.489$ & $0.558$  &$0.633$&$0.268$&$0.616$ \\ 
+% S-GCN & $0.472$ & $0.538$  &-&-&$0.595$ \\ 
+% S-MLP & $0.417$&$0.566$&-&-&$0.616$ \\
+% GCN & - & -  &-&-&$0.606$ \\ 
+% Drop-GCN & - & -  & $0.619$&$0.243$&$0.600$ \\ \hline
+% \end{tabular}
+% \end{center}
+% \end{table*}
 
@@
 Future work should consider the generalisation potential of this method by considering its performance on other challenging remote sensing classification datasets.
-There is also scope for research into how the choice of method for computing the $\hat{\boldsymbol{\alpha}}$ prior affects the quality of uncertainty estimates, either by varying the scale parameter $\sigma$ or by assessing a variety of entirely different function.
+There is also scope for research into how the choice of method for computing the $\hat{\boldsymbol{\alpha}}$ prior affects the quality of uncertainty estimates, either by varying the scale parameter $\sigma$ or considering different prior computation methods entirely.
 %% The acknowledgments section is defined using the "acknowledgments" environment

### 2021-07-02 latex/CEUR/paper.tex
Added 28421 around numbers in table

@@
                         & Vac. & Dis. & Ale. & Epi. & Ent. & Vac. & Dis. & Ale. & Epi. & Ent. \\ \hline 
-S-BGCN-T-K (superpixel prior) & $0.676$ & $0.801$ &$0.792$&$0.509$&$0.798$&0.352&0.398&0.467&0.237&0.474    \\
-S-BGCN-T-K (pixel prior) & $0.908$ & $0.840$ &$0.905$&$0.451$&$\mathbf{0.912}$&0.659&0.545&0.649&0.206&0.672  \\
-S-BGCN-T & $0.729$ & $0.834$ &$0.869$&$0.618$&$0.861$&0.451&0.484&0.591&0.278&0.579  \\ 
-S-BGCN & $0.760$ & $0.877$ &$0.894$&$0.623$&$0.886$&0.489&0.558&0.633&0.268&0.616  \\ 
-S-GCN & $0.729$ & $0.842$ &-&-&$0.859$&0.472&0.538&-&-&0.595  \\ 
-S-MLP &$0.845$&$0.904$&-&-&$0.909$&0.417&0.566&-&-&0.606  \\
-GCN & - & - &-&-&$0.887$&-&-&-&-&0.606  \\ 
-Drop-GCN & - & - &$0.897$&$0.552$&$0.887$&-&-&0.619&0.243&0.600  \\ \hline
+S-BGCN-T-K (superpixel prior) & $0.676$ & $0.801$ &$0.792$&$0.509$&$0.798$&$0.352$&$0.398$&$0.467$&$0.237$&$0.474$    \\
+S-BGCN-T-K (pixel prior) & $0.908$ & $0.840$ &$0.905$&$0.451$&$\mathbf{0.912}$&$0.659$&$0.545$&$0.649$&$0.206$&$\mathbf{0.672}$  \\
+S-BGCN-T & $0.729$ & $0.834$ &$0.869$&$0.618$&$0.861$&$0.451$&$0.484$&$0.591$&$0.278$&$0.579$  \\ 
+S-BGCN & $0.760$ & $0.877$ &$0.894$&$0.623$&$0.886$&$0.489$&$0.558$&$0.633$&$0.268$&$0.616$  \\ 
+S-GCN & $0.729$ & $0.842$ &-&-&$0.859$&$0.472$&$0.538$&-&-&$0.595$  \\ 
+S-MLP &$0.845$&$0.904$&-&-&$0.909$&$0.417$&$0.566$&-&-&$0.606$  \\
+GCN & - & - &-&-&$0.887$&-&-&-&-&$0.606$  \\ 
+Drop-GCN & - & - &$0.897$&$0.552$&$0.887$&-&-&$0.619$&$0.243$&$0.600$  \\ \hline
 \end{tabular}

### 2021-07-02 latex/CEUR/paper.tex
Removed reference to legend table from fig::gt caption
Wrote more thorough introduction

@@
 
-\author[1]{A Nother}[orcid=0000-0001-7116-9338, email=another@vu.nl,]
+\author[1]{A Nother}[orcid=0000-0000-0000-0000, email=another@vu.nl,]
 
-\author[1]{A Nother}[orcid=0000-0002-9421-8566,email=another@acm.org,]
+\author[1]{A Nother}[orcid=0000-0000-0000-0000,email=another@acm.org,]
 
@@
 
-ANOTHER PARAGRAPH OR TWO HERE!
+With remotely-sensed data being available with ever-greater temporal and spatial resolutions, the development of computational processing methods which are capable of robustly handling such large volumes of data will assist countless earth-monitoring applications.
+Specifically, with data being captured now using a wide range of capturing techniques with complementary strengths, the ability to combine this data into a multimodal analysis will allow each data mode to interact synergistically to provide better results than any individual data mode would produce in isolation.
+Each data capturing technique will naturally have its own strengths and weaknesses, inherent to the physically properties of the sensing mode.
+Deterministic classification is only useful up to a point.
+Adoption of such techniques will always be limited by the adopter's trust in the predictions.
+Uncertainty estimates will greatly assist trust in models as it will provide a quantification of confidence that might indicate when a prediction is not to be trusted, and more importantly, when a prediction is given with great certainty.
 
-The remainder of this paper is organised as follows: Section \ref{sec::related_work} contains a summary of related research into uncertainty-aware remote sensing classification methods, Section \ref{sec::unc_framework} describes the uncertainty framework adopted in the methods presented, Section \ref{sec::networks} details the construction of the graph-based neural networks used, Section \ref{sec::results} presents an analysis of results and Section \ref{sec::conclusion} summarises and draws conclusions as well as suggests areas for future work.
+In this paper, we have analysed how well different measures of model uncertainty perform the task of identifying misclassifications, as well as whether they can be used to identify data points which belong from a distribution other than those observed during training (out of distribution detection).
+To do so, we have used graph-based neural network architectures that are adapted to provide subjective opinions \cite{Kipf2017, ZhaoXujiang2020}, as described in the field of belief or evidence theory \cite{Josang2018}.
+Adopting such a method for performing multimodal classification of remote sensing data is, to the best of our knowledge, an as-yet untested approach.
+The performance of the adopted technique represents a promising avenue in the search for meaningful uncertainty estimates when performing multimodal remote sensing classification.
 
-\section{Related Work}
-\label{sec::related_work}
-TBW.
+The remainder of this paper is organised as follows: Section \ref{sec::unc_framework} describes the uncertainty framework adopted in the methods presented, Section \ref{sec::networks} details the construction of the graph-based neural networks used, Section \ref{sec::results} presents an analysis of results and Section \ref{sec::conclusion} summarises and draws conclusions as well as suggests areas for future work.
 
@@
 \includegraphics[width=\columnwidth]{figures/gt.jpg}
-\caption{Ground truth data with colors depicting classes as defined in Table \ref{tab::classes}.
+\caption{Ground truth data with colors depicting land cover classes.
 The subset area of the 2018 IEEE GRSS Data Fusion Challenge dataset covers the region with lower-left coordinate 272956, 3289689 and upper-right coordinate 273856, 3290290 (coordinates given in the NAD83 / UTM zone 15N Coordinate Reference System).}
@@
 %% consistent spelling of the heading.
-\begin{acknowledgments}
-  Thanks to ...
-\end{acknowledgments}
+% \begin{acknowledgments}
+%   Thanks to ...
+% \end{acknowledgments}
 

### 2021-07-02 latex/CEUR/paper.tex
Some amendments to sec::unc_framework section

@@
 In this paper, we have analysed how well different measures of model uncertainty perform the task of identifying misclassifications, as well as whether they can be used to identify data points which belong from a distribution other than those observed during training (out of distribution detection).
-To do so, we have used graph-based neural network architectures that are adapted to provide subjective opinions \cite{Kipf2017, ZhaoXujiang2020}, as described in the field of belief or evidence theory \cite{Josang2018}.
+To do so, we have used graph-based neural network architectures that are adapted to provide subjective opinions (as described in the field of belief or evidence theory \cite{Josang2018}) through the use of Dirichlet distribution parameterizations \cite{Kipf2017, ZhaoXujiang2020}.
 Adopting such a method for performing multimodal classification of remote sensing data is, to the best of our knowledge, an as-yet untested approach.
@@
 
+The framework described in this section is the same as is described by the work of \cite{ZhaoXujiang2020} where they use the approach to perform semi-supervised classification of benchmark graph classification datasets (e.g.
+Cora/Pubmed).
+The method they present has been adapted in order to perform the task of multimodal remote sensing classification.
+
 \subsection{Subjective Logic}
-In order to understand the mapping between Dirichlet distributions and uncertainty estimates, it is first necessary to describe the Subjective Logic (SL) framework.
-The uncertainty reasoning described by SL takes an evidence-based approach to decision making \cite{Josang2016}.
-Expressing an opinion using measured quantities of belief allows the distinction to be made between uncertainty due to a lack of evidence (vacuity) or uncertainty due to the presence of conflicting evidence (dissonance).
+Before describing how a model which can produce subjective opinions as its output can be trained, it is first important to understand what these opinions can be constructed.
+Subjective Logic (SL), takes an evidence-based approach to decision making \cite{Josang2016}.
+Expressing an opinion using measured quantities of belief allows the distinction to be made between uncertainty due to a lack of evidence (vacuity) and uncertainty due to the presence of conflicting evidence (dissonance).
 A multinomial opinion, $\omega$, can be expressed as $\omega=\left(\mathbf{b}, u, \mathbf{a}\right)$, where $\mathbf{b}$ is a belief mass vector, the scalar $u$ is the uncertainty mass and $\mathbf{a}$ is the base rate vector.
@@
 \subsection{Dirichlet mapping}
-If $\mathbf{p}$ is a K-dimensional random vector containing the probability of belonging to each output class, and $\boldsymbol{\alpha}$ is the strength vector which parameterizes the Dirichlet distribution, the probability density function of the Dirichlet is given by
+If $\mathbf{p}$ is a K-dimensional random vector containing the probability of belonging to each output class, and $\boldsymbol{\alpha}$ is the strength vector which parameterizes a Dirichlet distribution, the probability density function of the Dirichlet is given by
 \begin{equation}
@@
 \begin{equation}
-    b_k = \frac{\alpha_k-1}{S},
+    b_k = \frac{\alpha_k-1}{S}.
 \end{equation}
-which completes the mapping from Dirichlet distribution to SL opinion.
+This provides us with everything needed in order to map from a Dirichlet distribution to a SL opinion and vice versa.
 \subsection{Uncertainty measures}
@@
 where $\mathcal{H}()$ computes the differential entropy of a distribution.
-Aleatoric uncertainty, which accounts for noise inherent to the data observations and cannot be reduced with extra samples \cite{Kendall2017}, is given by
+Aleatoric uncertainty, which accounts for noise inherent to the data observations \cite{Kendall2017}, is given by
 \begin{equation}
@@
 \subsection{Graph convolutional networks}
-The problem involves a graph with $N$ nodes described by an adjacency matrix $\mathbf{A}\in\mathbb{R}^{N\times N}$ and node features $\mathbf{X}\in\mathbb{R}^{N\times C}$, where $C$ denotes the number of channels in the input which describes each node.
+The problem involves a graph with $N$ nodes described by an adjacency matrix $\mathbf{A}\in\mathbb{R}^{N\times N}$ and node features $\mathbf{X}\in\mathbb{R}^{N\times C}$, where $C$ denotes the number of channels in the input describing each node.
 The graph's degree matrix, $\mathbf{D}\in\mathbb{R}^{N\times N}$, is a diagonal matrix with elements given by $\mathbf{D}_{ii}=\sum_j\mathbf{A}_{ij} $.

### 2021-07-06 latex/CEUR/paper.tex
Cut down section describe graph convolutional network and simply left reference to Kipf and Welling for more details.

@@
 \label{sec::networks}
-\subsection{Graph convolutional networks}
 The problem involves a graph with $N$ nodes described by an adjacency matrix $\mathbf{A}\in\mathbb{R}^{N\times N}$ and node features $\mathbf{X}\in\mathbb{R}^{N\times C}$, where $C$ denotes the number of channels in the input describing each node.
 The graph's degree matrix, $\mathbf{D}\in\mathbb{R}^{N\times N}$, is a diagonal matrix with elements given by $\mathbf{D}_{ii}=\sum_j\mathbf{A}_{ij} $.
-For brevity, the tilde operator is used to represent the inclusion of self-connection edges in the graph, i.e.
-$\tilde{\mathbf{A}}=\mathbf{A}+\mathbf{I}$ and $\tilde{\mathbf{D}}=\mathbf{D}+\mathbf{I}$.
-Using the first-order approximation to spectral graph convolution derived by \cite{Kipf2017}, the graph convolutional layer is given by
+
+The graph convolutional networks used are of the form proposed by \cite{Kipf2017}, where the graph convolutional layer is given by
 \begin{equation}
@@
 where $\mathbf{Z}^{(l)}$, $\mathbf{Z}^{(l+1)}$ and $\boldsymbol{W}^{(l)}$ are the inputs, outputs and weights of the $\textrm{l}^\textrm{th}$ layer respectively, and $\sigma()$ is a non-linear activation function.
-For the first layer, the weights are $\boldsymbol{W}^{(0)}\in\mathbb{R}^{C\times F}$ and $\mathbf{Z}^{(0)} = \mathbf{X}\in\mathbb{R}^{N\times C}$ where $F$ is the number of features in the layer's output (a hyperparameter of the layer).
-Models referred to as graph convolutional networks (GCNs) from henceforth will refer to a model which consists of two of these layers used in sequence, the first using the rectified linear unit (ReLU) activation function, the second using a softmax activation.
+For brevity, the tilde operator is used to represent the inclusion of self-connection edges in the graph, i.e.
+$\tilde{\mathbf{A}}=\mathbf{A}+\mathbf{I}$ and $\tilde{\mathbf{D}}=\mathbf{D}+\mathbf{I}$.
+
 \subsection{Subjective models}

### 2021-07-06 latex/CEUR/paper.tex
Removed section explaining dropout inference, and will have to assume reader will follow references if unfamiliar.

@@
 \end{equation}
-In order to compute the above expressions for aleatoric and epistemic uncertainty, the posterior distribution over models is approximated by samples obtained using dropout inference \cite{Gal2016} as is described in Section \ref{sec::dropout_bayesian}.
+In order to compute the above expressions for aleatoric and epistemic uncertainty, the posterior distribution over models is approximated by samples obtained using dropout inference \cite{Gal2016}.
 
@@
 Models trained with such an output activation and loss function will be denoted using the `S-' prefix in order to indicate they provide subjective predictions, e.g. S-GCN.
-\subsection{Dropout inference as a Bayesian approximation}
-\label{sec::dropout_bayesian}
-It has been shown that a model with dropout can be considered to represent the posterior distribution over models \cite{Gal2016}.
-The dropouts are used to represent stochasticity in the model parameters \cite{Ryu2019}.
-A given combination of dropouts can be considered to represent a model sampled from the approximate posterior, $q(\boldsymbol{\theta})$, with the actual posterior distribution of models being $p(\boldsymbol{\theta}|\mathcal{D})$.
-Monte Carlo sampling can be used to approximately compute quantities such as the term $\mathbb{E}_{p\left(\boldsymbol{\theta}\vert \mathcal{D}\right)}\left[\mathcal{H}(p(y\vert x; \boldsymbol{\theta}))\right]$ in (\ref{eq::epistemic}) allowing the aleatoric and epistemic uncertainty to be calculated.
-This can be done using the approximation 
-\begin{equation}
-    \mathbb{E}_{p\left(\boldsymbol{\theta}\vert \mathcal{D}\right)}\left[\mathcal{H}(p(y\vert x; \boldsymbol{\theta}))\right]\approx\frac{1}{M}\sum_{m=1}^M \mathcal{H}\left(p(y\vert x; \boldsymbol{\theta}^m)\right),
-\end{equation}
-where $\boldsymbol{\theta}^m\sim q(\boldsymbol{\theta})$ is a model sampled by performing dropout inference.
-When this technique has been used, the model name represents this using a `B' in its name, e.g. S-BGCN, showing that this Bayesian approximation has been used.
-The Drop-GCN model, which is used for benchmarking the subjective methods, refers to the same technique when applied to a `vanilla' GCN.
 

### 2021-07-06 latex/CEUR/paper.tex
Removed equals sign alignment and rearranged expression so that equation number at RHS wasn't pushed out of line.

@@
 \subsection{Subjective Logic}
-Before describing how a model which can produce subjective opinions as its output can be trained, it is first important to understand what these opinions can be constructed.
 Subjective Logic (SL), takes an evidence-based approach to decision making \cite{Josang2016}.
@@
 \begin{split}
-    \mathcal{L}(\boldsymbol{\theta})&=\sum_{i\in\mathbb{L}}\sum_k \left[(p_{ik}-y_{ik})^2+\text{Var}(p_{ik})\right],\\
-    &=\sum_{i\in\mathbb{L}}\sum_k \left[(p_{ik}-y_{ik})^2+\frac{\left(\frac{\alpha_{ik}}{S_i}\right)\left(1-\frac{\alpha_{ik}}{S_i}\right)}{S_i-K}\right],
+    \mathcal{L}(\boldsymbol{\theta})=\sum_{i\in\mathbb{L}}\sum_k \left[(p_{ik}-y_{ik})^2+\text{Var}(p_{ik})\right],\\
+    =\sum_{i\in\mathbb{L}}\sum_k \left[(p_{ik}-y_{ik})^2+\frac{\alpha_{ik}}{S_i^2}\left(\frac{S_i-\alpha_{ik}}{S_i-K}\right)\right],
 \end{split}

### 2021-07-06 latex/CEUR/paper.tex
Further space-saving changes.

@@
 \newcolumntype{Z}{>{\centering\arraybackslash}m{1.6cm}}
-\newcolumntype{Y}{>{\centering\arraybackslash}m{2.3cm}}
+\newcolumntype{Y}{>{\centering\arraybackslash}m{1.6cm}}
 \usepackage{multirow}
@@
 
-The remainder of this paper is organised as follows: Section \ref{sec::unc_framework} describes the uncertainty framework adopted in the methods presented, Section \ref{sec::networks} details the construction of the graph-based neural networks used, Section \ref{sec::results} presents an analysis of results and Section \ref{sec::conclusion} summarises and draws conclusions as well as suggests areas for future work.
+The remainder of this paper is organised as follows: Section \ref{sec::unc_framework} describes the uncertainty framework adopted in the methods presented, Section \ref{sec::GraphNetworkArchitecture} details the construction of the graph-based neural networks used, Section \ref{sec::results} presents an analysis of results and Section \ref{sec::conclusion} summarises and draws conclusions as well as suggests areas for future work.
 
@@
 \end{equation}
-A projection of $\omega$ onto a probability distribution can be made according to
-\begin{equation}
-    P(y=k) = b_k + a_ku.
-\label{eq:prob_projection}
-\end{equation}
-Given that for the base rate vector $\sum_{k=1}^Ka_k=1$, an additivity requirement is described by
+A projection of $\omega$ onto a probability distribution can be made according to $P(y=k) = b_k + a_ku$.
+It follows that since $\sum_{k=1}^Ka_k=1$ for the base rate vector, an additivity requirement is described by
 \begin{equation}
@@
 
-\section{Networks}
-\label{sec::networks}
-The problem involves a graph with $N$ nodes described by an adjacency matrix $\mathbf{A}\in\mathbb{R}^{N\times N}$ and node features $\mathbf{X}\in\mathbb{R}^{N\times C}$, where $C$ denotes the number of channels in the input describing each node.
+\section{Graph network architecture}
+\label{sec::GraphNetworkArchitecture}
+The multimodal data can be represented using a graph, where each of the $N$ nodes in the graph represents a pixel in the image.
+The graph's adjacency matrix, $\mathbf{A}\in\mathbb{R}^{N\times N}$, is used to represent edges between nodes deemed similar.
+A set of features, $\mathbf{X}\in\mathbb{R}^{N\times C}$, is used to assign a vector description of each graph node, where $C$ denotes the number of input features.
 The graph's degree matrix, $\mathbf{D}\in\mathbb{R}^{N\times N}$, is a diagonal matrix with elements given by $\mathbf{D}_{ii}=\sum_j\mathbf{A}_{ij} $.
@@
 \subsection{Subjective models}
-In order to obtain models which will give node-level Dirichlet distribution parameters, the softmax output activation function used in a GCN is substituted for a ReLU function.
+An adaptation to the GCN architecture used by \cite{Kipf2017} must be made in order to obtain subjective opinions that will be used to obtain measures of vacuity and dissonance uncertainty.
+The adaptation made means that the model will output node-level Dirichlet distribution parameters, such that the output will provide a probability distribution over multinomial class probabilities for each node.
+To do so, the softmax output activation function used in the output layer of the GCN is substituted for a ReLU function.
 In this way, the model is trained to output non-negative evidence contributions, $\mathbf{E}\in\mathbb{R}^{N\times K}$, where $\mathbf{E}_{i} = \boldsymbol{\alpha}_{i}-\mathbf{1}$ and $\boldsymbol{\alpha}_{i}$ refers to the K-dimensional concentration parameters of the $\text{i}^\text{th}$ node.
-In order to train an evidential model, the loss function is made up of two components; a squared error term which is minimised in order to classify a greater proportion of the nodes correctly and a variance term which is minimized to incentivize the model to provide confident predictions where possible.
+In order to train such a model, the loss function is made up of two components; a squared error term which is minimised in order to classify a greater proportion of the nodes correctly and a variance term which is minimized to incentivize the model to provide confident predictions where possible.
 This loss, $\mathcal{L}(\boldsymbol{\theta})$, is given by
@@
 \begin{equation}
-    \mathcal{L}_{\text{``-T''}}(\boldsymbol{\theta})=\sum_i\sum_k\left(\hat{p}_{ik}\log\frac{\hat{p}_{ik}}{\mathbb{E}[p_{ik}]}\right),
+    \mathcal{L}_{\text{T}}(\boldsymbol{\theta})=\sum_i\sum_k\left(\hat{p}_{ik}\log\frac{\hat{p}_{ik}}{\mathbb{E}[p_{ik}]}\right),
 \end{equation}
@@
 \end{equation}
-A node which is far from all observed nodes, i.e. $h_{ik}(y_j,d_{ij})\approx0, \forall j\in\mathbb{L}$, will mean that $\hat{\boldsymbol{\alpha}}_{i}\approx\mathbf{1}$.
-The prior's Dirichlet strength for the $\text{i}^\text{th}$ node, $\hat{S}_i$, will therefore be approximately $K$ and the node's vacuity, as given by (\ref{eq::vacuity}), will be approximately 1.
-On the other hand, a node which is near to many observed nodes will have large $\hat{S}_i$ and node vacuity will be small.
 The KL-divergence between the Dirichlet distribution of the prior and the model output can be incorporated into the loss function using the term
 \begin{equation}
-    \mathcal{L}_{\text{``-K''}}(\boldsymbol{\theta})=\sum_i\infdiv{\text{Dir}(\mathbf{p}_i\vert\boldsymbol{\alpha}_i)}{\text{Dir}(\hat{\mathbf{p}}_i\vert\hat{\boldsymbol{\alpha}}_i)},
+    \mathcal{L}_{\text{K}}(\boldsymbol{\theta})=\sum_i\infdiv{\text{Dir}(\mathbf{p}_i\vert\boldsymbol{\alpha}_i)}{\text{Dir}(\hat{\mathbf{p}}_i\vert\hat{\boldsymbol{\alpha}}_i)},
 \label{eq::teacher_loss}
 \end{equation}
-which can be incorporated into the total loss.
+which can, in turn, be incorporated into the total loss.
 Models trained using a prior are denoted using the ``-K'' suffix e.g.
@@
 Table \ref{loss_table} shows how these convergence assistance techniques can be weighted and combined in various permutations to provide a total loss function, $\mathcal{L}_\text{total}(\boldsymbol{\theta})$, as well as the model name abbreviations used to denote which combination has been used.
-The coefficients $\lambda_{\text{``-T''}}$ and $\lambda_{\text{``-K''}}$ are used to control the relative importance of the teacher network and the Dirichlet prior respectively against the importance of the subjective loss function given in (\ref{eq:core_loss}).
-These are considered hyperparameters of the model which are to be tuned during training.
+The coefficients $\lambda_{\text{T}}$ and $\lambda_{\text{K}}$ are used to control the relative importance of the teacher network and the Dirichlet prior respectively against the importance of the subjective loss function given in (\ref{eq:core_loss}).
+These have been considered as hyperparameters which are to be tuned during training.
 
 \begin{table}
+\scriptsize
 \renewcommand{\arraystretch}{1.5}
@@
 S-BGCN & $\mathcal{L}(\boldsymbol{\theta})$ \\
-S-BGCN-T & $\mathcal{L}(\boldsymbol{\theta})+\lambda_{\text{``-T''}}\mathcal{L}_{\text{``-T''}}(\boldsymbol{\theta})$ \\
-S-BGCN-K & $\mathcal{L}(\boldsymbol{\theta})+\lambda_{\text{``-K''}}\mathcal{L}_{\text{``-K''}}(\boldsymbol{\theta})$ \\
-S-BGCN-T-K & $\mathcal{L}(\boldsymbol{\theta})+\lambda_{\text{``-T''}}\mathcal{L}_{\text{``-T''}}(\boldsymbol{\theta})+\lambda_{\text{``-K''}}\mathcal{L}_{\text{``-K''}}(\boldsymbol{\theta})$ \\
+S-BGCN-T & $\mathcal{L}(\boldsymbol{\theta})+\lambda_{\text{T}}\mathcal{L}_{\text{T}}(\boldsymbol{\theta})$ \\
+S-BGCN-K & $\mathcal{L}(\boldsymbol{\theta})+\lambda_{\text{K}}\mathcal{L}_{\text{K}}(\boldsymbol{\theta})$ \\
+S-BGCN-T-K & $\mathcal{L}(\boldsymbol{\theta})+\lambda_{\text{T}}\mathcal{L}_{\text{T}}(\boldsymbol{\theta})+\lambda_{\text{K}}\mathcal{L}_{\text{K}}(\boldsymbol{\theta})$ \\
 \hline
@@
 A subsection of the 2018 IEEE GRSS Data Fusion Challenge dataset was selected for the purposes of validating the described methods as a means for obtaining uncertainty aware classifications.
-The modes of data collected come from three sensor types: LiDAR, optical and hyperspectral (HS).
+The ground truth labels in this dataset describe 20 different urban land cover/land use classes (i.e. $K=20$) as well as an unlabelled state, described as Unclassified.
+The modes of input data represent measurements from three sensor types: LiDAR, optical and hyperspectral (HS).
 The LiDAR data was provided at $0.5$ m resolution, the same resolution as the ground truth labels (GT).
@@
 
-The graph was constructed with each $0.5$ m $\times$ $0.5$ m pixel representing a node in the graph.
+The graph was constructed with each $0.5$ m $\times$ $0.5$ m pixels representing a node in the graph.
 Each node has a 52-dimensional feature vector (produced by stacking 3 optical channels, 48 HS channels and 1 LiDAR channel) describing it.
@@
 
-The ground truth labels describe 20 different urban land cover/land use classes as well as an unlabelled state, described as Unclassified.
-The exact types and abundances of these classes can be found in Table \ref{tab::classes}.
-The classes which do not appear in the subsection of the dataset but exist within the wider GT are included for completeness.
+% The exact types and abundances of these classes can be found in Table \ref{tab::classes}.
+% The classes which do not appear in the subsection of the dataset but exist within the wider GT are included for completeness.
 
@@
 \centering
-\includegraphics[width=\columnwidth]{figures/gt.jpg}
-\caption{Ground truth data with colors depicting land cover classes.
-The subset area of the 2018 IEEE GRSS Data Fusion Challenge dataset covers the region with lower-left coordinate 272956, 3289689 and upper-right coordinate 273856, 3290290 (coordinates given in the NAD83 / UTM zone 15N Coordinate Reference System).}
+\includegraphics[width=.7\columnwidth]{figures/gt.jpg}
+\caption{Ground truth data with colors depicting land cover classes. This data represents a subset of the 2018 IEEE GRSS Data Fusion Challenge dataset.}
 \label{fig::gt}
@@
 Hyperparameters including the learning rate, the $L_2$ regularization coefficient and the number of GCN layer output features, $F$, were selected via a grid-search method.
-Where used, $\lambda_{\text{``-T''}}$ and $\lambda_{\text{``-K''}}$ were also found using a grid-search.
+Where used, $\lambda_{\text{T}}$ and $\lambda_{\text{K}}$ were also found using a grid-search.
 
@@
 Given that model uncertainties should provide a measure of the confidence which can be had about a model's predictions, a worthwhile estimate of uncertainty should be able to distinguish model misclassifications from accurate classifications.
-In order to measure a uncertainty output's ability to separate misclassifications, an experiment which produces a receiver operating characteristic (ROC) curve can be performed.
-By plotting the true positive rate (the proportion of misclassified nodes correctly flagged as misclassifications) against the false positive rate (the proportion of correctly classified nodes which were incorrectly flagged as misclassified) for various threshold values of the uncertainty metric, the ROC curve can be used to illustrate how well the uncertainty metric can separate the model's misclassifications.
-The area under the ROC curve (AUROC) can be used as a single numerical representation of the ROC figure, where a perfect discriminator would have an AUROC of $1.0$.
-An alternative measure of how well the uncertainty metric separates misclassified nodes is provided by considering the precision-recall (PR) curve, which plots the proportion of nodes which were detected as misclassifications which were actually misclassified nodes (precision) against the proportion of actually misclassified nodes which were detected as misclassifications (recall).
-Again, the area under the PR curve (AUPR) can be used as a single numerical summary of this relationship, and a perfect discriminator would have an AUPR of $1.0$.
+In order to measure a uncertainty output's ability to separate misclassifications, a receiver operating characteristic (ROC) curve and a precision-recall (PR) curve can be computed.
+The area under the ROC curve and PR curve (AUROC and AUPR respectively) can be used as a single numerical representation of the detection performance, where an area of $1.0$ would represent a perfect discriminator for both metrics.
 
-Models of each type described (as well as benchmark models) were trained and their outputs analysed in order to assess which model types as well as which of their uncertainty measures were best able to distinguish misclassified nodes.
-This was done by comparing the output labels for the test nodes to the respective test nodes' GT labels in order to separate correctly and incorrectly classified nodes.
-Each uncertainty metric in turn was then used to measure ROC and PR curve values for various threshold uncertainty metric values and the area under these curves subsequently calculated.
-
-The AUROC and AUPR values measured for the task of misclassification detection can be seen in Table \ref{tab::misc_auroc}.
+Models of each type described (as well as benchmark models) were trained and their outputs analysed in produce the AUROC and AUPR values seen in Table \ref{tab::misc_auroc}.
 
@@
 \label{tab::misc_auroc}
-\small
+\scriptsize
 \begin{center}
@@
 % \label{tab::misc_aupr}
-% \small
+% \scriptsize
 % \begin{center}
@@
 
-A lack of confidence held about the model's prediction might also arise if it receives an input which belongs to a distribution other than the distributions seen during training.
+It would also be reasonable to expect that uncertainty should be higher when the model is asked to make a prediction using an input which does not resemble the inputs upon which it was trained.
 The relative inability of neural networks' to successfully extrapolate beyond the support of the training data is a well-known weakness of these methods \cite{Lakshminarayanan2017}.
-By training models using only a subset of the classes provided by the GT, with the other classes acting as out of distribution (OOD) samples, an analysis of whether the uncertainty metrics are capable of distinguishing OOD nodes can be performed.
+By training models using only a subset of the classes provided by the GT, with the other classes acting as out of distribution (OOD) samples, the OOD detection ability of the uncertainty metrics can be measured.
 Using the same approach as described for misclassification detection, the AUROC and AUPR can be calculated for each uncertainty output provided by each model type, in order to determine the relative performance of the respective metrics for this task.
@@
 \label{tab::ood_auroc}
-\small
+\scriptsize
 \begin{center}
@@
 \label{tab::ood_aupr}
-\small
+\scriptsize
 \begin{center}

### 2021-07-06 latex/CEUR/paper.tex
Removed superpixel results from paper, no space to investigate in this conference paper

@@
 
-The framework described in this section is the same as is described by the work of \cite{ZhaoXujiang2020} where they use the approach to perform semi-supervised classification of benchmark graph classification datasets (e.g.
-Cora/Pubmed).
+The framework described in this section is the same as is described by the work of \cite{ZhaoXujiang2020} where they use the approach to perform semi-supervised classification of benchmark graph classification datasets including Cora and Pubmed.
 The method they present has been adapted in order to perform the task of multimodal remote sensing classification.
@@
 A multinomial opinion, $\omega$, can be expressed as $\omega=\left(\mathbf{b}, u, \mathbf{a}\right)$, where $\mathbf{b}$ is a belief mass vector, the scalar $u$ is the uncertainty mass and $\mathbf{a}$ is the base rate vector.
-For an output, $\mathbf{y}$, of dimension K
+For a $K$-class classification problem, $\mathbf{y}$, $\mathbf{a}$ and $\mathbf{b}$ are all vectors of dimension $K$.
+A projection of $\omega$ onto a probability distribution can be made according to
 \begin{equation}
-    \mathbf{b}\in\mathbb{R}^K,\quad\mathbf{a}\in\mathbb{R}^K,\quad\mathbf{y}\in\mathbb{R}^K.
+  P(y=k) = b_k + a_ku.
+  \label{eq:prob_projection}
 \end{equation}
-A projection of $\omega$ onto a probability distribution can be made according to $P(y=k) = b_k + a_ku$.
 It follows that since $\sum_{k=1}^Ka_k=1$ for the base rate vector, an additivity requirement is described by
@@
 \subsection{Dirichlet mapping}
-If $\mathbf{p}$ is a K-dimensional random vector containing the probability of belonging to each output class, and $\boldsymbol{\alpha}$ is the strength vector which parameterizes a Dirichlet distribution, the probability density function of the Dirichlet is given by
+If $\mathbf{p}$ is a $K$-dimensional random vector containing the probability of belonging to each output class, and $\boldsymbol{\alpha}$ is the strength vector which parameterizes a Dirichlet distribution, the probability density function of the Dirichlet is given by
 \begin{equation}
@@
 To do so, the softmax output activation function used in the output layer of the GCN is substituted for a ReLU function.
-In this way, the model is trained to output non-negative evidence contributions, $\mathbf{E}\in\mathbb{R}^{N\times K}$, where $\mathbf{E}_{i} = \boldsymbol{\alpha}_{i}-\mathbf{1}$ and $\boldsymbol{\alpha}_{i}$ refers to the K-dimensional concentration parameters of the $\text{i}^\text{th}$ node.
+In this way, the model is trained to output non-negative evidence contributions, $\mathbf{E}\in\mathbb{R}^{N\times K}$, where $\mathbf{E}_{i} = \boldsymbol{\alpha}_{i}-\mathbf{1}$ and $\boldsymbol{\alpha}_{i}$ refers to the $K$-dimensional concentration parameters of the $\text{i}^\text{th}$ node.
 In order to train such a model, the loss function is made up of two components; a squared error term which is minimised in order to classify a greater proportion of the nodes correctly and a variance term which is minimized to incentivize the model to provide confident predictions where possible.
@@
                         & Vac. & Dis. & Ale. & Epi. & Ent. & Vac. & Dis. & Ale. & Epi. & Ent. \\ \hline 
-S-BGCN-T-K (superpixel prior) & $0.676$ & $0.801$ &$0.792$&$0.509$&$0.798$&$0.352$&$0.398$&$0.467$&$0.237$&$0.474$    \\
-S-BGCN-T-K (pixel prior) & $0.908$ & $0.840$ &$0.905$&$0.451$&$\mathbf{0.912}$&$0.659$&$0.545$&$0.649$&$0.206$&$\mathbf{0.672}$  \\
+% S-BGCN-T-K (superpixel prior) & $0.676$ & $0.801$ &$0.792$&$0.509$&$0.798$&$0.352$&$0.398$&$0.467$&$0.237$&$0.474$    \\
+S-BGCN-T-K  & $0.908$ & $0.840$ &$0.905$&$0.451$&$\mathbf{0.912}$&$0.659$&$0.545$&$0.649$&$0.206$&$\mathbf{0.672}$  \\
 S-BGCN-T & $0.729$ & $0.834$ &$0.869$&$0.618$&$0.861$&$0.451$&$0.484$&$0.591$&$0.278$&$0.579$  \\ 
@@
 
-The S-BGCN-T-K model trained using the pixel prior achieves the highest ranked misclassification detection performance, with the uncertainty measured by entropy providing the best distinguishing metric, with AUROC and AUPR of $0.912$ and $0.672$ respectively, closely followed by the performance achieved by the measures of vacuity (AUROC and AUPR of $0.908$ and $0.659$ respectively) and aleatoric uncertainty (AUROC and AUPR of $0.905$ and $0.649$ respectively).
-The performance seen for the S-BGCN-T-K model trained using the superpixel prior is markedly lower, with its best-detecting uncertainty metrics (dissonance and aleatoric uncertainty) not exceeding AUROC and AUPR of $0.801$ and $0.467$ respectively.
+The S-BGCN-T-K model trained achieves the highest ranked misclassification detection performance, with the uncertainty measured by entropy providing the best distinguishing metric, with AUROC and AUPR of $0.912$ and $0.672$ respectively, closely followed by the performance achieved by the measures of vacuity (AUROC and AUPR of $0.908$ and $0.659$ respectively) and aleatoric uncertainty (AUROC and AUPR of $0.905$ and $0.649$ respectively).
 
@@
 \begin{center}
-\begin{tabular}{Yccccc}
+\begin{tabular}{Y|ccccc}
 \hline
 \multirow{2}{*}{Model}  & \multicolumn{5}{c}{AUROC}             \\
-      & Vac. & Dis. & Ale. & Epi. & Ent. \\ \hline 
-S-BGCN-T-K (superpixel prior) & $0.839\pm0.092$ & $0.691\pm0.173$ &$0.831\pm0.079$&$0.268\pm0.180$&$0.833\pm0.076$    \\           
-S-BGCN-T-K (pixel prior) & $\mathbf{0.882\pm0.085}$ & $0.605\pm0.197$ &$0.877\pm0.089$&$0.193\pm0.107$&$0.878\pm0.089$    \\        
+      & Vacuity & Dissonance & Aleatoric & Epistemic & Entropy \\ \hline 
+% S-BGCN-T-K (superpixel prior) & $0.839\pm0.092$ & $0.691\pm0.173$ &$0.831\pm0.079$&$0.268\pm0.180$&$0.833\pm0.076$    \\           
+S-BGCN-T-K & $\mathbf{0.882\pm0.085}$ & $0.605\pm0.197$ &$0.877\pm0.089$&$0.193\pm0.107$&$0.878\pm0.089$    \\        
 S-BGCN-T & $0.588\pm0.147$ & $0.664\pm0.133$ &$0.593\pm0.188$&$0.396\pm0.096$&$0.578\pm0.186$    \\ 
@@
 \begin{center}
-\begin{tabular}{Yccccc}
+\begin{tabular}{Y|ccccc}
 \hline
 \multirow{2}{*}{Model}  & \multicolumn{5}{c}{AUPR}             \\
-      & Vac. & Dis. & Ale. & Epi. & Ent. \\ \hline 
-S-BGCN-T-K (superpixel prior) &$0.234\pm0.252$&$0.142\pm0.185$&$0.214\pm0.249$&$0.099\pm0.227$&$0.212\pm0.251$    \\   
-S-BGCN-T-K (pixel prior) &$\mathbf{0.318\pm0.289}$&$0.132\pm0.184$&$0.316\pm0.306$&$0.082\pm0.178$&$0.316\pm0.306$    \\        
+      & Vacuity & Dissonance & Aleatoric & Epistemic & Entropy \\ \hline 
+% S-BGCN-T-K (superpixel prior) &$0.234\pm0.252$&$0.142\pm0.185$&$0.214\pm0.249$&$0.099\pm0.227$&$0.212\pm0.251$    \\   
+S-BGCN-T-K &$\mathbf{0.318\pm0.289}$&$0.132\pm0.184$&$0.316\pm0.306$&$0.082\pm0.178$&$0.316\pm0.306$    \\        
 S-BGCN-T &$0.128\pm0.187$&$0.137\pm0.192$&$0.148\pm0.211$&$0.095\pm0.193$&$0.143\pm0.208$    \\ 
@@
 
-As for the task of misclassification detection, the S-BGCN-T-K model trained using the pixel prior is also the highest ranked model for the task of OOD detection.
+As for the task of misclassification detection, the S-BGCN-T-K model trained using the pixel prior is the highest ranked model.
 Its measure of vacuity uncertainty provided the best distinguishing metric, with mean AUROC and AUPR of $0.882$ and $0.318$ respectively, closely followed by performance from the measures of entropy (AUROC and AUPR of $0.878$ and $0.316$ respectively) and aleatoric uncertainty (AUROC and AUPR of $0.877$ and $0.316$ respectively).
-While competitive performance was observed across a number of the model types trained for the task of misclassification detection, in the task of OOD detection the performance of the S-BGCN-T-K model trained using the pixel prior stands out above others.
+The performance of the S-BGCN-T-K model trained using the pixel prior stands out above the performance of other models trained.
 This highlights the importance of describing a meaningful prior in advance for the purposes of achieving improved uncertainty estimates.
-While the S-BGCN-T-K model trained using the superpixel prior does not detect OOD nodes quite so successfully, it still seems to benefit from the use of the prior as it achieves next-best performance (with its measure of vacuity giving a mean AUROC and AUPR of $0.839$ and $0.234$ respectively), perhaps also alongside the S-MLP (with its measure of dissonance giving a mean AUROC and AUPR of $0.805$ and $0.233$ respectively).
 

### 2021-07-06 latex/CEUR/paper.tex
Removed a few more reference to pixel prior models in text since there isn't room to compare superpixel/pixel prior in this paper

@@
 \subsection{Data}
-A subsection of the 2018 IEEE GRSS Data Fusion Challenge dataset was selected for the purposes of validating the described methods as a means for obtaining uncertainty aware classifications.
+A subsection of the 2018 IEEE GRSS Data Fusion Challenge dataset was selected for the purposes of validating the described methods.
 The ground truth labels in this dataset describe 20 different urban land cover/land use classes (i.e. $K=20$) as well as an unlabelled state, described as Unclassified.
@@
 
-In order to divide the annotations into a training, a validation and a test set, any adjacent pixels with the same label were considered part of one contiguous label block.
-Before randomly allocating these contiguous label blocks into the different sets, the blocks were separated along grid lines in order to prevent any particularly large contiguous blocks from skewing its set into having an over-representation of that class (see Figure \ref{fig::dataset_split} for a visual depiction of a random split).
-The set of contiguous blocks obtained after splitting along these arbitrary grid lines were then randomly allocated into training, validation and test sets with proportions of 40\%, 30\% and 30\% respectively.
-This method of assigning contiguous blocks into a split together as opposed to randomly splitting pixels was done so as to reduce the number of strongly correlated samples (due to local spatial correlations in the input vectors) across the test/validation/test sets which would come with having pixels of immediate proximity split into different sets.
-
-\begin{figure}[!t]
-\centering
-\includegraphics[width=\columnwidth]{figures/dataset_split.jpg}
-\caption{RGB data channels with overlaying colors used to depict a random dataset split with the red, green and blue overlay colors representing training, validation and test set pixels respectively.}
-\label{fig::dataset_split}
-\end{figure}
+% In order to divide the annotations into a training, a validation and a test set, any adjacent pixels with the same label were considered part of one contiguous label block.
+% Before randomly allocating these contiguous label blocks into the different sets, the blocks were separated along grid lines in order to prevent any prevent large contiguous blocks from skewing class balances between sets (see Figure \ref{fig::dataset_split} for a depiction of a random split).
+% The resulting set of blocks were then randomly allocated into training, validation and test sets with proportions of 40\%, 30\% and 30\% respectively.
+% This method of assigning contiguous blocks into a split together as opposed to randomly splitting pixels was done so as to reduce the number of strongly correlated samples (due to local spatial correlations in the input vectors) across the test/validation/test sets which would come with having pixels of immediate proximity split into different sets.
+% 
+% \begin{figure}[!t]
+% \centering
+% \includegraphics[width=\columnwidth]{figures/dataset_split.jpg}
+% \caption{RGB data channels with overlaying colors used to depict a random dataset split with the red, green and blue overlay colors representing training, validation and test set pixels respectively.}
+% \label{fig::dataset_split}
+% \end{figure}
 
@@
 In the results presented, two classes were randomly selected to act as OOD.
-This was repeated 10 times, with two new randomly sampled classes selected for each training and evaluation loop in order that the variation in OOD detection performance due to the nature of the classes selected as OOD could be averaged out and the mean and standard deviation of performance presented.
+This was repeated 10 times, with two new randomly sampled classes selected for each training and evaluation loop in order that the variation in OOD detection performance due to the nature of the classes selected as OOD could be averaged out and the mean and standard deviation computed.
 Each model type was assessed over the same 10 sampled OOD class pairs for fairness.
@@
 
-As for the task of misclassification detection, the S-BGCN-T-K model trained using the pixel prior is the highest ranked model.
+As for the task of misclassification detection, the S-BGCN-T-K model is the highest ranked model.
 Its measure of vacuity uncertainty provided the best distinguishing metric, with mean AUROC and AUPR of $0.882$ and $0.318$ respectively, closely followed by performance from the measures of entropy (AUROC and AUPR of $0.878$ and $0.316$ respectively) and aleatoric uncertainty (AUROC and AUPR of $0.877$ and $0.316$ respectively).
-The performance of the S-BGCN-T-K model trained using the pixel prior stands out above the performance of other models trained.
+The performance of the S-BGCN-T-K model stands out above the performance of other models trained.
 This highlights the importance of describing a meaningful prior in advance for the purposes of achieving improved uncertainty estimates.

### 2021-07-08 latex/CEUR/paper.tex
Complete first read through and corrections.

@@
 \begin{abstract}
-In order to adopt deep learning methods in environments where the decisions being made are high-stakes, it is important to have methods which are capable of producing a quantification of the prediction confidence or uncertainty.
-Graph-based convolutional neural networks which are trained to perform classification of multimodal remote sensing data such that the model output represents a Dirichlet distribution parameterization can also be used to obtain measures of prediction uncertainty.
+In order to adopt deep learning methods in environments where the decisions being made are high-stakes, it is important to have methods which are capable of quantifying the prediction confidence or uncertainty.
+Graph-based convolutional neural networks can be trained to perform classification of multimodal remote sensing data using a model output which represents a Dirichlet distribution parameterization.
+This parameterization can then also be used to obtain measures of prediction uncertainty.
 By making a correspondence between a multinomial opinion, as described by subjective logic, and a Dirichlet distribution parameterization, a direct mapping between the two can be performed.
-A multinomial opinion of this kind can produce quantified measures of uncertainty and distinguishes uncertainty due to a lack of evidence (vacuity) and uncertainty due to conflicting evidence (dissonance).
+A multinomial opinion of this kind can produce quantified measures of uncertainty and distinguish uncertainty due to a lack of evidence (vacuity) and uncertainty due to conflicting evidence (dissonance).
 With an appropriately chosen loss function, the graph-based classifier will converge to provide accurate estimates of uncertainty.
-The results presented in this paper show that the measures of uncertainty provided by such models are capable of better distinguishing model misclassifications as well as out-of-distribution data samples than probabilistic measures of uncertainty produced by deterministic neural networks.
+The results presented in this paper show that the measures of uncertainty provided by such models are capable of better distinguishing model misclassifications as well as out-of-distribution data samples than probabilistic measures of uncertainty produced by equivalent deterministic neural networks.
 \end{abstract}
@@
 Each data capturing technique will naturally have its own strengths and weaknesses, inherent to the physically properties of the sensing mode.
-Deterministic classification is only useful up to a point.
+Deterministic classification, while useful, is held back by its inability to express uncertainty.
 Adoption of such techniques will always be limited by the adopter's trust in the predictions.
-Uncertainty estimates will greatly assist trust in models as it will provide a quantification of confidence that might indicate when a prediction is not to be trusted, and more importantly, when a prediction is given with great certainty.
+Uncertainty estimates, however, will greatly assist human trust in models as it will provide a quantification of confidence that might indicate when a prediction is not to be trusted, and more importantly, when a prediction is given with great certainty.
 
@@
 \subsection{Uncertainty measures}
+\label{sec::UncertaintyMeasures}
 From the definitions of the evidential uncertainties presented in \cite{Josang2018}, the measures of vacuity and dissonance have been adopted.
@@
 In order assess the relative ability of evidential uncertainties to express different types of doubt, three commonly used probabilistic measures of uncertainty (aleatoric, epistemic and entropy) are computed to provide comparisons.
-For a Bayesian model with inputs, outputs and parameters denoted $x$, $y$ and $\boldsymbol{\theta}$ respectively, the posterior which will be approximated is $p(\boldsymbol{\theta}\vert\mathcal{D})$, where $\mathcal{D}$ is the observed dataset.
+For a Bayesian model with inputs, outputs and parameters denoted $x$, $y$ and $\boldsymbol{\theta}$ respectively, the posterior, which will be approximated, is $p(\boldsymbol{\theta}\vert\mathcal{D})$, where $\mathcal{D}$ is the observed dataset.
 The total entropy, made up of both aleatoric and epistemic uncertainty \cite{Depeweg2018} is given by
@@
 \end{equation}
-where $\mathbf{Z}^{(l)}$, $\mathbf{Z}^{(l+1)}$ and $\boldsymbol{W}^{(l)}$ are the inputs, outputs and weights of the $\textrm{l}^\textrm{th}$ layer respectively, and $\sigma()$ is a non-linear activation function.
+where $\mathbf{Z}^{(l)}$, $\mathbf{Z}^{(l+1)}$ and $\boldsymbol{W}^{(l)}$ are the inputs, outputs and weights of the $l^\textrm{th}$ layer respectively, and $\sigma()$ is a non-linear activation function.
 For brevity, the tilde operator is used to represent the inclusion of self-connection edges in the graph, i.e.
@@
 To do so, the softmax output activation function used in the output layer of the GCN is substituted for a ReLU function.
-In this way, the model is trained to output non-negative evidence contributions, $\mathbf{E}\in\mathbb{R}^{N\times K}$, where $\mathbf{E}_{i} = \boldsymbol{\alpha}_{i}-\mathbf{1}$ and $\boldsymbol{\alpha}_{i}$ refers to the $K$-dimensional concentration parameters of the $\text{i}^\text{th}$ node.
-In order to train such a model, the loss function is made up of two components; a squared error term which is minimised in order to classify a greater proportion of the nodes correctly and a variance term which is minimized to incentivize the model to provide confident predictions where possible.
+In this way, the model is trained to output non-negative evidence contributions, $\mathbf{E}\in\mathbb{R}^{N\times K}$, where $\mathbf{E}_{i} = \boldsymbol{\alpha}_{i}-\mathbf{1}$ and $\boldsymbol{\alpha}_{i}$ refers to the $K$-dimensional concentration parameters of the $i^\text{th}$ node.
+In order to train such a model, the loss function is made up of two components: a squared error term, which is minimised in order to classify a greater proportion of the nodes correctly, and a variance term, which is minimized to incentivize the model to provide confident predictions where possible.
 This loss, $\mathcal{L}(\boldsymbol{\theta})$, is given by
@@
 Using this assumption, we can use the computed distances on the graph in order to assign contributions of evidence from observed node labels to the other nodes in the graph using a function of our choosing.
-If $d_{ij}$ denotes the shortest path distance between a given node, indexed by $i$ and an observed node, indexed by $j$, then the amount of evidence contributed to suggest that the $\text{i}^\text{th}$ node belongs to the $\text{k}^\text{th}$ class is given by
+If $d_{ij}$ denotes the shortest path distance between a given node, indexed by $i$ and an observed node, indexed by $j$, then the amount of evidence contributed to suggest that the $i^\text{th}$ node belongs to the $k^\text{th}$ class is given by
 \begin{equation}
@@
 where $\sigma$ is a scale parameter which controls the order of distance magnitude over which evidence will propagate in the prior.
-The total evidence to suggest the $\text{i}^\text{th}$ node belongs to the $\text{k}^\text{th}$ class, $e_{ik}$ can be found by summing these contributions over the nodes in the training set such that the element in the prior is given by
+The total evidence to suggest the $i^\text{th}$ node belongs to the $k^\text{th}$ class, $e_{ik}$ can be found by summing these contributions over the nodes in the training set, such that the element in the prior is given by
 \begin{equation}
@@
 \end{equation}
-The KL-divergence between the Dirichlet distribution of the prior and the model output can be incorporated into the loss function using the term
+The KL-divergence between the Dirichlet distribution of the prior and the model output is given by the term
 \begin{equation}
@@
 \end{equation}
-which can, in turn, be incorporated into the total loss.
-Models trained using a prior are denoted using the ``-K'' suffix e.g.
-a S-BGCN-K model would indicate that the graph convolutional network was trained with a loss function using a weighted combination of the loss in (\ref{eq:core_loss}) and the term described in (\ref{eq::teacher_loss}).
+which can, in turn, be incorporated into the total loss function.
+Models trained using a prior are denoted using the ``-K'' suffix.
 
 Table \ref{loss_table} shows how these convergence assistance techniques can be weighted and combined in various permutations to provide a total loss function, $\mathcal{L}_\text{total}(\boldsymbol{\theta})$, as well as the model name abbreviations used to denote which combination has been used.
+The "B" in the model names of Table \ref{loss_table} refers to the fact that dropout inference has been used as a Bayesian approximation, as mentioned in Section \ref{sec::UncertaintyMeasures}.
 The coefficients $\lambda_{\text{T}}$ and $\lambda_{\text{K}}$ are used to control the relative importance of the teacher network and the Dirichlet prior respectively against the importance of the subjective loss function given in (\ref{eq:core_loss}).
@@
 
-The graph was constructed with each $0.5$ m $\times$ $0.5$ m pixels representing a node in the graph.
-Each node has a 52-dimensional feature vector (produced by stacking 3 optical channels, 48 HS channels and 1 LiDAR channel) describing it.
+The graph was constructed with each $0.5$ m $\times$ $0.5$ m pixel representing a node in the graph.
+Each node has a 52-dimensional feature vector describing it (produced by stacking 3 optical channels, 48 HS channels and 1 LiDAR channel).
 The graph edges are computed using a $k$-nearest neighbors algorithm with two nodes receiving an edge connecting them if either node was one of the $k$ nodes which were nearest the other.
@@
 Samples were given weights which were inversely proportional to the number of total samples of each class in the training set.
-These weights were used when computing the loss during training such that the loss related to nodes belonging to under-represented classes were given an increased influence over parameter updates and vice versa.
+These weights were used when computing the loss during training such that the losses related to nodes belonging to under-represented classes were given an increased influence over parameter updates and vice versa.
 
@@
 The kernel weights of the first graph convolutional layer were regularized using an $L_2$ penalization.
-Where dropout inference has been used, the number of samples taken, $M$, was 100.
+Where dropout inference has been used, the number of samples taken was 100.
 
@@
 Given that model uncertainties should provide a measure of the confidence which can be had about a model's predictions, a worthwhile estimate of uncertainty should be able to distinguish model misclassifications from accurate classifications.
-In order to measure a uncertainty output's ability to separate misclassifications, a receiver operating characteristic (ROC) curve and a precision-recall (PR) curve can be computed.
+In order to measure an uncertainty output's ability to separate misclassifications, a receiver operating characteristic (ROC) curve and a precision-recall (PR) curve can be computed.
 The area under the ROC curve and PR curve (AUROC and AUPR respectively) can be used as a single numerical representation of the detection performance, where an area of $1.0$ would represent a perfect discriminator for both metrics.
 
-Models of each type described (as well as benchmark models) were trained and their outputs analysed in produce the AUROC and AUPR values seen in Table \ref{tab::misc_auroc}.
+Models of each type described (as well as benchmark models) were trained and their outputs analysed in order to produce the AUROC and AUPR values seen in Table \ref{tab::misc_auroc}.
 
@@
 It would also be reasonable to expect that uncertainty should be higher when the model is asked to make a prediction using an input which does not resemble the inputs upon which it was trained.
-The relative inability of neural networks' to successfully extrapolate beyond the support of the training data is a well-known weakness of these methods \cite{Lakshminarayanan2017}.
+The relative inability of neural networks to successfully extrapolate beyond the support of the training data is a well-known weakness of these methods \cite{Lakshminarayanan2017}.
 By training models using only a subset of the classes provided by the GT, with the other classes acting as out of distribution (OOD) samples, the OOD detection ability of the uncertainty metrics can be measured.
@@
 The performance of the S-BGCN-T-K model stands out above the performance of other models trained.
-This highlights the importance of describing a meaningful prior in advance for the purposes of achieving improved uncertainty estimates.
+This highlights the importance of the convergence assistance techniques used, particularly the use of a meaningful prior.
 
-The fact that vacuity is the uncertainty measure which best distinguishes OOD nodes for either form of S-BGCN-T-K model reflects intuition.
-Since vacuity measures the absence of evidence for a prediction, it is natural to expect that it would better distinguish OOD nodes for which vacuity is likely higher.
+The fact that vacuity is the uncertainty measure which best distinguishes OOD nodes reflects intuition.
+Since vacuity measures the absence of evidence for a prediction, it is natural to expect that it would better distinguish OOD nodes for which the model ought to have little evidence to support its predictions.
 
@@
 
-In this paper we have presented a novel method for providing uncertainties while perfoming multi-class classification of multimodal remote sensing data.
+In this paper we have adapted a novel classification method capable of providing uncertainty estimates to the task of multi-class classification of multimodal remote sensing data.
 The adopted framework, based upon the theory of Subjective Logic, provides measures of vacuity and dissonance which are better capable of identifying misclassifications and out of distribution samples than the alternative probabilistic measures of uncertainty assessed.
@@
 This represents a promising avenue for uncertainty-aware learning in the task of multimodal remote sensing classification.
-The development of algorithms which can be used to better distinguish misclassified nodes and OOD nodes and thus can better quantify confidence, is important for real-world applications where the consequences of misplaced model certainty can be high-stake.
 
-The presented results have illustrated an improvement in the quality of uncertainty estimates obtained through the use of a prior.
+The presented results have illustrated the importance of convergence assistance techniques as a means for improving the quality of uncertainty estimates, particularly through the use of a prior.
 This can be seen by comparing the S-BGCN-T-K misclassification detection and OOD detection performance with equivalent models which do not use a prior, e.g. S-BGCN-T.
@@
 Future work should consider the generalisation potential of this method by considering its performance on other challenging remote sensing classification datasets.
-There is also scope for research into how the choice of method for computing the $\hat{\boldsymbol{\alpha}}$ prior affects the quality of uncertainty estimates, either by varying the scale parameter $\sigma$ or considering different prior computation methods entirely.
+There is also scope for research into how the choice of method for computing the $\hat{\boldsymbol{\alpha}}$ prior affects the quality of uncertainty estimates, either by varying the scale parameter, $\sigma$, or considering different prior computation methods entirely.
 %% The acknowledgments section is defined using the "acknowledgments" environment

### 2021-07-09 latex/CEUR/paper.tex
Fixed some -ise to -ize word endings.

@@
 \begin{abstract}
-In order to adopt deep learning methods in environments where the decisions being made are high-stakes, it is important to have methods which are capable of quantifying the prediction confidence or uncertainty.
+In order to adopt deep learning methods in environments where the decisions being made are high-stakes, it is important the methods are capable of quantifying the prediction confidence or uncertainty.
 Graph-based convolutional neural networks can be trained to perform classification of multimodal remote sensing data using a model output which represents a Dirichlet distribution parameterization.
@@
 The capability of algorithms to provide accurate measures of confidence and uncertainty is important if they are to be adopted in real-world scenarios where the stakes can be high \cite{Goodman2017}.
-Although deep learning methods are often capable of producing high-accuracy predictions \cite{LeCun2015, LiangpeiZhang2016}, they are generally criticised for being unable to express when to have confidence in the prediction and when the prediction should be presented as uncertain.
+Although deep learning methods are often capable of producing high-accuracy predictions \cite{LeCun2015, LiangpeiZhang2016}, they are generally criticized for being unable to express when to have confidence in the prediction and when the prediction should be presented as uncertain.
 If deep learning models are to be integrated reliably into real-world decision making processes, it is of vital importance that the methods being used are capable of accurately expressing uncertainty.
@@
 Adoption of such techniques will always be limited by the adopter's trust in the predictions.
-Uncertainty estimates, however, will greatly assist human trust in models as it will provide a quantification of confidence that might indicate when a prediction is not to be trusted, and more importantly, when a prediction is given with great certainty.
+Uncertainty estimates, however, will greatly assist human trust in models, as it will provide a quantification of confidence that might indicate when a prediction is not to be trusted, and more importantly, when a prediction is given with great certainty.
 
-In this paper, we have analysed how well different measures of model uncertainty perform the task of identifying misclassifications, as well as whether they can be used to identify data points which belong from a distribution other than those observed during training (out of distribution detection).
+In this paper, we have analyzed how well different measures of model uncertainty perform the task of identifying misclassifications, as well as whether they can be used to identify data points which belong from a distribution other than those observed during training (out of distribution detection).
 To do so, we have used graph-based neural network architectures that are adapted to provide subjective opinions (as described in the field of belief or evidence theory \cite{Josang2018}) through the use of Dirichlet distribution parameterizations \cite{Kipf2017, ZhaoXujiang2020}.
@@
 
-The remainder of this paper is organised as follows: Section \ref{sec::unc_framework} describes the uncertainty framework adopted in the methods presented, Section \ref{sec::GraphNetworkArchitecture} details the construction of the graph-based neural networks used, Section \ref{sec::results} presents an analysis of results and Section \ref{sec::conclusion} summarises and draws conclusions as well as suggests areas for future work.
+The remainder of this paper is organized as follows: Section \ref{sec::unc_framework} describes the uncertainty framework adopted in the methods presented, Section \ref{sec::GraphNetworkArchitecture} details the construction of the graph-based neural networks used, Section \ref{sec::results} presents an analysis of results and Section \ref{sec::conclusion} summarizes and draws conclusions as well as suggests areas for future work.
 
@@
 The framework described in this section is the same as is described by the work of \cite{ZhaoXujiang2020} where they use the approach to perform semi-supervised classification of benchmark graph classification datasets including Cora and Pubmed.
-The method they present has been adapted in order to perform the task of multimodal remote sensing classification.
+The method they present has been adapted here in order to perform the task of multimodal remote sensing classification.
 
@@
 
-The graph convolutional networks used are of the form proposed by \cite{Kipf2017}, where the graph convolutional layer is given by
+The graph convolutional networks (GCNs) used are of the form proposed by \cite{Kipf2017}, where the graph convolutional layer is given by
 \begin{equation}
@@
 In this way, the model is trained to output non-negative evidence contributions, $\mathbf{E}\in\mathbb{R}^{N\times K}$, where $\mathbf{E}_{i} = \boldsymbol{\alpha}_{i}-\mathbf{1}$ and $\boldsymbol{\alpha}_{i}$ refers to the $K$-dimensional concentration parameters of the $i^\text{th}$ node.
-In order to train such a model, the loss function is made up of two components: a squared error term, which is minimised in order to classify a greater proportion of the nodes correctly, and a variance term, which is minimized to incentivize the model to provide confident predictions where possible.
+In order to train such a model, the loss function is made up of two components: a squared error term, which is minimized in order to classify a greater proportion of the nodes correctly, and a variance term, which is minimized to incentivize the model to provide confident predictions where possible.
 This loss, $\mathcal{L}(\boldsymbol{\theta})$, is given by
@@
 In order to assist the convergence of subjective models, two additional assistance techniques have been used: teacher knowledge distillation and the use of a Dirichlet prior.
-These methods have been shown to allow subjective models to provide better uncertainty estimates \cite{ZhaoXujiang2020}.
+These have been shown to allow subjective models to provide better uncertainty estimates \cite{ZhaoXujiang2020}.
 \subsubsection{Teacher knowledge distillation}
@@
 Samples were given weights which were inversely proportional to the number of total samples of each class in the training set.
-These weights were used when computing the loss during training such that the losses related to nodes belonging to under-represented classes were given an increased influence over parameter updates and vice versa.
+These weights such that the losses related to nodes belonging to under-represented classes were given an increased influence over parameter updates and vice versa.
 
@@
 
-Models of each type described (as well as benchmark models) were trained and their outputs analysed in order to produce the AUROC and AUPR values seen in Table \ref{tab::misc_auroc}.
+Models of each type described (as well as benchmark models) were trained and their outputs analyzed in order to produce the AUROC and AUPR values seen in Table \ref{tab::misc_auroc}.
 

### 2021-07-09 latex/CEUR/paper.tex
.pdf back within 6 pages again

@@
 The framework described in this section is the same as is described by the work of \cite{ZhaoXujiang2020} where they use the approach to perform semi-supervised classification of benchmark graph classification datasets including Cora and Pubmed.
-The method they present has been adapted here in order to perform the task of multimodal remote sensing classification.
+The method they present has been adapted here to perform the task of multimodal remote sensing classification.
 
@@
 The exact method chosen to provide $\hat{\boldsymbol{\alpha}}$ will depend on the nature of the problem but we will assume nodes which are nearby in the graph are more likely to belong to the same output class than nodes which are far apart, a property known as homophily \cite{HuangQian2019}.
-Using this assumption, we can use the computed distances on the graph in order to assign contributions of evidence from observed node labels to the other nodes in the graph using a function of our choosing.
+Using this assumption, we can use the computed distances on the graph to assign contributions of evidence from observed node labels to the other nodes in the graph using a function of our choosing.
 If $d_{ij}$ denotes the shortest path distance between a given node, indexed by $i$ and an observed node, indexed by $j$, then the amount of evidence contributed to suggest that the $i^\text{th}$ node belongs to the $k^\text{th}$ class is given by
@@
     \begin{cases}
-    \frac{1}{\sqrt{2\pi\sigma^2}}\exp{\left(\frac{-d_{ij}^2}{2\sigma^2}\right)}, & \text{if } y_{jk}=1,\\
+      \frac{\exp{\left(\frac{-d_{ij}^2}{2\sigma^2}\right)}}{\left(2\pi\sigma^2\right)^{1/2}}, & \text{if } y_{jk}=1,\\
     0, & \text{otherwise},
@@
 
-\begin{table}
+\begin{table}[!t]
 \scriptsize
@@
 Samples were given weights which were inversely proportional to the number of total samples of each class in the training set.
-These weights such that the losses related to nodes belonging to under-represented classes were given an increased influence over parameter updates and vice versa.
+This allows the losses related to nodes from under-represented classes to have an increased influence over parameter updates and vice versa.
 
@@
 
-Each test was performed for different random dataset splits and model weight initializations in order to obtain mean and standard deviation measures of performance.
+Each test was performed for different random dataset splits and model weight initializations to obtain mean and standard deviation measures of performance.
 
-Benchmark models presented include the `vanilla' GCN (which can provide uncertainty via entropy) and the Drop-GCN which is a GCN where dropout inference has been applied in order to produce estimates of aleatoric and epistemic uncertainty in addition to entropy.
-
-\subsection{Misclassification detection}
-
-Given that model uncertainties should provide a measure of the confidence which can be had about a model's predictions, a worthwhile estimate of uncertainty should be able to distinguish model misclassifications from accurate classifications.
-In order to measure an uncertainty output's ability to separate misclassifications, a receiver operating characteristic (ROC) curve and a precision-recall (PR) curve can be computed.
-The area under the ROC curve and PR curve (AUROC and AUPR respectively) can be used as a single numerical representation of the detection performance, where an area of $1.0$ would represent a perfect discriminator for both metrics.
-
-Models of each type described (as well as benchmark models) were trained and their outputs analyzed in order to produce the AUROC and AUPR values seen in Table \ref{tab::misc_auroc}.
+Benchmark models presented include the `vanilla' GCN (which can provide uncertainty via entropy) and the Drop-GCN which is a GCN where dropout inference has been applied to produce estimates of aleatoric and epistemic uncertainty in addition to entropy.
 
@@
 
+\subsection{Misclassification detection}
+
+Given that model uncertainties should provide a measure of the confidence which can be had about a model's predictions, a worthwhile estimate of uncertainty should be able to distinguish model misclassifications from accurate classifications.
+In order to measure an uncertainty output's ability to separate misclassifications, a receiver operating characteristic (ROC) curve and a precision-recall (PR) curve can be computed.
+The area under the ROC curve and PR curve (AUROC and AUPR respectively) can be used as a single numerical representation of the detection performance, where an area of $1.0$ would represent a perfect discriminator for both metrics.
+
+Models of each type described (as well as benchmark models) were trained and their outputs analyzed to produce the AUROC and AUPR values seen in Table \ref{tab::misc_auroc}.
+
 % \begin{table*}[!t]
@@
 
-The S-BGCN-T-K model trained achieves the highest ranked misclassification detection performance, with the uncertainty measured by entropy providing the best distinguishing metric, with AUROC and AUPR of $0.912$ and $0.672$ respectively, closely followed by the performance achieved by the measures of vacuity (AUROC and AUPR of $0.908$ and $0.659$ respectively) and aleatoric uncertainty (AUROC and AUPR of $0.905$ and $0.649$ respectively).
+The S-BGCN-T-K model achieves the best misclassification detection performance, with the uncertainty measured by entropy providing the best distinguishing metric, with AUROC and AUPR of $0.912$ and $0.672$ respectively, closely followed by the performance achieved by the measures of vacuity (AUROC and AUPR of $0.908$ and $0.659$ respectively) and aleatoric uncertainty (AUROC and AUPR of $0.905$ and $0.649$ respectively).
 
@@
 
-The presented results have illustrated the importance of convergence assistance techniques as a means for improving the quality of uncertainty estimates, particularly through the use of a prior.
+The presented results illustrate the importance of convergence assistance techniques as a means for improving the quality of uncertainty estimates, particularly through the use of a prior.
 This can be seen by comparing the S-BGCN-T-K misclassification detection and OOD detection performance with equivalent models which do not use a prior, e.g. S-BGCN-T.
-Of the uncertainty measures produced by the presented S-BGCN-T-K model, the measures of vacuity, aleatoric uncertainty or entropy all provide near-best performance for the task of identifying misclassifications.
+Of the uncertainty measures produced by the S-BGCN-T-K model, the measures of vacuity, aleatoric uncertainty or entropy all provide near-best performance for the identifying misclassifications.
 In order to identify OOD nodes, the measure of vacuity stands out as the best-performing uncertainty metric.
 
-Future work should consider the generalisation potential of this method by considering its performance on other challenging remote sensing classification datasets.
+Future work should consider the generalisation potential of this method by assessing performance on other challenging remote sensing classification datasets.
 There is also scope for research into how the choice of method for computing the $\hat{\boldsymbol{\alpha}}$ prior affects the quality of uncertainty estimates, either by varying the scale parameter, $\sigma$, or considering different prior computation methods entirely.

### 2021-07-13 latex/CEUR/paper.tex
Update author info

@@
 
-\author[1]{A Nother}[orcid=0000-0000-0000-0000, email=another@vu.nl,]
+\author[1,2]{Andrea~Marinoni}[orcid=0000-0001-6789-0915, email=andrea.marinoni@uit.no,]
 
-\author[1]{A Nother}[orcid=0000-0000-0000-0000,email=another@acm.org,]
+\author[1]{Sivasakthy~Selvakumaran}[orcid=0000-0002-8591-0702,email=ss683@cam.ac.uk,]
 

### 2021-07-14 latex/CEUR/paper.tex
Making changes from Sakthy/Andrea feedback

@@
 % This command is for the conference information
-\conference{Proceedings of the CIKM 2021 Workshops, November 01--05, 2021, Online}
+\conference{Proceedings of the CIKM 2021 Workshops, November 1-5, Online}
 
 % The "title" command
-\title{Uncertainty-aware graph-based multimodal remote sensing classification}
+\title{Uncertainty-aware graph-based multimodal remote sensing}
 
@@
 Although deep learning methods are often capable of producing high-accuracy predictions \cite{LeCun2015, LiangpeiZhang2016}, they are generally criticized for being unable to express when to have confidence in the prediction and when the prediction should be presented as uncertain.
-If deep learning models are to be integrated reliably into real-world decision making processes, it is of vital importance that the methods being used are capable of accurately expressing uncertainty.
+If deep learning models are to be integrated reliably into real-world decision making processes, it is of vital importance that the methods being used are capable of accurately expressing uncertainty \cite{Lee2004}.
 
-With remotely-sensed data being available with ever-greater temporal and spatial resolutions, the development of computational processing methods which are capable of robustly handling such large volumes of data will assist countless earth-monitoring applications.
-Specifically, with data being captured now using a wide range of capturing techniques with complementary strengths, the ability to combine this data into a multimodal analysis will allow each data mode to interact synergistically to provide better results than any individual data mode would produce in isolation.
-Each data capturing technique will naturally have its own strengths and weaknesses, inherent to the physically properties of the sensing mode.
+With remotely-sensed data being available with ever-greater temporal and spatial resolutions, the development of computational processing methods which are capable of robustly handling such large volumes of data will assist countless earth-monitoring applications \cite{Chi2016}.
+Specifically, with data being captured now using a wide range of techniques with complementary strengths, the ability to combine this data into a multimodal analysis will allow each data mode to interact synergistically to provide better results than any individual data mode would produce in isolation.
+Each data capturing technique will naturally have its own strengths and weaknesses, inherent to the physical properties of the sensing mode \cite{Chlaily2021, Marinoni2021}.
 Deterministic classification, while useful, is held back by its inability to express uncertainty.
 Adoption of such techniques will always be limited by the adopter's trust in the predictions.
-Uncertainty estimates, however, will greatly assist human trust in models, as it will provide a quantification of confidence that might indicate when a prediction is not to be trusted, and more importantly, when a prediction is given with great certainty.
+Uncertainty estimates, however, will greatly assist human trust in models, as it will provide a quantification of confidence that might indicate when a prediction is not to be trusted, and more importantly, when a prediction is given with great certainty \cite{Chakraborty2017}.
 
-In this paper, we have analyzed how well different measures of model uncertainty perform the task of identifying misclassifications, as well as whether they can be used to identify data points which belong from a distribution other than those observed during training (out of distribution detection).
+In this paper, we have analyzed how well different measures of model uncertainty perform the task of identifying data points which belong from a distribution other than those observed during training (out of distribution detection).
 To do so, we have used graph-based neural network architectures that are adapted to provide subjective opinions (as described in the field of belief or evidence theory \cite{Josang2018}) through the use of Dirichlet distribution parameterizations \cite{Kipf2017, ZhaoXujiang2020}.
@@
 
-The framework described in this section is the same as is described by the work of \cite{ZhaoXujiang2020} where they use the approach to perform semi-supervised classification of benchmark graph classification datasets including Cora and Pubmed.
-The method they present has been adapted here to perform the task of multimodal remote sensing classification.
+% The framework described in this section is the same as is described by the work of \cite{ZhaoXujiang2020} where they use the approach to perform semi-supervised classification of benchmark graph classification datasets including Cora and Pubmed.
+% The method they present has been adapted here to perform the task of multimodal remote sensing classification.
 
@@
 where $\mathcal{H}()$ computes the differential entropy of a distribution.
-Aleatoric uncertainty, which accounts for noise inherent to the data observations \cite{Kendall2017}, is given by
-\begin{equation}
-    \mathbb{E}_{p\left(\boldsymbol{\theta}\vert \mathcal{D}\right)}\left[\mathcal{H}(p(y\vert x; \boldsymbol{\theta}))\right].
-\end{equation}
-The epistemic uncertainty, therefore, is given by the difference between these two quantities
-\begin{equation}
-    \mathcal{H}\left(\mathbb{E}_{p(\boldsymbol{\theta}\vert \mathcal{D})}\left[p(y\vert x;\boldsymbol{\theta}\right]\right)-\mathbb{E}_{p\left(\boldsymbol{\theta}\vert \mathcal{D}\right)}\left[\mathcal{H}(p(y\vert x; \boldsymbol{\theta}))\right].
-\label{eq::epistemic}
-\end{equation}
-In order to compute the above expressions for aleatoric and epistemic uncertainty, the posterior distribution over models is approximated by samples obtained using dropout inference \cite{Gal2016}.
+% Aleatoric uncertainty, which accounts for noise inherent to the data observations \cite{Kendall2017}, is given by
+% \begin{equation}
+%     \mathbb{E}_{p\left(\boldsymbol{\theta}\vert \mathcal{D}\right)}\left[\mathcal{H}(p(y\vert x; \boldsymbol{\theta}))\right].
+% \end{equation}
+% The epistemic uncertainty, therefore, is given by the difference between these two quantities
+% \begin{equation}
+%     \mathcal{H}\left(\mathbb{E}_{p(\boldsymbol{\theta}\vert \mathcal{D})}\left[p(y\vert x;\boldsymbol{\theta}\right]\right)-\mathbb{E}_{p\left(\boldsymbol{\theta}\vert \mathcal{D}\right)}\left[\mathcal{H}(p(y\vert x; \boldsymbol{\theta}))\right].
+% \label{eq::epistemic}
+% \end{equation}
+% In order to compute the above expressions for aleatoric and epistemic uncertainty, the posterior distribution over models is approximated by samples obtained using dropout inference \cite{Gal2016}.
 
@@
 
+In order to measure an uncertainty output's ability to separate misclassifications, a receiver operating characteristic (ROC) curve and a precision-recall (PR) curve can be computed.
+The area under the ROC curve and PR curve (AUROC and AUPR respectively) can be used as a single numerical representation of the detection performance, where an area of $1.0$ would represent a perfect discriminator for both metrics.
+
 % The exact types and abundances of these classes can be found in Table \ref{tab::classes}.
@@
 
-Benchmark models presented include the `vanilla' GCN (which can provide uncertainty via entropy) and the Drop-GCN which is a GCN where dropout inference has been applied to produce estimates of aleatoric and epistemic uncertainty in addition to entropy.
-
-\begin{table*}[!t]
-\renewcommand{\arraystretch}{1.3}
-\caption{Misclassification detection: Ability of each uncertainty type to detect misclassifications (measured by AUROC and AUPR).}
-\label{tab::misc_auroc}
-\scriptsize
-\begin{center}
-\begin{tabular}{Y|ccccc|ccccc}
-\hline
-\multirow{2}{*}{Model}  & \multicolumn{5}{c}{AUROC}\vline&\multicolumn{5}{c}{AUPR}        \\
-                        & Vac. & Dis. & Ale. & Epi. & Ent. & Vac. & Dis. & Ale. & Epi. & Ent. \\ \hline 
-% S-BGCN-T-K (superpixel prior) & $0.676$ & $0.801$ &$0.792$&$0.509$&$0.798$&$0.352$&$0.398$&$0.467$&$0.237$&$0.474$    \\
-S-BGCN-T-K  & $0.908$ & $0.840$ &$0.905$&$0.451$&$\mathbf{0.912}$&$0.659$&$0.545$&$0.649$&$0.206$&$\mathbf{0.672}$  \\
-S-BGCN-T & $0.729$ & $0.834$ &$0.869$&$0.618$&$0.861$&$0.451$&$0.484$&$0.591$&$0.278$&$0.579$  \\ 
-S-BGCN & $0.760$ & $0.877$ &$0.894$&$0.623$&$0.886$&$0.489$&$0.558$&$0.633$&$0.268$&$0.616$  \\ 
-S-GCN & $0.729$ & $0.842$ &-&-&$0.859$&$0.472$&$0.538$&-&-&$0.595$  \\ 
-S-MLP &$0.845$&$0.904$&-&-&$0.909$&$0.417$&$0.566$&-&-&$0.606$  \\
-GCN & - & - &-&-&$0.887$&-&-&-&-&$0.606$  \\ 
-Drop-GCN & - & - &$0.897$&$0.552$&$0.887$&-&-&$0.619$&$0.243$&$0.600$  \\ \hline
-\end{tabular}
-\end{center}
-\end{table*}
-
-\subsection{Misclassification detection}
-
-Given that model uncertainties should provide a measure of the confidence which can be had about a model's predictions, a worthwhile estimate of uncertainty should be able to distinguish model misclassifications from accurate classifications.
-In order to measure an uncertainty output's ability to separate misclassifications, a receiver operating characteristic (ROC) curve and a precision-recall (PR) curve can be computed.
-The area under the ROC curve and PR curve (AUROC and AUPR respectively) can be used as a single numerical representation of the detection performance, where an area of $1.0$ would represent a perfect discriminator for both metrics.
-
-Models of each type described (as well as benchmark models) were trained and their outputs analyzed to produce the AUROC and AUPR values seen in Table \ref{tab::misc_auroc}.
+Benchmark models presented include the `standard' GCN (which can provide uncertainty via entropy) and the Drop-GCN which is a GCN where dropout inference has been applied to produce estimates of aleatoric and epistemic uncertainty in addition to entropy.
 
@@
 % \renewcommand{\arraystretch}{1.3}
-% \caption{Misclassification detection: Ability of each uncertainty type to detect misclassifications (measured by the AUPR metric).}
-% \label{tab::misc_aupr}
+% \caption{Misclassification detection: Ability of each uncertainty type to detect misclassifications (measured by AUROC and AUPR).}
+% \label{tab::misc_auroc}
 % \scriptsize
 % \begin{center}
-% \begin{tabular}{cccccc}
+% \begin{tabular}{Y|ccccc|ccccc}
 % \hline
-% \multirow{2}{*}{Model}  & \multicolumn{5}{c}{AUPR}             \\
-%       & Vac. & Dis. & Ale. & Epi. & Ent. \\ \hline 
-% S-BGCN-T-K (superpixel prior) & $0.352$&$0.398$&$0.467$&$0.237$&$0.474$ \\
-% S-BGCN-T-K (pixel prior) & $0.659$&$0.545$&$0.649$&$0.206$&$\mathbf{0.672}$ \\
-% S-BGCN-T & $0.451$&$0.484$&$0.591$&$0.278$&$0.579$ \\ 
-% S-BGCN & $0.489$ & $0.558$  &$0.633$&$0.268$&$0.616$ \\ 
-% S-GCN & $0.472$ & $0.538$  &-&-&$0.595$ \\ 
-% S-MLP & $0.417$&$0.566$&-&-&$0.616$ \\
-% GCN & - & -  &-&-&$0.606$ \\ 
-% Drop-GCN & - & -  & $0.619$&$0.243$&$0.600$ \\ \hline
+% \multirow{2}{*}{Model}  & \multicolumn{5}{c}{AUROC}\vline&\multicolumn{5}{c}{AUPR}        \\
+%                         & Vac. & Dis. & Ale. & Epi. & Ent. & Vac. & Dis. & Ale. & Epi. & Ent. \\ \hline 
+% % S-BGCN-T-K (superpixel prior) & $0.676$ & $0.801$ &$0.792$&$0.509$&$0.798$&$0.352$&$0.398$&$0.467$&$0.237$&$0.474$    \\
+% S-BGCN-T-K  & $0.908$ & $0.840$ &$0.905$&$0.451$&$\mathbf{0.912}$&$0.659$&$0.545$&$0.649$&$0.206$&$\mathbf{0.672}$  \\
+% S-BGCN-T & $0.729$ & $0.834$ &$0.869$&$0.618$&$0.861$&$0.451$&$0.484$&$0.591$&$0.278$&$0.579$  \\ 
+% S-BGCN & $0.760$ & $0.877$ &$0.894$&$0.623$&$0.886$&$0.489$&$0.558$&$0.633$&$0.268$&$0.616$  \\ 
+% S-GCN & $0.729$ & $0.842$ &-&-&$0.859$&$0.472$&$0.538$&-&-&$0.595$  \\ 
+% S-MLP &$0.845$&$0.904$&-&-&$0.909$&$0.417$&$0.566$&-&-&$0.606$  \\
+% GCN & - & - &-&-&$0.887$&-&-&-&-&$0.606$  \\ 
+% Drop-GCN & - & - &$0.897$&$0.552$&$0.887$&-&-&$0.619$&$0.243$&$0.600$  \\ \hline
 % \end{tabular}
@@
 
-The S-BGCN-T-K model achieves the best misclassification detection performance, with the uncertainty measured by entropy providing the best distinguishing metric, with AUROC and AUPR of $0.912$ and $0.672$ respectively, closely followed by the performance achieved by the measures of vacuity (AUROC and AUPR of $0.908$ and $0.659$ respectively) and aleatoric uncertainty (AUROC and AUPR of $0.905$ and $0.649$ respectively).
+% \subsection{Misclassification detection}
+% 
+% Given that model uncertainties should provide a measure of the confidence which can be had about a model's predictions, a worthwhile estimate of uncertainty should be able to distinguish model misclassifications from accurate classifications.
+% 
+% 
+% Models of each type described (as well as benchmark models) were trained and their outputs analyzed to produce the AUROC and AUPR values seen in Table \ref{tab::misc_auroc}.
+% 
+% % \begin{table*}[!t]
+% % \renewcommand{\arraystretch}{1.3}
+% % \caption{Misclassification detection: Ability of each uncertainty type to detect misclassifications (measured by the AUPR metric).}
+% % \label{tab::misc_aupr}
+% % \scriptsize
+% % \begin{center}
+% % \begin{tabular}{cccccc}
+% % \hline
+% % \multirow{2}{*}{Model}  & \multicolumn{5}{c}{AUPR}             \\
+% %       & Vac. & Dis. & Ale. & Epi. & Ent. \\ \hline 
+% % S-BGCN-T-K (superpixel prior) & $0.352$&$0.398$&$0.467$&$0.237$&$0.474$ \\
+% % S-BGCN-T-K (pixel prior) & $0.659$&$0.545$&$0.649$&$0.206$&$\mathbf{0.672}$ \\
+% % S-BGCN-T & $0.451$&$0.484$&$0.591$&$0.278$&$0.579$ \\ 
+% % S-BGCN & $0.489$ & $0.558$  &$0.633$&$0.268$&$0.616$ \\ 
+% % S-GCN & $0.472$ & $0.538$  &-&-&$0.595$ \\ 
+% % S-MLP & $0.417$&$0.566$&-&-&$0.616$ \\
+% % GCN & - & -  &-&-&$0.606$ \\ 
+% % Drop-GCN & - & -  & $0.619$&$0.243$&$0.600$ \\ \hline
+% % \end{tabular}
+% % \end{center}
+% % \end{table*}
+% 
+% The S-BGCN-T-K model achieves the best misclassification detection performance, with the uncertainty measured by entropy providing the best distinguishing metric, with AUROC and AUPR of $0.912$ and $0.672$ respectively, closely followed by the performance achieved by the measures of vacuity (AUROC and AUPR of $0.908$ and $0.659$ respectively) and aleatoric uncertainty (AUROC and AUPR of $0.905$ and $0.649$ respectively).
 
@@
 Each model type was assessed over the same 10 sampled OOD class pairs for fairness.
-The AUROC and AUPR values measured can be found in Table \ref{tab::ood_auroc} and Table \ref{tab::ood_aupr} respectively.
+The AUROC and AUPR values measured can be found in Table \ref{tab::ood}.
 
@@
 \renewcommand{\arraystretch}{1.3}
-\caption{OOD detection: Ability of each uncertainty type to detect OOD nodes (measured by the AUROC metric). Values shown represent the mean $\pm$ standard deviation.}
-\label{tab::ood_auroc}
+\caption{OOD detection: Ability of each uncertainty type to detect OOD nodes (measured by the AUROC and AUPR metrics). Values shown represent the mean $\pm$ standard deviation.}
+\label{tab::ood}
 \scriptsize
 \begin{center}
-\begin{tabular}{Y|ccccc}
+\begin{tabular}{Y|ccc|ccc}
 \hline
-\multirow{2}{*}{Model}  & \multicolumn{5}{c}{AUROC}             \\
-      & Vacuity & Dissonance & Aleatoric & Epistemic & Entropy \\ \hline 
+\multirow{2}{*}{Model}  & \multicolumn{3}{c|}{AUROC} & \multicolumn{3}{c}{AUPR} \\
+                        & Vacuity & Dissonance & Entropy & Vacuity & Dissonance & Entropy\\ \hline 
 % S-BGCN-T-K (superpixel prior) & $0.839\pm0.092$ & $0.691\pm0.173$ &$0.831\pm0.079$&$0.268\pm0.180$&$0.833\pm0.076$    \\           
-S-BGCN-T-K & $\mathbf{0.882\pm0.085}$ & $0.605\pm0.197$ &$0.877\pm0.089$&$0.193\pm0.107$&$0.878\pm0.089$    \\        
-S-BGCN-T & $0.588\pm0.147$ & $0.664\pm0.133$ &$0.593\pm0.188$&$0.396\pm0.096$&$0.578\pm0.186$    \\ 
-S-BGCN & $0.586\pm0.147$ & $0.666\pm0.132$ &$0.596\pm0.193$&$0.401\pm0.092$&$0.580\pm0.191$    \\ 
-S-GCN & $0.580\pm0.145$ & $0.650\pm0.120$ &-&-&$0.586\pm0.181$    \\ 
-S-MLP & $0.767\pm0.152$ & $0.805\pm0.114$ &-&-&$0.787\pm0.125$    \\   
-GCN & - & - &-&-&$0.538\pm0.188$    \\ 
-Drop-GCN & - & - &$0.541\pm0.185$&$0.420\pm0.161$&$0.538\pm0.187$    \\ \hline
+S-BGCN-T-K & $\mathbf{0.882\pm0.085}$ & $0.605\pm0.197$ & $0.878\pm0.089$ & $\mathbf{0.318\pm0.289}$ & $0.132\pm0.184$ & $0.316\pm0.306$  \\        
+S-BGCN-T & $0.588\pm0.147$ & $0.664\pm0.133$ & $0.578\pm0.186$ & $0.128\pm0.187$ & $0.137\pm0.192$ & $0.143\pm0.208$   \\ 
+S-BGCN & $0.586\pm0.147$ & $0.666\pm0.132$ & $0.580\pm0.191$ & $0.127\pm0.186$ & $0.139\pm0.190$ & $0.145\pm0.209$  \\ 
+S-GCN & $0.580\pm0.145$ & $0.650\pm0.120$ & $0.586\pm0.181 $ & $0.125\pm0.185$ & $0.130\pm0.191$ & $0.143\pm0.207$   \\ 
+S-MLP & $0.767\pm0.152$ & $0.805\pm0.114$ & $0.787\pm0.125$ & $0.245\pm0.214$ & $0.233\pm0.170$ & $0.219\pm0.201$   \\   
+GCN & - & - & $0.538\pm0.188$ & - & - & $0.116\pm0.179$  \\ 
+Drop-GCN & - & - & $0.538\pm0.187$ & - & - & $0.116\pm0.179$  \\ \hline
 \end{tabular}
@@
 
-\begin{table*}[!t]
-\renewcommand{\arraystretch}{1.3}
-\caption{OOD detection: Ability of each uncertainty type to detect OOD nodes (measured by the AUPR metric). Values shown represent the mean $\pm$ standard deviation.}
-\label{tab::ood_aupr}
-\scriptsize
-\begin{center}
-\begin{tabular}{Y|ccccc}
-\hline
-\multirow{2}{*}{Model}  & \multicolumn{5}{c}{AUPR}             \\
-      & Vacuity & Dissonance & Aleatoric & Epistemic & Entropy \\ \hline 
-% S-BGCN-T-K (superpixel prior) &$0.234\pm0.252$&$0.142\pm0.185$&$0.214\pm0.249$&$0.099\pm0.227$&$0.212\pm0.251$    \\   
-S-BGCN-T-K &$\mathbf{0.318\pm0.289}$&$0.132\pm0.184$&$0.316\pm0.306$&$0.082\pm0.178$&$0.316\pm0.306$    \\        
-S-BGCN-T &$0.128\pm0.187$&$0.137\pm0.192$&$0.148\pm0.211$&$0.095\pm0.193$&$0.143\pm0.208$    \\ 
-S-BGCN & $0.127\pm0.186$ & $0.139\pm0.190$  &$0.150\pm0.213$&$0.095\pm0.195$&$0.145\pm0.209$    \\ 
-S-GCN & $0.125\pm0.185$ & $0.130\pm0.191$  &-&-&$0.143\pm0.207$    \\ 
-S-MLP & $0.245\pm0.214$ & $0.233\pm0.170$ &-&-&$0.219\pm0.201$    \\   
-GCN & - & -  &-&-&$0.116\pm0.179$    \\ 
-Drop-GCN & - & -  & $0.116\pm0.179$&$0.115\pm0.257$&$0.116\pm0.179$    \\ \hline
-\end{tabular}
-\end{center}
-\end{table*}
+% \begin{table*}[!t]
+% \renewcommand{\arraystretch}{1.3}
+% \caption{OOD detection: Ability of each uncertainty type to detect OOD nodes (measured by the AUPR metric). Values shown represent the mean $\pm$ standard deviation.}
+% \label{tab::ood_aupr}
+% \scriptsize
+% \begin{center}
+% \begin{tabular}{Y|ccccc}
+% \hline
+% \multirow{2}{*}{Model}  & \multicolumn{5}{c}{AUPR}             \\
+%       & Vacuity & Dissonance & Aleatoric & Epistemic & Entropy \\ \hline 
+% % S-BGCN-T-K (superpixel prior) &$0.234\pm0.252$&$0.142\pm0.185$&$0.214\pm0.249$&$0.099\pm0.227$&$0.212\pm0.251$    \\   
+% S-BGCN-T-K &$\mathbf{0.318\pm0.289}$&$0.132\pm0.184$&$0.316\pm0.306$&$0.082\pm0.178$&$0.316\pm0.306$    \\        
+% S-BGCN-T &$0.128\pm0.187$&$0.137\pm0.192$&$0.148\pm0.211$&$0.095\pm0.193$&$0.143\pm0.208$    \\ 
+% S-BGCN & $0.127\pm0.186$ & $0.139\pm0.190$  &$0.150\pm0.213$&$0.095\pm0.195$&$0.145\pm0.209$    \\ 
+% S-GCN & $0.125\pm0.185$ & $0.130\pm0.191$  &-&-&$0.143\pm0.207$    \\ 
+% S-MLP & $0.245\pm0.214$ & $0.233\pm0.170$ &-&-&$0.219\pm0.201$    \\   
+% GCN & - & -  &-&-&$0.116\pm0.179$    \\ 
+% Drop-GCN & - & -  & $0.116\pm0.179$&$0.115\pm0.257$&$0.116\pm0.179$    \\ \hline
+% \end{tabular}
+% \end{center}
+% \end{table*}
 
-As for the task of misclassification detection, the S-BGCN-T-K model is the highest ranked model.
+For the task of OOD detection, the S-BGCN-T-K model is the highest ranked model.
 Its measure of vacuity uncertainty provided the best distinguishing metric, with mean AUROC and AUPR of $0.882$ and $0.318$ respectively, closely followed by performance from the measures of entropy (AUROC and AUPR of $0.878$ and $0.316$ respectively) and aleatoric uncertainty (AUROC and AUPR of $0.877$ and $0.316$ respectively).
@@
 In this paper we have adapted a novel classification method capable of providing uncertainty estimates to the task of multi-class classification of multimodal remote sensing data.
-The adopted framework, based upon the theory of Subjective Logic, provides measures of vacuity and dissonance which are better capable of identifying misclassifications and out of distribution samples than the alternative probabilistic measures of uncertainty assessed.
-Experimental results have shown the performance of the S-BGCN-T-K model in the tasks of misclassification and OOD detection to be improved against baseline methods.
+The adopted framework, based upon the theory of Subjective Logic, provides measures of vacuity and dissonance which are better capable of identifying out of distribution samples than the alternative probabilistic measures of uncertainty assessed.
+Experimental results have shown the performance of the S-BGCN-T-K model for OOD detection to be improved against baseline methods.
 This represents a promising avenue for uncertainty-aware learning in the task of multimodal remote sensing classification.
@@
 The presented results illustrate the importance of convergence assistance techniques as a means for improving the quality of uncertainty estimates, particularly through the use of a prior.
-This can be seen by comparing the S-BGCN-T-K misclassification detection and OOD detection performance with equivalent models which do not use a prior, e.g. S-BGCN-T.
-Of the uncertainty measures produced by the S-BGCN-T-K model, the measures of vacuity, aleatoric uncertainty or entropy all provide near-best performance for the identifying misclassifications.
+This can be seen by comparing the S-BGCN-T-K OOD detection performance with equivalent models which do not use a prior, e.g. S-BGCN-T.
+% Of the uncertainty measures produced by the S-BGCN-T-K model, the measures of vacuity, aleatoric uncertainty or entropy all provide near-best performance for the identifying misclassifications.
 In order to identify OOD nodes, the measure of vacuity stands out as the best-performing uncertainty metric.
@@
 There is also scope for research into how the choice of method for computing the $\hat{\boldsymbol{\alpha}}$ prior affects the quality of uncertainty estimates, either by varying the scale parameter, $\sigma$, or considering different prior computation methods entirely.
-%% The acknowledgments section is defined using the "acknowledgments" environment
-%% (and NOT an unnumbered section). This ensures the proper
-%% identification of the section in the article metadata, and the
-%% consistent spelling of the heading.
-% \begin{acknowledgments}
-%   Thanks to ...
-% \end{acknowledgments}
+% The acknowledgments section is defined using the "acknowledgments" environment
+% (and NOT an unnumbered section). This ensures the proper
+% identification of the section in the article metadata, and the
+% consistent spelling of the heading.
+\begin{acknowledgments}
+This work is funded in part by Centre for Integrated Remote Sensing and Forecasting for Arctic Operations (CIRFA) and the Research Council of Norway (RCN Grant no.
+237906), the Automatic Multisensor remote sensing for Sea Ice Characterization (AMUSIC) Framsenteret ``Polhavet'' flagship project 2020, the Isaac Newton Trust, and Newnham College, Cambridge, UK.
+\end{acknowledgments}
 

### 2021-07-14 latex/CEUR/paper.tex
Wed evening save

@@
 With an appropriately chosen loss function, the graph-based classifier will converge to provide accurate estimates of uncertainty.
-The results presented in this paper show that the measures of uncertainty provided by such models are capable of better distinguishing model misclassifications as well as out-of-distribution data samples than probabilistic measures of uncertainty produced by equivalent deterministic neural networks.
+The results presented in this paper show that the measures of uncertainty provided by such models are capable of better distinguishing out-of-distribution data samples than probabilistic measures of uncertainty produced by equivalent deterministic neural networks.
 \end{abstract}
@@
 
-In order assess the relative ability of evidential uncertainties to express different types of doubt, three commonly used probabilistic measures of uncertainty (aleatoric, epistemic and entropy) are computed to provide comparisons.
-For a Bayesian model with inputs, outputs and parameters denoted $x$, $y$ and $\boldsymbol{\theta}$ respectively, the posterior, which will be approximated, is $p(\boldsymbol{\theta}\vert\mathcal{D})$, where $\mathcal{D}$ is the observed dataset.
-The total entropy, made up of both aleatoric and epistemic uncertainty \cite{Depeweg2018} is given by
-\begin{equation}
-    \mathcal{H}\left(\mathbb{E}_{p(\boldsymbol{\theta}\vert \mathcal{D})}\left[p(y\vert x;\boldsymbol{\theta}\right]\right),
-\end{equation}
-where $\mathcal{H}()$ computes the differential entropy of a distribution.
+The differential entropy of the model predictions is also computed to provide a comparitive metric against which the evidential uncertainties can be compared.
+% For a Bayesian model with inputs, outputs and parameters denoted $x$, $y$ and $\boldsymbol{\theta}$ respectively, the posterior, which will be approximated, is $p(\boldsymbol{\theta}\vert\mathcal{D})$, where $\mathcal{D}$ is the observed dataset.
+% The total entropy, made up of both aleatoric and epistemic uncertainty \cite{Depeweg2018} is given by
+% \begin{equation}
+%     \mathcal{H}\left(\mathbb{E}_{p(\boldsymbol{\theta}\vert \mathcal{D})}\left[p(y\vert x;\boldsymbol{\theta}\right]\right),
+% \end{equation}
+% where $\mathcal{H}()$ computes the differential entropy of a distribution.
 % Aleatoric uncertainty, which accounts for noise inherent to the data observations \cite{Kendall2017}, is given by
@@
 
-In order to measure an uncertainty output's ability to separate misclassifications, a receiver operating characteristic (ROC) curve and a precision-recall (PR) curve can be computed.
+In order to measure an uncertainty output's ability to separate OOD nodes, a receiver operating characteristic (ROC) curve and a precision-recall (PR) curve can be computed.
 The area under the ROC curve and PR curve (AUROC and AUPR respectively) can be used as a single numerical representation of the detection performance, where an area of $1.0$ would represent a perfect discriminator for both metrics.
@@
 
-Benchmark models presented include the `standard' GCN (which can provide uncertainty via entropy) and the Drop-GCN which is a GCN where dropout inference has been applied to produce estimates of aleatoric and epistemic uncertainty in addition to entropy.
+A benchmark has been provided by training `standard' GCNs which provide prediction entropy as a form of uncertainty estimate.
 
@@
 By training models using only a subset of the classes provided by the GT, with the other classes acting as out of distribution (OOD) samples, the OOD detection ability of the uncertainty metrics can be measured.
-Using the same approach as described for misclassification detection, the AUROC and AUPR can be calculated for each uncertainty output provided by each model type, in order to determine the relative performance of the respective metrics for this task.
+The AUROC and AUPR can be calculated for each uncertainty output provided by each model type, in order to determine the relative performance of the respective metrics for this task.
 
@@
 S-MLP & $0.767\pm0.152$ & $0.805\pm0.114$ & $0.787\pm0.125$ & $0.245\pm0.214$ & $0.233\pm0.170$ & $0.219\pm0.201$   \\   
-GCN & - & - & $0.538\pm0.188$ & - & - & $0.116\pm0.179$  \\ 
-Drop-GCN & - & - & $0.538\pm0.187$ & - & - & $0.116\pm0.179$  \\ \hline
+GCN & - & - & $0.538\pm0.188$ & - & - & $0.116\pm0.179$  \\  \hline
+% Drop-GCN & - & - & $0.538\pm0.187$ & - & - & $0.116\pm0.179$  \\ \hline
 \end{tabular}
@@
 For the task of OOD detection, the S-BGCN-T-K model is the highest ranked model.
-Its measure of vacuity uncertainty provided the best distinguishing metric, with mean AUROC and AUPR of $0.882$ and $0.318$ respectively, closely followed by performance from the measures of entropy (AUROC and AUPR of $0.878$ and $0.316$ respectively) and aleatoric uncertainty (AUROC and AUPR of $0.877$ and $0.316$ respectively).
+Its measure of vacuity uncertainty provided the best distinguishing metric, with mean AUROC and AUPR of $0.882$ and $0.318$ respectively, closely followed by performance from the measure of entropy (AUROC and AUPR of $0.878$ and $0.316$ respectively).
 The performance of the S-BGCN-T-K model stands out above the performance of other models trained.

### 2021-07-15 latex/CEUR/paper.tex
Addressed all feedback. Just needs one last proof-read.

@@
 \begin{abstract}
-In order to adopt deep learning methods in environments where the decisions being made are high-stakes, it is important the methods are capable of quantifying the prediction confidence or uncertainty.
+%In order to adopt deep learning methods in environments where the decisions being made are high-stakes, it is important the methods are capable of quantifying the prediction confidence or uncertainty.
+Having the ability to quantify prediction confidence or uncertainty will greatly assist the successful integration of deep learning methods into high-stake decision making processes.
 Graph-based convolutional neural networks can be trained to perform classification of multimodal remote sensing data using a model output which represents a Dirichlet distribution parameterization.
@@
 
-The differential entropy of the model predictions is also computed to provide a comparitive metric against which the evidential uncertainties can be compared.
+The entropy of the node-level multinomial distributions provided by the models is also computed to represent a form of uncertainty.
+This is done in order to provide a comparitive metric against which the evidential uncertainties can be compared.
 % For a Bayesian model with inputs, outputs and parameters denoted $x$, $y$ and $\boldsymbol{\theta}$ respectively, the posterior, which will be approximated, is $p(\boldsymbol{\theta}\vert\mathcal{D})$, where $\mathcal{D}$ is the observed dataset.
@@
 
-It would also be reasonable to expect that uncertainty should be higher when the model is asked to make a prediction using an input which does not resemble the inputs upon which it was trained.
+It would be reasonable to expect that uncertainty should be higher when the model is asked to make a prediction using an input which does not resemble the inputs upon which it was trained.
 The relative inability of neural networks to successfully extrapolate beyond the support of the training data is a well-known weakness of these methods \cite{Lakshminarayanan2017}.
@@
 The fact that vacuity is the uncertainty measure which best distinguishes OOD nodes reflects intuition.
-Since vacuity measures the absence of evidence for a prediction, it is natural to expect that it would better distinguish OOD nodes for which the model ought to have little evidence to support its predictions.
+Since vacuity measures the absence of evidence for a prediction, it is natural to expect that it would better distinguish OOD nodes for which the model ought to have little evidence to support its classification.
 
@@
 In this paper we have adapted a novel classification method capable of providing uncertainty estimates to the task of multi-class classification of multimodal remote sensing data.
-The adopted framework, based upon the theory of Subjective Logic, provides measures of vacuity and dissonance which are better capable of identifying out of distribution samples than the alternative probabilistic measures of uncertainty assessed.
+The adopted framework, based upon the theory of Subjective Logic, provides measures of vacuity and dissonance uncertainty.
+Of the types of uncertainty assessed, the measure of vacuity was the best metric to perform identification of out of distribution samples.
 Experimental results have shown the performance of the S-BGCN-T-K model for OOD detection to be improved against baseline methods.
@@
 % Of the uncertainty measures produced by the S-BGCN-T-K model, the measures of vacuity, aleatoric uncertainty or entropy all provide near-best performance for the identifying misclassifications.
-In order to identify OOD nodes, the measure of vacuity stands out as the best-performing uncertainty metric.
 
 Future work should consider the generalisation potential of this method by assessing performance on other challenging remote sensing classification datasets.
-There is also scope for research into how the choice of method for computing the $\hat{\boldsymbol{\alpha}}$ prior affects the quality of uncertainty estimates, either by varying the scale parameter, $\sigma$, or considering different prior computation methods entirely.
+The analysis could also be extended to assess whether the presented uncertainty measures could be used to detect model misclassifications.
+Additionally, there is scope for research into how the choice of method for computing the $\hat{\boldsymbol{\alpha}}$ prior affects the quality of uncertainty estimates, either by varying the scale parameter, $\sigma$, or considering different prior computation methods entirely.
 % The acknowledgments section is defined using the "acknowledgments" environment

### 2021-07-19 latex/CEUR/paper.tex
CDCEO submission sent.

@@
 }
-\newcommand{\infdiv}{D\infdivx}
+\newcommand{\infdiv}{D_{\textrm{KL}}\infdivx}
 \DeclarePairedDelimiter{\norm}{\lVert}{\rVert}
@@
 % The "title" command
-\title{Uncertainty-aware graph-based multimodal remote sensing}
+\title{Uncertainty-aware graph-based multimodal remote sensing detection of out-of-distribution samples}
 
@@
 \label{sec::unc_framework}
+The proposed uncertainty-aware framework relies on the definition of uncertainty metrics, which in turn are based on subjective logic and a Dirichlet mapping \cite{ZhaoXujiang2020}.
+These steps are detailed in this section, and have been properly adapted to the task of multimodal remote sensing classification.
 
@@
 \end{equation}
-which corresponds to the summation of KL-divergence terms between the teacher output probability and the expected value of the subjective model's Dirichlet distribution for each node, $\sum_i\infdiv{\hat{p}_{ik}}{\mathbb{E}[p_{ik}]}$.
+which corresponds to the summation of Kullback-Leibler (KL) divergence terms between the teacher output probability and the expected value of the subjective model's Dirichlet distribution for each node.
+Using $D_{\textrm{KL}}(\,\vert\vert\,)$ to compute the KL divergence, this is stated equivalently as $\sum_i\infdiv{\hat{p}_{ik}}{\mathbb{E}[p_{ik}]}$.
 Notice that this sum is computed over all nodes as opposed to just the nodes in $\mathbb{L}$.
@@
 \end{equation}
-The KL-divergence between the Dirichlet distribution of the prior and the model output is given by the term
+The KL divergence between the Dirichlet distribution of the prior and the model output is given by the term
 \begin{equation}
@@
 \subsection{Data}
-A subsection of the 2018 IEEE GRSS Data Fusion Challenge dataset was selected for the purposes of validating the described methods.
+A subsection of the 2018 IEEE GRSS Data Fusion Challenge dataset \cite{HoustonDataset} ws selected for the purposes of validating the described methods.
 The ground truth labels in this dataset describe 20 different urban land cover/land use classes (i.e. $K=20$) as well as an unlabelled state, described as Unclassified.
@@
 The adopted framework, based upon the theory of Subjective Logic, provides measures of vacuity and dissonance uncertainty.
-Of the types of uncertainty assessed, the measure of vacuity was the best metric to perform identification of out of distribution samples.
-Experimental results have shown the performance of the S-BGCN-T-K model for OOD detection to be improved against baseline methods.
+Of the types of uncertainty assessed, the measure of vacuity was the best metric to perform identification of OOD samples.
+Experimental results have shown the performance of the S-BGCN-T-K model in the task of OOD detection to be improved against baseline methods.
 This represents a promising avenue for uncertainty-aware learning in the task of multimodal remote sensing classification.

### 2021-10-18 latex/CEUR/paper.tex
Responded to reviewer feedback

@@
 % This command is for the conference information
-\conference{Proceedings of the CIKM 2021 Workshops, November 1-5, Online}
+\conference{Proceedings of the CIKM 2021 Workshops, November 01-05, 2021, Online}
 
@@
 
-\address[1]{Department of Engineering, University of Cambridge, Cambridge, CB2 1PZ United Kingdom}
+\address[1]{Department of Engineering, University of Cambridge, Cambridge, CB2 1PZ, United Kingdom}
 \address[2]{Department of Physics and Technology, UiT the Arctic University of Norway, P.O. box 6050 Langnes, NO-9037, Tromsø, Norway}
@@
 
-In this paper, we have analyzed how well different measures of model uncertainty perform the task of identifying data points which belong from a distribution other than those observed during training (out of distribution detection).
+In this paper, we have analyzed how well different measures of model uncertainty perform the task of identifying data points which belong to a distribution other than those observed during training (out of distribution detection).
 To do so, we have used graph-based neural network architectures that are adapted to provide subjective opinions (as described in the field of belief or evidence theory \cite{Josang2018}) through the use of Dirichlet distribution parameterizations \cite{Kipf2017, ZhaoXujiang2020}.
-Adopting such a method for performing multimodal classification of remote sensing data is, to the best of our knowledge, an as-yet untested approach.
-The performance of the adopted technique represents a promising avenue in the search for meaningful uncertainty estimates when performing multimodal remote sensing classification.
+The subjective opinions can be used to measure two intuitive measures of uncertainty: vacuity and dissonance.
+Vacuity is a measure of the uncertainty related to an absence of observed evidence, i.e. a higher measure of vacuity suggests a lack of supporting evidence for a prediction.
+Dissonance is a measure of prediction uncertainty arising due to the presence of conflicting evidence.
+This approach (using graph-based neural networks within a subjective-logic framework) is, to the best of our knowledge, as-yet untested as a method for performing classification of multimodal remote sensing data.
+The performance of the adopted technique represents a promising avenue in the search for meaningful uncertainty estimates for this task.
 
@@
 \subsection{Subjective models}
-An adaptation to the GCN architecture used by \cite{Kipf2017} must be made in order to obtain subjective opinions that will be used to obtain measures of vacuity and dissonance uncertainty.
+An adaptation to the GCN architecture used by \cite{Kipf2017} must be made in order to obtain the subjective opinions that will be used to obtain measures of vacuity and dissonance uncertainty.
 The adaptation made means that the model will output node-level Dirichlet distribution parameters, such that the output will provide a probability distribution over multinomial class probabilities for each node.
@@
 Notice that this sum is computed over all nodes as opposed to just the nodes in $\mathbb{L}$.
-Models trained using a teacher are denoted using the ``-T'' suffix e.g.
+Models trained using a teacher are denoted using the `-T' suffix e.g.
 a S-BGCN-T model would indicate that a pre-trained GCN was used as a teacher in order to assist the training convergence of a subjective graph convolutional model.
@@
 which can, in turn, be incorporated into the total loss function.
-Models trained using a prior are denoted using the ``-K'' suffix.
+Models trained using a prior are denoted using the `-K' suffix.
 
 Table \ref{loss_table} shows how these convergence assistance techniques can be weighted and combined in various permutations to provide a total loss function, $\mathcal{L}_\text{total}(\boldsymbol{\theta})$, as well as the model name abbreviations used to denote which combination has been used.
-The "B" in the model names of Table \ref{loss_table} refers to the fact that dropout inference has been used as a Bayesian approximation, as mentioned in Section \ref{sec::UncertaintyMeasures}.
+The `B' in the model names of Table \ref{loss_table} refers to the fact that dropout inference has been used as a Bayesian approximation.
 The coefficients $\lambda_{\text{T}}$ and $\lambda_{\text{K}}$ are used to control the relative importance of the teacher network and the Dirichlet prior respectively against the importance of the subjective loss function given in (\ref{eq:core_loss}).
@@
 \subsection{Network training and hyperparameters}
-Models were implemented and trained using the TensorFlow library \cite{Abadi2015}.
+Models were implemented and trained using the TensorFlow library \cite{Abadi2015} on a personal laptop computer with Intel Core i7 CPU and 16 GB of RAM.
 In order to handle the imbalance of classes in the dataset, sample weighting was used.
@@
 This work is funded in part by Centre for Integrated Remote Sensing and Forecasting for Arctic Operations (CIRFA) and the Research Council of Norway (RCN Grant no.
-237906), the Automatic Multisensor remote sensing for Sea Ice Characterization (AMUSIC) Framsenteret ``Polhavet'' flagship project 2020, the Isaac Newton Trust, and Newnham College, Cambridge, UK.
+237906), the Automatic Multisensor remote sensing for Sea Ice Characterization (AMUSIC) Framsenteret `Polhavet' flagship project 2020, the Isaac Newton Trust, and Newnham College, Cambridge, UK.
 \end{acknowledgments}

### 2021-10-18 uncertainty_utils.py
Wrapped long lines of code

@@ -1,6 +1,6 @@
 import numpy as np
 from tqdm import tqdm
-from utils import mask_to_weights, log_error
+from .utils import mask_to_weights, log_error
 from sklearn.metrics import roc_auc_score, average_precision_score
 from scipy.special import xlogy
 import tensorflow as tf
@@ -36,11 +36,13 @@ def dissonance_uncertainty(alpha):
 
     for i in tqdm(range(alpha.shape[0])):  # for each node
         b = belief[i]  # belief vector
-        numerator, denominator = np.abs(b[:, None] - b[None, :]), b[None, :] + b[:, None]
+        numerator, denominator = np.abs(
+            b[:, None] - b[None, :]), b[None, :] + b[:, None]
         bal = 1 - np.true_divide(numerator, denominator, where=denominator != 0,
                                  out=np.zeros_like(denominator)) - np.eye(len(b))
         coefficients = b[:, None] * b[None, :] - np.diag(b ** 2)
-        denominator = np.sum(b[None, :] * np.ones(belief.shape[1]) - np.diag(b), axis=-1, keepdims=True)
+        denominator = np.sum(
+            b[None, :] * np.ones(belief.shape[1]) - np.diag(b), axis=-1, keepdims=True)
         dis_un[i] = (coefficients * np.true_divide(bal, denominator, where=denominator != 0,
                                                    out=np.zeros_like(bal))).sum()
 
@@ -57,14 +59,16 @@ def entropy(prob):
 
 
 def entropy_bayesian(prob_samples):
-    prob = np.mean(prob_samples, axis=0)  # take the average probability from MC-Dropouts and compute its entropy
+    # take the average probability from MC-Dropouts and compute its entropy
+    prob = np.mean(prob_samples, axis=0)
     return entropy(prob)
 
 
 def aleatoric_bayesian(prob_samples):
     al_total, al_class = [], []
     for prob in prob_samples:
-        total_en, class_en = entropy(prob)  # take the entropy of each MC-Dropout output and compute the mean entropy
+        # take the entropy of each MC-Dropout output and compute the mean entropy
+        total_en, class_en = entropy(prob)
         al_total.append(total_en), al_class.append(class_en)
     return np.mean(al_total, axis=0), np.mean(al_class, axis=0)
 
@@ -91,8 +95,10 @@ class DropoutUncertainties:
             message = "Probabilities sum to greater than one, has method been called using Dirichlet parameters?"
             raise log_error(AssertionError, message)
         if self.samples_seen >= self.num_samples:
[…]
